%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Overall Description}
\label{chap:overall-description}

This chapter provides a high-level description of the EcoTrace
Intelligent Electronic Waste Recovery and Circular Economy Management
System. It describes the system's relationship to its operational
environment, identifies its major functions, defines the intended user
classes, specifies the operating environment, outlines design
constraints, and documents assumptions and dependencies that influence
the development and operation of the system.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Product Perspective}
\label{sec:product-perspective}

EcoTrace is an integrated electronic waste management platform designed
to support the complete lifecycle of electronic waste, from
registration and collection to repair, refurbishment, recycling,
resale, and final disposal.

The platform adopts a modular architecture that combines mobile
applications, web applications, cloud services, geospatial services,
and artificial intelligence into a unified solution.

The system supports multiple stakeholders, including households,
businesses, waste collectors, drivers, technicians, recyclers, and
system administrators.

EcoTrace operates as a cloud-based information system where data is
centrally managed while allowing authorized users to access services
from multiple platforms.

The overall product architecture consists of:

\begin{itemize}

\item Flutter cross-platform applications;

\item Firebase cloud infrastructure;

\item Cloud Firestore database;

\item Firebase Storage;

\item Firebase Authentication;

\item Firebase Cloud Messaging;

\item Google Maps Platform;

\item PyTorch-based Artificial Intelligence service; and

\item Administrative web dashboard.

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Product Functions}
\label{sec:product-functions}

The EcoTrace platform provides a comprehensive set of functions for the
management of electronic waste and circular economy operations.

The major system functions include:

\begin{itemize}

\item user registration and authentication;

\item role-based access control;

\item electronic waste registration;

\item AI-assisted electronic waste classification;

\item pickup request management;

\item route visualization and navigation;

\item repair and refurbishment management;

\item recycling management;

\item reverse logistics management;

\item marketplace management;

\item notification management;

\item reporting and analytics; and

\item system administration.

\end{itemize}

The detailed functional requirements for each module are presented in
Chapter~\ref{chap:functional-requirements}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{User Classes and Characteristics}
\label{sec:user-classes}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The EcoTrace platform serves multiple categories of users. Each user
class has specific responsibilities and access privileges.

\begin{table}[H]
\centering
\caption{User Classes and Characteristics}
\label{tab:user_classes}
\small

\begin{tabular}{|p{4cm}|p{10cm}|}

\hline
\textbf{User Class} &
\textbf{Description} \\
\hline

Household User &
Individuals who register electronic waste and request collection
services. \\
\hline

Business User &
Organizations responsible for managing institutional electronic waste
and coordinating bulk collections. \\
\hline

Collector &
Field personnel responsible for collecting electronic waste from
registered locations. \\
\hline

Driver &
Personnel responsible for transporting collected electronic waste to
repair, refurbishment, or recycling facilities. \\
\hline

Technician &
Users responsible for inspecting, repairing, and refurbishing
electronic devices. \\
\hline

Recycler &
Personnel responsible for processing electronic waste materials for
recycling and recovery. \\
\hline

Administrator &
Authorized personnel responsible for system configuration, monitoring,
reporting, and user management. \\
\hline

Super Administrator &
Users with unrestricted administrative privileges over the entire
platform. \\
\hline

\end{tabular}

\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Operating Environment}
\label{sec:operating-environment}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

EcoTrace operates within a cloud-based computing environment that
supports Android mobile devices, modern web browsers, and Microsoft
Windows desktop systems.

The operational environment consists of:

\begin{itemize}

\item Android smartphones and tablets;

\item Windows desktop computers;

\item modern web browsers;

\item Firebase cloud infrastructure;

\item Google Maps Platform;

\item Internet connectivity;

\item Cloud Firestore database;

\item Firebase Storage;

\item PyTorch inference server; and

\item secure HTTPS communication.

\end{itemize}

The system requires reliable network connectivity for synchronization,
cloud storage, authentication, and artificial intelligence inference.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Design Constraints}
\label{sec:design-constraints}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The development of EcoTrace is subject to several technical,
operational, and organizational constraints.

The principal constraints include:

\begin{itemize}

\item Flutter is used as the cross-platform development framework.

\item Firebase provides authentication, cloud database, storage, and
notification services.

\item Google Maps Platform provides geospatial functionality.

\item PyTorch provides artificial intelligence inference.

\item The system depends on Internet connectivity for cloud-based
operations.

\item Access to protected resources requires authentication.

\item Personal information must be protected according to applicable
privacy requirements.

\item The system shall remain scalable to accommodate future expansion.

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{User Documentation}
\label{sec:user-documentation}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The EcoTrace platform shall be accompanied by documentation to support
installation, operation, maintenance, and training.

The documentation shall include:

\begin{itemize}

\item User Manual;

\item Administrator Guide;

\item Installation Guide;

\item Software Requirements Specification;

\item System Design Documentation;

\item API Documentation;

\item Maintenance Guide; and

\item Training Materials.

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Assumptions and Dependencies}
\label{sec:assumptions-dependencies}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The EcoTrace platform shall be accompanied by documentation to support
installation, operation, maintenance, and training.

The documentation shall include:

\begin{itemize}

\item User Manual;

\item Administrator Guide;

\item Installation Guide;

\item Software Requirements Specification;

\item System Design Documentation;

\item API Documentation;

\item Maintenance Guide; and

\item Training Materials.

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Assumptions and Dependencies}
\label{sec:assumptions-dependencies}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The successful operation of EcoTrace depends on several assumptions and
external services.

These assumptions include:

\begin{itemize}

\item Users possess compatible computing devices.

\item Reliable Internet connectivity is available.

\item Firebase cloud services remain operational.

\item Google Maps Platform services are available.

\item The PyTorch inference server remains accessible.

\item Users provide accurate registration information.

\item Electronic waste images are of sufficient quality for AI
classification.

\item Authorized personnel maintain the cloud infrastructure.

\end{itemize}

These assumptions define the operational context within which the
EcoTrace platform is expected to function.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%