 
\chapter{External Interface Requirements}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}

The External Interface Requirements specify how the EcoTrace:
Intelligent Electronic Waste Recovery and Circular Economy Management
System interacts with users, hardware devices, software platforms,
communication networks, cloud services, artificial intelligence
components, and external information systems.

These requirements define the interfaces necessary to ensure reliable,
secure, interoperable, and efficient communication between the EcoTrace
platform and all internal and external entities. They establish the
technical contracts that govern data exchange, user interaction,
hardware communication, software integration, network protocols,
third-party services, and cloud infrastructure.

EcoTrace is designed as a multi-platform enterprise information system
developed using Flutter and Firebase technologies. The platform supports
Android mobile applications, Web applications, and Windows desktop
applications while integrating with cloud-based services,
artificial intelligence engines, mapping services, notification
services, payment gateways, and environmental regulatory systems.

The interfaces defined in this chapter shall ensure secure,
interoperable, reliable, maintainable, and scalable communication
between all components of the EcoTrace platform.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{User Interface Requirements}

\subsection{Overview}

The User Interface Requirements define the visual, navigational, accessibility, security, and interaction standards for all EcoTrace client applications. These requirements apply to Android mobile applications, Web portals, and Windows desktop applications unless a role-specific requirement states otherwise.

\subsection{General User Interface Requirements}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection*{Purpose}

The General User Interface Requirements define the common interface
standards that shall be implemented across all EcoTrace applications,
including Android mobile applications, Web applications, and Windows
desktop applications. These requirements ensure a consistent user
experience, reduce training requirements, improve accessibility, and
support efficient completion of user tasks.

The interface shall follow modern enterprise application design
principles while remaining intuitive for household users, businesses,
collectors, drivers, technicians, recyclers, administrators, and other
authorized stakeholders.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{User Interface Design Principles}

The EcoTrace user interface shall be designed according to the following
principles:

\begin{itemize}
\item Simplicity
\item Consistency
\item Accessibility
\item Responsiveness
\item Readability
\item Security
\item Scalability
\item Performance
\item Professional Appearance
\item User-Centred Design
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{General User Interface Requirements}

\paragraph{UIR-001 Interface Consistency}
The system shall maintain a consistent interface across all supported
platforms.

\paragraph{UIR-002 Responsive Design}
The interface shall automatically adapt to mobile, tablet, desktop,
and large-screen devices.

\paragraph{UIR-003 Responsive Layout}
Interface components shall automatically resize according to screen
resolution.

\paragraph{UIR-004 Navigation Consistency}
Navigation menus shall remain consistent throughout the platform.

\paragraph{UIR-005 Corporate Branding}
The interface shall consistently display EcoTrace branding elements.

\paragraph{UIR-006 Logo Placement}
The EcoTrace logo shall appear consistently in application headers.

\paragraph{UIR-007 Color Scheme}
The interface shall use the approved EcoTrace colour palette.

\paragraph{UIR-008 Typography}
The system shall use consistent typography throughout the platform.

\paragraph{UIR-009 Icons}
The system shall use consistent iconography.

\paragraph{UIR-010 White Space}
The interface shall maintain adequate spacing to improve readability.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Navigation Requirements}

\paragraph{UIR-011 Main Navigation}
The system shall provide a primary navigation menu.

\paragraph{UIR-012 Secondary Navigation}
The system shall support contextual secondary navigation.

\paragraph{UIR-013 Dashboard Navigation}
Users shall navigate directly from dashboards to related modules.

\paragraph{UIR-014 Breadcrumbs}
Web and desktop interfaces shall display breadcrumb navigation.

\paragraph{UIR-015 Search}
The interface shall provide global search functionality.

\paragraph{UIR-016 Quick Actions}
Dashboards shall provide frequently used actions.

\paragraph{UIR-017 Notifications}
Unread notifications shall be prominently displayed.

\paragraph{UIR-018 User Profile}
Authenticated users shall access their profiles from every screen.

\paragraph{UIR-019 Logout}
Users shall be able to securely sign out from any authenticated page.

\paragraph{UIR-020 Help}
Context-sensitive help shall be available throughout the application.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Dashboard Requirements}

\paragraph{UIR-021 Personalized Dashboard}
Each authenticated user shall receive a role-specific dashboard.

\paragraph{UIR-022 Dashboard Widgets}
Dashboard widgets shall be configurable where permitted.

\paragraph{UIR-023 Real-Time Data}
Dashboards shall display current operational information.

\paragraph{UIR-024 KPI Cards}
Dashboards shall display key performance indicators.

\paragraph{UIR-025 Charts}
Dashboards shall support graphical visualization.

\paragraph{UIR-026 Activity Timeline}
Dashboards shall display recent activities.

\paragraph{UIR-027 Notification Panel}
Dashboards shall include a notification panel.

\paragraph{UIR-028 Quick Statistics}
Dashboards shall display summary statistics.

\paragraph{UIR-029 Shortcuts}
Frequently used operations shall be accessible through dashboard
shortcuts.

\paragraph{UIR-030 Refresh}
Users shall be able to refresh dashboard information.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Forms and Data Entry}

\paragraph{UIR-031 Form Validation}
Forms shall validate user input before submission.

\paragraph{UIR-032 Mandatory Fields}
Mandatory fields shall be clearly identified.

\paragraph{UIR-033 Input Constraints}
Input fields shall enforce format constraints.

\paragraph{UIR-034 Date Picker}
Date fields shall use graphical date pickers.

\paragraph{UIR-035 Time Picker}
Time fields shall use graphical time selectors.

\paragraph{UIR-036 Dropdown Lists}
Standardized options shall be presented using dropdown controls.

\paragraph{UIR-037 Auto-Complete}
Frequently entered values shall support auto-complete.

\paragraph{UIR-038 File Upload}
The interface shall support secure file uploads.

\paragraph{UIR-039 Image Preview}
Uploaded images shall be previewed before submission.

\paragraph{UIR-040 Draft Saving}
Long forms shall support draft saving.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Feedback and Messaging}

\paragraph{UIR-041 Success Message}
Successful operations shall display confirmation messages.

\paragraph{UIR-042 Warning Message}
Potentially risky actions shall display warning messages.

\paragraph{UIR-043 Error Message}
Errors shall clearly explain the problem and recommended action.

\paragraph{UIR-044 Confirmation Dialog}
Critical operations shall require user confirmation.

\paragraph{UIR-045 Loading Indicator}
The interface shall display loading indicators during processing.

\paragraph{UIR-046 Progress Indicator}
Long-running operations shall display progress information.

\paragraph{UIR-047 Toast Notifications}
Brief status updates may be displayed using toast notifications.

\paragraph{UIR-048 Retry Option}
Users shall be able to retry failed operations where appropriate.

\paragraph{UIR-049 Offline Indicator}
The interface shall indicate offline operation.

\paragraph{UIR-050 Synchronization Status}
The interface shall display synchronization status for offline data.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection*{Accessibility Requirements}

\paragraph{UIR-051 Accessibility Compliance}
The user interface shall comply with the Web Content Accessibility
Guidelines (WCAG) 2.1 Level AA where applicable.

\paragraph{UIR-052 Keyboard Navigation}
Desktop users shall be able to navigate the application using only the
keyboard.

\paragraph{UIR-053 Screen Reader Support}
The interface shall support screen reader technologies.

\paragraph{UIR-054 Colour Contrast}
Text and graphical elements shall satisfy minimum accessibility colour
contrast requirements.

\paragraph{UIR-055 Scalable Text}
Users shall be able to enlarge text without loss of functionality.

\paragraph{UIR-056 Alternative Text}
Images and icons shall support descriptive alternative text where
appropriate.

\paragraph{UIR-057 Focus Indicator}
The interface shall visibly indicate keyboard focus.

\paragraph{UIR-058 Accessible Forms}
All form controls shall include descriptive labels.

\paragraph{UIR-059 Error Identification}
Input validation errors shall clearly identify the affected field.

\paragraph{UIR-060 Accessibility Consistency}
Accessibility features shall be consistently implemented across all
supported platforms.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection*{Performance Requirements}

\paragraph{UIR-061 Fast Navigation}
Navigation between screens shall occur without unnecessary delays.

\paragraph{UIR-062 Optimized Images}
Images shall be optimized for fast loading.

\paragraph{UIR-063 Lazy Loading}
Large datasets shall support lazy loading or pagination.

\paragraph{UIR-064 Efficient Rendering}
The interface shall efficiently render dynamic content.

\paragraph{UIR-065 Background Processing}
Long-running operations shall execute in the background where
appropriate.

\paragraph{UIR-066 Responsive Feedback}
User interactions shall receive immediate visual feedback.

\paragraph{UIR-067 Caching}
Frequently accessed information shall support local caching.

\paragraph{UIR-068 Offline Support}
Supported functions shall remain available during temporary network
interruptions.

\paragraph{UIR-069 Automatic Synchronization}
Offline data shall synchronize automatically when connectivity is
restored.

\paragraph{UIR-070 Resource Optimization}
The interface shall minimize unnecessary network and battery
consumption.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection*{Security Requirements}

\paragraph{UIR-071 Session Timeout}
Inactive authenticated sessions shall expire according to configured
security policies.

\paragraph{UIR-072 Automatic Logout}
Users shall be automatically logged out after prolonged inactivity where
required.

\paragraph{UIR-073 Sensitive Information}
Sensitive information shall not remain visible after logout.

\paragraph{UIR-074 Password Protection}
Password fields shall mask entered characters.

\paragraph{UIR-075 Secure Clipboard}
Sensitive information copied to the clipboard shall follow configured
security policies.

\paragraph{UIR-076 Unauthorized Access}
Unauthorized users shall not access protected screens.

\paragraph{UIR-077 Secure Navigation}
Navigation to protected pages shall require authorization.

\paragraph{UIR-078 Privacy Protection}
Personally identifiable information shall be displayed only to
authorized users.

\paragraph{UIR-079 Secure Downloads}
Protected documents shall require authorization before download.

\paragraph{UIR-080 Audit Logging}
Critical user interface actions shall be recorded by the Audit Trail and
Activity Logging Module.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection*{User Experience Requirements}

\paragraph{UIR-081 Consistent Workflow}
Business workflows shall remain consistent throughout the platform.

\paragraph{UIR-082 Minimal User Actions}
Frequently used tasks shall require the minimum practical number of user
interactions.

\paragraph{UIR-083 Clear Terminology}
The interface shall use clear, consistent terminology.

\paragraph{UIR-084 Predictable Behaviour}
Interface behaviour shall remain predictable.

\paragraph{UIR-085 Visual Hierarchy}
Important information shall receive greater visual emphasis.

\paragraph{UIR-086 Context Awareness}
The interface shall display context-relevant information.

\paragraph{UIR-087 Professional Appearance}
The interface shall maintain a clean and professional appearance.

\paragraph{UIR-088 Consistent Components}
Reusable interface components shall behave consistently.

\paragraph{UIR-089 Adaptive Layout}
The interface shall adapt to different device orientations.

\paragraph{UIR-090 User Preferences}
Users shall be able to personalize supported interface settings.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection*{General Validation Rules}

\begin{itemize}

\item All mandatory fields shall be completed before submission.

\item Invalid input shall be rejected with meaningful validation
messages.

\item Navigation shall remain consistent throughout the platform.

\item Protected pages shall require authentication.

\item Dashboard information shall reflect current authorized data.

\item Interface elements shall remain responsive on supported devices.

\item Accessibility requirements shall be applied consistently.

\item Sensitive information shall never be displayed to unauthorized
users.

\item User interface operations shall generate appropriate audit records
where required.

\item Interface behaviour shall remain consistent across Android, Web,
and Windows applications.

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Household Mobile Application}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Purpose}

The Household Mobile Application shall provide individual households
with a secure, intuitive, and user-friendly interface for participating
in electronic waste management activities. The application shall enable
users to schedule electronic waste collection, identify electronic
devices using artificial intelligence, monitor collection requests,
receive environmental rewards, purchase refurbished electronics,
participate in recycling campaigns, and track their environmental
contribution.

The application shall be developed using Flutter and shall support
Android devices. The interface shall remain responsive, secure,
accessible, and consistent with the overall EcoTrace design language.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Primary Users}

\begin{itemize}

\item Household Users

\item Registered Citizens

\item Residential Property Owners

\item Residential Tenants

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Main Navigation}

The Household Mobile Application shall provide the following primary
navigation menu:

\begin{itemize}

\item Home

\item AI Scan

\item Pickups

\item Marketplace

\item Rewards

\item Notifications

\item Profile

\item Settings

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Home Dashboard Components}

The Home Dashboard shall include the following interface components:

\begin{itemize}

\item Welcome Banner

\item User Profile Summary

\item Environmental Impact Summary

\item Pickup Status Card

\item AI Scan Shortcut

\item Marketplace Shortcut

\item Rewards Summary

\item Collection History

\item Recent Notifications

\item Quick Actions

\item Educational Tips

\item Community Campaign Banner

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Household User Interface Requirements}

\paragraph{HUI-001 Home Dashboard}

The application shall display a personalized Home Dashboard after
successful authentication.

\paragraph{HUI-002 Welcome Message}

The Home Dashboard shall display a personalized welcome message.

\paragraph{HUI-003 User Profile Card}

The dashboard shall display the user's profile summary.

\paragraph{HUI-004 Environmental Impact}

The dashboard shall summarize the user's environmental contribution,
including total electronic waste recycled, carbon emissions avoided,
and reward points earned.

\paragraph{HUI-005 Quick Actions}

The dashboard shall provide quick access to frequently used features.

\paragraph{HUI-006 Pickup Shortcut}

The dashboard shall provide a shortcut for requesting a new pickup.

\paragraph{HUI-007 AI Scan Shortcut}

The dashboard shall provide direct access to the AI e-waste
identification feature.

\paragraph{HUI-008 Marketplace Shortcut}

The dashboard shall provide access to the refurbished electronics
marketplace.

\paragraph{HUI-009 Rewards Shortcut}

The dashboard shall display the user's available reward points.

\paragraph{HUI-010 Notification Indicator}

Unread notifications shall be prominently displayed on the dashboard.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Pickup Request Interface}

\paragraph{HUI-011 Pickup Request}

The application shall allow household users to schedule electronic waste
collection requests.

\paragraph{HUI-012 Pickup Categories}

The application shall allow users to select one or more categories of
electronic waste.

\paragraph{HUI-013 Pickup Address}

The application shall allow users to choose a registered pickup address
or add a new location.

\paragraph{HUI-014 GPS Location}

The application shall allow automatic retrieval of the user's GPS
location.

\paragraph{HUI-015 Interactive Map}

The application shall display an interactive map during pickup
scheduling.

\paragraph{HUI-016 Preferred Date}

Users shall select their preferred pickup date.

\paragraph{HUI-017 Preferred Time}

Users shall select an available pickup time slot.

\paragraph{HUI-018 Quantity}

Users shall specify the estimated quantity of electronic waste.

\paragraph{HUI-019 Photo Upload}

Users shall upload photographs of electronic waste before submitting a
pickup request.

\paragraph{HUI-020 Pickup Confirmation}

The application shall display a confirmation summary before submission.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Pickup Tracking Interface}

\paragraph{HUI-021 Pickup Status}

The application shall display the current pickup status.

\paragraph{HUI-022 Collector Information}

Users shall view assigned collector information.

\paragraph{HUI-023 Vehicle Information}

Users shall view assigned vehicle information where applicable.

\paragraph{HUI-024 Estimated Arrival}

The application shall display estimated collector arrival time.

\paragraph{HUI-025 Live Tracking}

Users shall track the assigned collector in real time using GPS.

\paragraph{HUI-026 Pickup History}

The application shall maintain complete pickup history.

\paragraph{HUI-027 Pickup Cancellation}

Users shall cancel eligible pickup requests.

\paragraph{HUI-028 Pickup Rescheduling}

Users shall reschedule eligible pickup requests.

\paragraph{HUI-029 Pickup Notifications}

Users shall receive notifications for pickup status changes.

\paragraph{HUI-030 Digital Receipt}

The application shall provide a digital receipt after successful
collection.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Artificial Intelligence Interface}

\paragraph{HUI-031 AI Device Identification}

The application shall provide AI-assisted identification of electronic
devices.

\paragraph{HUI-032 Camera Access}

The application shall allow image capture using the device camera.

\paragraph{HUI-033 Gallery Upload}

Users shall upload existing images from the device gallery.

\paragraph{HUI-034 Image Preview}

The application shall display captured images before analysis.

\paragraph{HUI-035 AI Prediction}

The application shall display AI identification results.

\paragraph{HUI-036 Confidence Score}

The application shall display AI confidence scores.

\paragraph{HUI-037 Disposal Recommendation}

The application shall recommend appropriate disposal methods.

\paragraph{HUI-038 Recycling Recommendation}

The application shall recommend recycling options.

\paragraph{HUI-039 Hazard Warning}

The application shall display hazardous material warnings where
applicable.

\paragraph{HUI-040 Save Result}

Users shall save AI analysis results for future reference.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Rewards Interface}

\paragraph{HUI-041 Reward Dashboard}

The application shall display a reward dashboard.

\paragraph{HUI-042 Reward Points}

Users shall view accumulated reward points.

\paragraph{HUI-043 Reward History}

The application shall maintain reward transaction history.

\paragraph{HUI-044 Available Rewards}

Users shall browse available rewards.

\paragraph{HUI-045 Reward Redemption}

Users shall redeem eligible rewards.

\paragraph{HUI-046 Achievement Badges}

Users shall earn environmental achievement badges.

\paragraph{HUI-047 Environmental Score}

The application shall display an environmental sustainability score.

\paragraph{HUI-048 Community Ranking}

Users shall view community leaderboards where enabled.

\paragraph{HUI-049 Reward Notifications}

Users shall receive reward notifications.

\paragraph{HUI-050 Reward Expiry}

The application shall notify users before reward expiration.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Marketplace Interface}

\paragraph{HUI-051 Marketplace Home}

The application shall provide access to the refurbished electronics
marketplace.

\paragraph{HUI-052 Product Categories}

Products shall be organized into categories.

\paragraph{HUI-053 Product Search}

Users shall search marketplace products.

\paragraph{HUI-054 Product Filters}

Users shall filter products using multiple criteria.

\paragraph{HUI-055 Product Details}

The application shall display detailed product information.

\paragraph{HUI-056 Product Images}

Products shall include multiple high-resolution images.

\paragraph{HUI-057 Shopping Cart}

The application shall support shopping cart functionality.

\paragraph{HUI-058 Secure Checkout}

The application shall provide secure checkout.

\paragraph{HUI-059 Order Tracking}

Users shall monitor order status.

\paragraph{HUI-060 Purchase History}

The application shall maintain purchase history.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Notification Interface}

\paragraph{HUI-061 Notification Centre}

The application shall provide a centralized notification centre.

\paragraph{HUI-062 Push Notifications}

The application shall receive real-time push notifications.

\paragraph{HUI-063 Pickup Notifications}

Users shall receive notifications regarding pickup status changes.

\paragraph{HUI-064 Reward Notifications}

Users shall receive reward and achievement notifications.

\paragraph{HUI-065 Marketplace Notifications}

Users shall receive marketplace order notifications.

\paragraph{HUI-066 Campaign Notifications}

Users shall receive environmental campaign announcements.

\paragraph{HUI-067 Read Status}

The application shall distinguish between read and unread
notifications.

\paragraph{HUI-068 Notification Archive}

Users shall access previous notifications.

\paragraph{HUI-069 Notification Preferences}

Users shall configure notification preferences.

\paragraph{HUI-070 Notification Deletion}

Users shall delete non-essential notifications.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Profile Management Interface}

\paragraph{HUI-071 User Profile}

The application shall provide a comprehensive user profile page.

\paragraph{HUI-072 Profile Photo}

Users shall upload and update profile photographs.

\paragraph{HUI-073 Personal Information}

Users shall update personal information.

\paragraph{HUI-074 Address Management}

Users shall manage multiple pickup addresses.

\paragraph{HUI-075 Contact Information}

Users shall update contact information.

\paragraph{HUI-076 Password Management}

Users shall securely change passwords.

\paragraph{HUI-077 Security Settings}

Users shall configure security settings.

\paragraph{HUI-078 Privacy Preferences}

Users shall manage privacy preferences.

\paragraph{HUI-079 Account Verification}

The application shall display account verification status.

\paragraph{HUI-080 Account Deactivation}

Users shall request account deactivation where permitted.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Settings Interface}

\paragraph{HUI-081 Theme Selection}

Users shall switch between Light Mode and Dark Mode.

\paragraph{HUI-082 Language Selection}

Users shall choose the preferred application language.

\paragraph{HUI-083 Date Format}

Users shall configure preferred date formats.

\paragraph{HUI-084 Time Format}

Users shall configure preferred time formats.

\paragraph{HUI-085 Notification Settings}

Users shall enable or disable notification categories.

\paragraph{HUI-086 Location Services}

Users shall manage GPS and location permissions.

\paragraph{HUI-087 Camera Permission}

Users shall manage camera permissions.

\paragraph{HUI-088 Storage Permission}

Users shall manage storage access permissions.

\paragraph{HUI-089 Data Synchronization}

Users shall configure synchronization preferences.

\paragraph{HUI-090 Reset Preferences}

Users shall restore application settings to default values.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Help and Support Interface}

\paragraph{HUI-091 Help Centre}

The application shall provide an integrated help centre.

\paragraph{HUI-092 Frequently Asked Questions}

Users shall access frequently asked questions.

\paragraph{HUI-093 Contact Support}

Users shall contact customer support directly from the application.

\paragraph{HUI-094 Report Issue}

Users shall report technical issues.

\paragraph{HUI-095 Feedback Submission}

Users shall submit feedback regarding the application.

\paragraph{HUI-096 User Guide}

The application shall provide a digital user guide.

\paragraph{HUI-097 Tutorial}

New users shall have access to an onboarding tutorial.

\paragraph{HUI-098 Emergency Contacts}

Users shall access emergency environmental contact information where
applicable.

\paragraph{HUI-099 Application Information}

Users shall view application version information.

\paragraph{HUI-100 About EcoTrace}

The application shall provide information about EcoTrace and its
environmental objectives.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{General Validation Rules}

\begin{itemize}

\item Mandatory fields shall be completed before submission.

\item Uploaded images shall satisfy supported file formats.

\item GPS coordinates shall be validated before pickup requests.

\item AI image analysis shall require a valid image.

\item Reward redemption shall require sufficient reward points.

\item Marketplace purchases shall require successful payment.

\item Personal information shall be validated before updates.

\item Pickup requests shall comply with configured scheduling rules.

\item Household users shall only access authorized functions.

\item All significant household activities shall be recorded by the
Audit Trail and Activity Logging Module.

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Acceptance Criteria}

\paragraph{HAC-001}

Household users can successfully schedule electronic waste pickups.

\paragraph{HAC-002}

Users can identify electronic devices using AI image recognition.

\paragraph{HAC-003}

Users can monitor pickup progress in real time.

\paragraph{HAC-004}

Users can earn and redeem environmental rewards.

\paragraph{HAC-005}

Users can securely purchase refurbished electronic devices.

\paragraph{HAC-006}

The application provides a responsive and intuitive user experience.

\paragraph{HAC-007}

All household functions operate securely according to assigned
permissions.

\paragraph{HAC-008}

Offline synchronization functions correctly when connectivity is
restored.

\paragraph{HAC-009}

Notifications are delivered according to user preferences.

\paragraph{HAC-010}

The Household Mobile Application provides a complete, secure, and
user-friendly interface for residential participation in electronic
waste recovery and circular economy initiatives.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Business Mobile Application}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Purpose}

The Business Mobile Application shall provide registered organizations,
commercial enterprises, educational institutions, healthcare facilities,
government agencies, and other corporate users with a secure and
comprehensive interface for managing electronic waste throughout its
lifecycle.

The application shall enable organizations to register electronic waste,
schedule bulk collections, monitor collection operations, manage
organizational assets, generate compliance reports, track environmental
performance, purchase refurbished equipment, monitor recycling
activities, and communicate with EcoTrace service providers.

The application shall be developed using Flutter and shall support
Android devices while maintaining consistency with the Web Portal and
Windows Desktop Application.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Primary Users}

\begin{itemize}

\item Business Organizations

\item Government Institutions

\item Educational Institutions

\item Hospitals

\item Banks

\item Corporate Offices

\item Manufacturing Companies

\item NGOs

\item Organization Administrators

\item Sustainability Officers

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Main Navigation}

The Business Mobile Application shall provide the following navigation
menu:

\begin{itemize}

\item Dashboard

\item Assets

\item Pickup Requests

\item AI Scan

\item Marketplace

\item Reports

\item Notifications

\item Organization

\item Profile

\item Settings

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Business Dashboard Components}

The dashboard shall include:

\begin{itemize}

\item Organization Summary

\item Active Pickup Requests

\item Pending Approvals

\item Environmental Impact Summary

\item Carbon Reduction Statistics

\item Asset Inventory Summary

\item AI Identification Summary

\item Marketplace Orders

\item Compliance Alerts

\item Quick Actions

\item Analytics Cards

\item Recent Activities

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Business User Interface Requirements}

\paragraph{BUI-001 Dashboard}

The application shall display a personalized business dashboard after
successful authentication.

\paragraph{BUI-002 Organization Profile}

The dashboard shall display organization information.

\paragraph{BUI-003 Sustainability Metrics}

The dashboard shall summarize environmental sustainability metrics.

\paragraph{BUI-004 Inventory Summary}

The dashboard shall display organizational electronic asset summaries.

\paragraph{BUI-005 Pending Pickups}

The dashboard shall display pending pickup requests.

\paragraph{BUI-006 Quick Actions}

The dashboard shall provide shortcuts to frequently used business
operations.

\paragraph{BUI-007 Notifications}

Unread business notifications shall be displayed prominently.

\paragraph{BUI-008 Analytics}

The dashboard shall display graphical analytics.

\paragraph{BUI-009 Reports}

The dashboard shall provide shortcuts to compliance reports.

\paragraph{BUI-010 Activity Feed}

The dashboard shall display recent organizational activities.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Asset Management Interface}

\paragraph{BUI-011 Asset Registration}

Organizations shall register electronic assets.

\paragraph{BUI-012 Asset Categories}

The application shall support multiple asset categories.

\paragraph{BUI-013 Asset Search}

Users shall search registered assets.

\paragraph{BUI-014 Asset Details}

The application shall display detailed asset information.

\paragraph{BUI-015 Asset Status}

Users shall monitor asset lifecycle status.

\paragraph{BUI-016 Asset Images}

The application shall support uploading asset photographs.

\paragraph{BUI-017 Asset QR Code}

Each asset shall receive a unique QR Code.

\paragraph{BUI-018 Asset Barcode}

The system shall support barcode identification.

\paragraph{BUI-019 Asset History}

The application shall maintain complete asset history.

\paragraph{BUI-020 Asset Disposal}

Organizations shall initiate disposal requests for registered assets.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Bulk Pickup Interface}

\paragraph{BUI-021 Bulk Pickup Request}

The application shall allow organizations to submit bulk electronic
waste pickup requests.

\paragraph{BUI-022 Multiple Assets}

Organizations shall include multiple electronic assets within a single
pickup request.

\paragraph{BUI-023 Pickup Location}

Organizations shall select one or more approved pickup locations.

\paragraph{BUI-024 Pickup Schedule}

The application shall allow selection of preferred collection dates and
time windows.

\paragraph{BUI-025 Pickup Priority}

Authorized users shall specify pickup priority where applicable.

\paragraph{BUI-026 Supporting Documents}

Organizations shall upload supporting documentation for pickup requests.

\paragraph{BUI-027 Pickup Confirmation}

The application shall display a pickup confirmation summary before
submission.

\paragraph{BUI-028 Pickup Tracking}

Organizations shall monitor pickup progress in real time.

\paragraph{BUI-029 Pickup History}

The application shall maintain complete organizational pickup history.

\paragraph{BUI-030 Digital Collection Certificate}

The application shall generate digital collection certificates after
successful pickups.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Artificial Intelligence Interface}

\paragraph{BUI-031 AI Asset Identification}

The application shall provide AI-assisted identification of electronic
equipment.

\paragraph{BUI-032 Image Capture}

Users shall capture equipment images using the device camera.

\paragraph{BUI-033 Gallery Upload}

Users shall upload existing equipment photographs.

\paragraph{BUI-034 Image Preview}

The application shall preview uploaded images before AI analysis.

\paragraph{BUI-035 AI Classification}

The application shall classify electronic equipment using the deployed
AI model.

\paragraph{BUI-036 Confidence Score}

The AI prediction shall include a confidence score.

\paragraph{BUI-037 Hazard Classification}

The AI service shall identify hazardous electronic waste where
applicable.

\paragraph{BUI-038 Recycling Recommendation}

The application shall recommend suitable recycling methods.

\paragraph{BUI-039 Refurbishment Recommendation}

Where appropriate, the AI service shall recommend refurbishment instead
of recycling.

\paragraph{BUI-040 Save Analysis}

Organizations shall save AI analysis results for future reference.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Compliance and Reporting Interface}

\paragraph{BUI-041 Compliance Dashboard}

The application shall provide an organizational compliance dashboard.

\paragraph{BUI-042 Environmental Reports}

Organizations shall generate environmental compliance reports.

\paragraph{BUI-043 Recycling Certificates}

The application shall display issued recycling certificates.

\paragraph{BUI-044 Collection Certificates}

The application shall display electronic waste collection certificates.

\paragraph{BUI-045 Carbon Reduction Reports}

The application shall display carbon reduction reports.

\paragraph{BUI-046 Sustainability Reports}

Organizations shall generate sustainability performance reports.

\paragraph{BUI-047 Export Reports}

Reports shall be exportable in PDF format.

\paragraph{BUI-048 Report Filtering}

Reports shall support filtering by reporting period.

\paragraph{BUI-049 Report Sharing}

Authorized users shall securely share reports.

\paragraph{BUI-050 Compliance Alerts}

The application shall notify organizations of compliance deadlines.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Marketplace Interface}

\paragraph{BUI-051 Marketplace Access}

Organizations shall access the EcoTrace marketplace.

\paragraph{BUI-052 Product Catalogue}

The marketplace shall display available refurbished products.

\paragraph{BUI-053 Product Search}

Organizations shall search marketplace products.

\paragraph{BUI-054 Product Filters}

The marketplace shall support advanced product filtering.

\paragraph{BUI-055 Product Details}

Detailed product specifications shall be displayed.

\paragraph{BUI-056 Quotation Request}

Organizations shall request quotations for large purchases.

\paragraph{BUI-057 Bulk Purchase}

The marketplace shall support bulk purchasing.

\paragraph{BUI-058 Order Tracking}

Organizations shall monitor order progress.

\paragraph{BUI-059 Purchase History}

The application shall maintain organizational purchase history.

\paragraph{BUI-060 Marketplace Notifications}

Organizations shall receive marketplace notifications.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Organization Management Interface}

\paragraph{BUI-061 Organization Profile}

Authorized users shall manage organizational profiles.

\paragraph{BUI-062 Branch Management}

Organizations shall manage multiple branches.

\paragraph{BUI-063 User Management}

Organization administrators shall manage organization users.

\paragraph{BUI-064 Role Assignment}

Organization administrators shall assign organizational roles.

\paragraph{BUI-065 Department Management}

Organizations shall manage organizational departments.

\paragraph{BUI-066 Contact Directory}

The application shall maintain organization contact information.

\paragraph{BUI-067 Organization Settings}

Authorized users shall configure organization settings.

\paragraph{BUI-068 Notification Preferences}

Organizations shall configure notification preferences.

\paragraph{BUI-069 Organization Security}

Organization administrators shall configure security preferences.

\paragraph{BUI-070 Organization Audit}

Administrative organization activities shall be recorded by the Audit
Trail and Activity Logging Module.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Settings Interface}

\paragraph{BUI-071 Theme Selection}

Authorized users shall switch between Light Mode and Dark Mode.

\paragraph{BUI-072 Language}

The application shall support configurable language preferences.

\paragraph{BUI-073 Regional Settings}

Organizations shall configure regional settings.

\paragraph{BUI-074 Time Zone}

Users shall configure organizational time zones.

\paragraph{BUI-075 Date Format}

Users shall configure preferred date formats.

\paragraph{BUI-076 Notification Settings}

Organizations shall configure notification preferences.

\paragraph{BUI-077 Data Synchronization}

The application shall support synchronization preferences.

\paragraph{BUI-078 Security Preferences}

Organizations shall configure application security settings.

\paragraph{BUI-079 Privacy Settings}

Authorized users shall configure organizational privacy settings.

\paragraph{BUI-080 Restore Defaults}

The application shall allow restoration of default settings.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Help and Support Interface}

\paragraph{BUI-081 Help Centre}

The application shall provide a business help centre.

\paragraph{BUI-082 Frequently Asked Questions}

Users shall access business-related frequently asked questions.

\paragraph{BUI-083 User Manual}

The application shall provide a digital user manual.

\paragraph{BUI-084 Contact Support}

Authorized users shall contact EcoTrace support services.

\paragraph{BUI-085 Live Chat}

The application shall support live customer support where available.

\paragraph{BUI-086 Ticket Submission}

Organizations shall submit technical support tickets.

\paragraph{BUI-087 Ticket Tracking}

Organizations shall monitor support ticket status.

\paragraph{BUI-088 Feedback Submission}

Organizations shall submit suggestions and feedback.

\paragraph{BUI-089 Training Materials}

The application shall provide training materials and tutorials.

\paragraph{BUI-090 Application Information}

Users shall access application version and licensing information.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Security Interface}

\paragraph{BUI-091 Secure Authentication}

The application shall require secure authentication before granting
access.

\paragraph{BUI-092 Multi-Factor Authentication}

The application shall support multi-factor authentication.

\paragraph{BUI-093 Session Timeout}

Inactive sessions shall automatically expire according to configured
security policies.

\paragraph{BUI-094 Device Registration}

Organizations shall manage trusted devices.

\paragraph{BUI-095 Session Management}

Users shall review active login sessions.

\paragraph{BUI-096 Password Management}

Users shall securely change passwords.

\paragraph{BUI-097 Secure Document Access}

Protected organizational documents shall require authorization before
access.

\paragraph{BUI-098 Secure Downloads}

Downloaded compliance documents shall comply with organizational
security policies.

\paragraph{BUI-099 Audit Logging}

Critical user activities shall be recorded by the Audit Trail and
Activity Logging Module.

\paragraph{BUI-100 Data Privacy}

The application shall protect organizational information according to
configured privacy policies.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Offline Operation}

\paragraph{BUI-101 Offline Viewing}

Previously synchronized information shall remain available while
offline.

\paragraph{BUI-102 Offline Pickup Registration}

Authorized users shall prepare pickup requests while offline.

\paragraph{BUI-103 Offline Asset Registration}

The application shall support offline asset registration.

\paragraph{BUI-104 Offline Image Capture}

Users shall capture equipment images without network connectivity.

\paragraph{BUI-105 Offline Queue}

Offline transactions shall be stored in a synchronization queue.

\paragraph{BUI-106 Automatic Synchronization}

Queued transactions shall synchronize automatically when network
connectivity is restored.

\paragraph{BUI-107 Synchronization Status}

The application shall display synchronization progress.

\paragraph{BUI-108 Conflict Resolution}

The system shall detect synchronization conflicts.

\paragraph{BUI-109 Synchronization Retry}

Failed synchronization attempts shall automatically retry according to
configured policies.

\paragraph{BUI-110 Offline Audit}

Offline activities shall be audited after synchronization.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Validation Rules}

\begin{itemize}

\item Only authenticated organization users shall access business
functions.

\item Organization administrators shall manage organizational settings.

\item Mandatory asset information shall be completed before registration.

\item Pickup requests shall contain valid organizational information.

\item Compliance reports shall be generated only from authorized data.

\item AI analysis shall require valid electronic equipment images.

\item Marketplace purchases shall require successful payment
authorization.

\item Offline transactions shall synchronize successfully before final
processing.

\item Organization security settings shall comply with configured
security policies.

\item All business operations shall be recorded by the Audit Trail and
Activity Logging Module.

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Acceptance Criteria}

\paragraph{BAC-001}

Organizations can successfully manage electronic assets.

\paragraph{BAC-002}

Bulk pickup requests can be scheduled and tracked.

\paragraph{BAC-003}

AI successfully identifies electronic equipment.

\paragraph{BAC-004}

Compliance reports are generated accurately.

\paragraph{BAC-005}

Organizations can securely purchase refurbished equipment.

\paragraph{BAC-006}

Offline functionality synchronizes successfully after connectivity is
restored.

\paragraph{BAC-007}

Organization administrators can manage users and organizational
settings.

\paragraph{BAC-008}

Environmental performance metrics are accurately displayed.

\paragraph{BAC-009}

Business activities are securely audited.

\paragraph{BAC-010}

The Business Mobile Application provides a secure, scalable, and
enterprise-grade interface for organizational participation in the
EcoTrace platform.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Collector Mobile Application}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Purpose}

The Collector Mobile Application shall provide authorized electronic
waste collectors with a secure, efficient, and field-oriented interface
for managing daily collection operations. The application shall enable
collectors to receive assigned pickup requests, navigate to customer
locations, verify electronic waste, record collection activities,
capture photographic evidence, collect digital signatures, communicate
with dispatch personnel, and synchronize operational data with the
EcoTrace cloud platform.

The application shall support both online and offline operation to
ensure uninterrupted field activities in areas with limited network
connectivity.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Primary Users}

\begin{itemize}

\item Electronic Waste Collectors

\item Field Collection Officers

\item Collection Supervisors

\item Dispatch Coordinators

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Main Navigation}

The Collector Mobile Application shall provide the following navigation
menu:

\begin{itemize}

\item Dashboard

\item Assigned Pickups

\item Route Navigation

\item Scan Device

\item Collection History

\item Notifications

\item Messages

\item Profile

\item Settings

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Collector Dashboard Components}

The dashboard shall display:

\begin{itemize}

\item Collector Profile

\item Today's Assigned Jobs

\item Completed Pickups

\item Pending Pickups

\item Route Summary

\item Vehicle Assignment

\item Performance Statistics

\item Collection Targets

\item Notifications

\item Quick Actions

\item GPS Status

\item Network Status

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Collector User Interface Requirements}

\paragraph{CUI-001 Dashboard}

The application shall display a personalized collector dashboard after
successful authentication.

\paragraph{CUI-002 Assigned Jobs}

The dashboard shall display today's assigned pickup requests.

\paragraph{CUI-003 Job Summary}

The dashboard shall summarize completed, pending, and overdue pickup
tasks.

\paragraph{CUI-004 Route Summary}

The application shall display today's collection route summary.

\paragraph{CUI-005 Vehicle Assignment}

The application shall display the assigned collection vehicle.

\paragraph{CUI-006 Performance Summary}

The dashboard shall display collector performance statistics.

\paragraph{CUI-007 Notification Indicator}

Unread operational notifications shall be prominently displayed.

\paragraph{CUI-008 GPS Status}

The application shall display current GPS connectivity status.

\paragraph{CUI-009 Synchronization Status}

The application shall display cloud synchronization status.

\paragraph{CUI-010 Quick Actions}

The dashboard shall provide shortcuts to frequently used collection
operations.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Assigned Pickup Interface}

\paragraph{CUI-011 Pickup List}

Collectors shall view all assigned pickup requests.

\paragraph{CUI-012 Pickup Details}

The application shall display complete pickup information.

\paragraph{CUI-013 Customer Information}

The application shall display customer contact details.

\paragraph{CUI-014 Pickup Address}

The application shall display pickup location information.

\paragraph{CUI-015 GPS Navigation}

Collectors shall launch GPS navigation directly from the pickup record.

\paragraph{CUI-016 Route Optimization}

The application shall display optimized collection routes.

\paragraph{CUI-017 Pickup Status}

Collectors shall update pickup status throughout the collection process.

\paragraph{CUI-018 Arrival Confirmation}

Collectors shall confirm arrival at the pickup location.

\paragraph{CUI-019 Collection Start}

Collectors shall record the start of collection activities.

\paragraph{CUI-020 Collection Completion}

Collectors shall record successful completion of pickups.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Electronic Waste Verification Interface}

\paragraph{CUI-021 QR Code Scanner}

The application shall allow collectors to scan QR codes attached to
registered electronic assets.

\paragraph{CUI-022 Barcode Scanner}

The application shall support barcode scanning for asset verification.

\paragraph{CUI-023 Asset Verification}

The application shall verify scanned assets against the EcoTrace
database.

\paragraph{CUI-024 Asset Details}

The application shall display complete asset information after
successful verification.

\paragraph{CUI-025 Unregistered Asset}

The application shall allow registration of previously unregistered
electronic waste.

\paragraph{CUI-026 AI Verification}

Collectors shall use AI-assisted identification for unknown electronic
devices.

\paragraph{CUI-027 Hazard Identification}

The application shall identify hazardous electronic waste where
applicable.

\paragraph{CUI-028 Duplicate Detection}

The application shall detect duplicate asset registrations.

\paragraph{CUI-029 Asset Condition}

Collectors shall record the physical condition of collected items.

\paragraph{CUI-030 Verification Confirmation}

The application shall require verification confirmation before
continuing the collection process.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Collection Evidence Interface}

\paragraph{CUI-031 Image Capture}

Collectors shall capture photographs before collection.

\paragraph{CUI-032 Multiple Images}

The application shall support multiple photographs per collection.

\paragraph{CUI-033 Image Preview}

Captured photographs shall be previewed before submission.

\paragraph{CUI-034 Image Retake}

Collectors shall retake photographs when necessary.

\paragraph{CUI-035 Automatic Timestamp}

Collection photographs shall include automatic timestamps.

\paragraph{CUI-036 GPS Coordinates}

Collection photographs shall include GPS coordinates.

\paragraph{CUI-037 Digital Signature}

Customers shall provide digital signatures confirming collection.

\paragraph{CUI-038 Collector Signature}

Collectors shall digitally sign completed collection records.

\paragraph{CUI-039 Supporting Documents}

Collectors shall attach supporting documents where required.

\paragraph{CUI-040 Collection Receipt}

The application shall generate a digital collection receipt.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Incident Reporting Interface}

\paragraph{CUI-041 Incident Registration}

Collectors shall report operational incidents.

\paragraph{CUI-042 Incident Categories}

The application shall support standardized incident categories.

\paragraph{CUI-043 Incident Description}

Collectors shall provide detailed incident descriptions.

\paragraph{CUI-044 Incident Images}

Collectors shall upload supporting photographs.

\paragraph{CUI-045 Incident Location}

The application shall record incident GPS coordinates.

\paragraph{CUI-046 Incident Priority}

Collectors shall assign incident priority levels.

\paragraph{CUI-047 Supervisor Notification}

Supervisors shall receive incident notifications.

\paragraph{CUI-048 Emergency Reporting}

Emergency incidents shall be reported immediately.

\paragraph{CUI-049 Incident Tracking}

Collectors shall monitor incident resolution status.

\paragraph{CUI-050 Incident History}

The application shall maintain complete incident history.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Communication Interface}

\paragraph{CUI-051 Dispatch Communication}

Collectors shall communicate with dispatch personnel.

\paragraph{CUI-052 Driver Communication}

Collectors shall communicate with assigned drivers.

\paragraph{CUI-053 Customer Communication}

Collectors shall contact customers directly from pickup records.

\paragraph{CUI-054 Internal Messaging}

The application shall provide secure internal messaging.

\paragraph{CUI-055 Broadcast Messages}

Administrators shall broadcast operational announcements.

\paragraph{CUI-056 Notification Centre}

Collectors shall receive operational notifications.

\paragraph{CUI-057 Read Confirmation}

The application shall identify read and unread messages.

\paragraph{CUI-058 Attachment Support}

Messages shall support file attachments.

\paragraph{CUI-059 Offline Messaging}

Messages created offline shall synchronize automatically.

\paragraph{CUI-060 Communication History}

The application shall maintain communication history.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Offline Operation Interface}

\paragraph{CUI-061 Offline Mode}

The application shall support offline operation during field collection
activities.

\paragraph{CUI-062 Offline Authentication}

Previously authenticated collectors shall continue working while
offline.

\paragraph{CUI-063 Offline Pickup List}

Assigned pickup jobs shall remain accessible without Internet
connectivity.

\paragraph{CUI-064 Offline Data Capture}

Collectors shall capture collection data while offline.

\paragraph{CUI-065 Offline Image Storage}

Collection photographs shall be securely stored locally until
synchronization.

\paragraph{CUI-066 Offline Signature}

Customer digital signatures shall be captured while offline.

\paragraph{CUI-067 Offline QR Verification}

Previously synchronized QR records shall remain available for
verification.

\paragraph{CUI-068 Synchronization Queue}

Offline transactions shall be placed in a synchronization queue.

\paragraph{CUI-069 Automatic Synchronization}

The application shall automatically synchronize queued data when
network connectivity is restored.

\paragraph{CUI-070 Synchronization Report}

Collectors shall view synchronization status and history.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Vehicle Interface}

\paragraph{CUI-071 Assigned Vehicle}

The application shall display assigned vehicle information.

\paragraph{CUI-072 Vehicle Status}

Collectors shall monitor vehicle operational status.

\paragraph{CUI-073 Vehicle Capacity}

The application shall display available vehicle capacity.

\paragraph{CUI-074 Vehicle Inspection}

Collectors shall complete pre-collection vehicle inspections.

\paragraph{CUI-075 Fuel Status}

The application shall display fuel status where integrated.

\paragraph{CUI-076 Route Assignment}

Collectors shall receive assigned collection routes.

\paragraph{CUI-077 Route Completion}

Collectors shall confirm completion of assigned routes.

\paragraph{CUI-078 Vehicle Incident}

Collectors shall report vehicle incidents.

\paragraph{CUI-079 Vehicle Maintenance}

Collectors shall report maintenance requirements.

\paragraph{CUI-080 Vehicle Handover}

Collectors shall record vehicle handover information where applicable.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Settings Interface}

\paragraph{CUI-081 Theme}

Collectors shall switch between Light Mode and Dark Mode.

\paragraph{CUI-082 Language}

Collectors shall configure preferred language settings.

\paragraph{CUI-083 Notification Preferences}

Collectors shall configure notification preferences.

\paragraph{CUI-084 GPS Permission}

Collectors shall manage GPS permissions.

\paragraph{CUI-085 Camera Permission}

Collectors shall manage camera permissions.

\paragraph{CUI-086 Storage Permission}

Collectors shall manage storage permissions.

\paragraph{CUI-087 Synchronization Settings}

Collectors shall configure synchronization preferences.

\paragraph{CUI-088 Security Settings}

Collectors shall manage security preferences.

\paragraph{CUI-089 Application Information}

The application shall display application version information.

\paragraph{CUI-090 Restore Default Settings}

Collectors shall restore default application settings.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Help and Support Interface}

\paragraph{CUI-091 Help Centre}

The application shall provide an integrated help centre.

\paragraph{CUI-092 User Manual}

Collectors shall access a digital user manual.

\paragraph{CUI-093 Frequently Asked Questions}

The application shall provide frequently asked questions.

\paragraph{CUI-094 Contact Supervisor}

Collectors shall contact assigned supervisors.

\paragraph{CUI-095 Technical Support}

Collectors shall report technical problems.

\paragraph{CUI-096 Support Tickets}

Collectors shall submit support tickets.

\paragraph{CUI-097 Ticket Tracking}

Collectors shall monitor support ticket progress.

\paragraph{CUI-098 Feedback}

Collectors shall submit operational feedback.

\paragraph{CUI-099 Emergency Contacts}

Emergency contact information shall be available.

\paragraph{CUI-100 About EcoTrace}

The application shall provide information about EcoTrace.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Validation Rules}

\begin{itemize}

\item Collectors shall authenticate before accessing operational data.

\item Pickup completion shall require customer verification.

\item Collection photographs shall be attached before completing
collection where required.

\item GPS location shall be recorded for completed pickups.

\item QR or barcode verification shall be completed when applicable.

\item Offline records shall synchronize successfully before permanent
storage.

\item Digital signatures shall be validated before submission.

\item Incident reports shall contain mandatory information.

\item Unauthorized users shall not access collector functions.

\item All collector activities shall be recorded by the Audit Trail and
Activity Logging Module.

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Acceptance Criteria}

\paragraph{CAC-001}

Collectors can successfully receive assigned pickup jobs.

\paragraph{CAC-002}

Collectors can navigate to customer locations using integrated GPS.

\paragraph{CAC-003}

Electronic waste can be verified using QR codes, barcodes, or AI
identification.

\paragraph{CAC-004}

Collection evidence, including photographs and digital signatures, is
captured successfully.

\paragraph{CAC-005}

Offline collection activities synchronize automatically after network
connectivity is restored.

\paragraph{CAC-006}

Operational incidents can be reported and tracked.

\paragraph{CAC-007}

Collectors can communicate securely with dispatch personnel and
supervisors.

\paragraph{CAC-008}

Vehicle information and collection routes are accurately displayed.

\paragraph{CAC-009}

All operational activities are securely audited.

\paragraph{CAC-010}

The Collector Mobile Application provides a secure, efficient, and
field-ready interface for electronic waste collection operations.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Driver Mobile Application}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Purpose}

The Driver Mobile Application shall provide authorized EcoTrace drivers
with a secure, efficient, and field-oriented interface for transporting
electronic waste between collection locations, transfer stations,
warehouses, repair centres, refurbishment facilities, recycling plants,
and approved disposal facilities.

The application shall support route navigation, vehicle inspections,
trip management, load tracking, proof of delivery, fuel monitoring,
vehicle maintenance reporting, communication with dispatch personnel,
and offline operation. The application shall be developed using Flutter
and shall operate on Android devices.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Primary Users}

\begin{itemize}

\item Drivers

\item Fleet Drivers

\item Fleet Supervisors

\item Dispatch Coordinators

\item Transport Managers

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Main Navigation}

The Driver Mobile Application shall provide the following navigation
menu:

\begin{itemize}

\item Dashboard

\item Assigned Trips

\item Route Navigation

\item Vehicle

\item Deliveries

\item Notifications

\item Messages

\item Profile

\item Settings

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Driver Dashboard Components}

The dashboard shall include:

\begin{itemize}

\item Driver Profile

\item Assigned Trips

\item Today's Schedule

\item Vehicle Summary

\item Route Summary

\item Fuel Status

\item Load Summary

\item Delivery Status

\item Performance Summary

\item Notifications

\item GPS Status

\item Synchronization Status

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Driver User Interface Requirements}

\paragraph{DUI-001 Dashboard}

The application shall display a personalized driver dashboard after
successful authentication.

\paragraph{DUI-002 Assigned Trips}

The dashboard shall display all assigned transport jobs.

\paragraph{DUI-003 Trip Summary}

The dashboard shall summarize completed, active, and scheduled trips.

\paragraph{DUI-004 Vehicle Summary}

The dashboard shall display assigned vehicle information.

\paragraph{DUI-005 Route Summary}

The dashboard shall display today's assigned transportation route.

\paragraph{DUI-006 Fuel Summary}

The dashboard shall display current vehicle fuel status where available.

\paragraph{DUI-007 Delivery Summary}

The dashboard shall summarize completed and pending deliveries.

\paragraph{DUI-008 Notifications}

Unread operational notifications shall be displayed prominently.

\paragraph{DUI-009 GPS Status}

The dashboard shall display GPS connectivity status.

\paragraph{DUI-010 Synchronization Status}

The dashboard shall display cloud synchronization status.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Trip Management Interface}

\paragraph{DUI-011 Assigned Trips}

Drivers shall access assigned transportation jobs.

\paragraph{DUI-012 Trip Details}

The application shall display complete trip information.

\paragraph{DUI-013 Pickup Location}

Drivers shall view collection locations.

\paragraph{DUI-014 Destination}

Drivers shall view delivery destinations.

\paragraph{DUI-015 Route Navigation}

The application shall launch GPS navigation.

\paragraph{DUI-016 Route Optimization}

The application shall display optimized transportation routes.

\paragraph{DUI-017 Trip Start}

Drivers shall confirm trip commencement.

\paragraph{DUI-018 Trip Progress}

The application shall display trip progress.

\paragraph{DUI-019 Trip Completion}

Drivers shall confirm successful completion of assigned trips.

\paragraph{DUI-020 Trip History}

The application shall maintain complete transportation history.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Vehicle Inspection Interface}

\paragraph{DUI-021 Pre-Trip Inspection}

Drivers shall complete a pre-trip vehicle inspection before commencing
any assigned trip.

\paragraph{DUI-022 Inspection Checklist}

The application shall display a standardized vehicle inspection
checklist.

\paragraph{DUI-023 Brake Inspection}

Drivers shall record the operational status of the braking system.

\paragraph{DUI-024 Tire Inspection}

Drivers shall inspect and record tire condition.

\paragraph{DUI-025 Lighting Inspection}

Drivers shall verify vehicle lights before departure.

\paragraph{DUI-026 Fuel Level}

Drivers shall record the current fuel level before starting a trip.

\paragraph{DUI-027 Battery Status}

The application shall allow recording of vehicle battery condition.

\paragraph{DUI-028 Vehicle Images}

Drivers shall capture photographs of vehicle condition where required.

\paragraph{DUI-029 Inspection Approval}

Vehicle inspections shall require confirmation before trip initiation.

\paragraph{DUI-030 Inspection History}

The application shall maintain historical inspection records.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Load Management Interface}

\paragraph{DUI-031 Load Assignment}

Drivers shall view assigned electronic waste loads.

\paragraph{DUI-032 Load Details}

The application shall display complete load information.

\paragraph{DUI-033 Load Weight}

The application shall display estimated and actual load weight.

\paragraph{DUI-034 Load Capacity}

Drivers shall monitor remaining vehicle carrying capacity.

\paragraph{DUI-035 Load Verification}

Drivers shall verify collected electronic waste before transport.

\paragraph{DUI-036 QR Verification}

Drivers shall scan QR codes before accepting loads.

\paragraph{DUI-037 Barcode Verification}

Drivers shall scan barcodes where applicable.

\paragraph{DUI-038 Load Images}

Drivers shall capture photographs of transported loads.

\paragraph{DUI-039 Hazardous Load}

Hazardous electronic waste shall be clearly identified.

\paragraph{DUI-040 Load Confirmation}

Drivers shall confirm load acceptance before departure.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Navigation Interface}

\paragraph{DUI-041 GPS Navigation}

The application shall provide turn-by-turn GPS navigation.

\paragraph{DUI-042 Route Optimization}

The navigation system shall recommend the most efficient route.

\paragraph{DUI-043 Traffic Information}

The application shall display real-time traffic information where
available.

\paragraph{DUI-044 Route Recalculation}

Navigation routes shall automatically recalculate when drivers deviate
from the planned route.

\paragraph{DUI-045 Estimated Arrival Time}

The application shall display estimated arrival times.

\paragraph{DUI-046 Distance Remaining}

Drivers shall view remaining travel distance.

\paragraph{DUI-047 Destination Confirmation}

Drivers shall confirm arrival at destination.

\paragraph{DUI-048 Route History}

Completed routes shall be retained for reporting purposes.

\paragraph{DUI-049 Offline Navigation}

Previously downloaded routes shall remain available during temporary
network interruptions.

\paragraph{DUI-050 Location Sharing}

Drivers shall securely share their real-time location with authorized
dispatch personnel.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Delivery Verification Interface}

\paragraph{DUI-051 Delivery Confirmation}

Drivers shall confirm successful delivery of electronic waste.

\paragraph{DUI-052 Receiving Officer}

The application shall record receiving officer information.

\paragraph{DUI-053 Digital Signature}

Receiving personnel shall provide a digital signature.

\paragraph{DUI-054 Delivery Images}

Drivers shall capture delivery photographs.

\paragraph{DUI-055 Timestamp}

Delivery confirmation shall include an automatic timestamp.

\paragraph{DUI-056 GPS Coordinates}

Delivery confirmation shall include GPS coordinates.

\paragraph{DUI-057 Delivery Receipt}

The application shall generate a digital delivery receipt.

\paragraph{DUI-058 Delivery Status}

Drivers shall update delivery status throughout transportation.

\paragraph{DUI-059 Delivery History}

The application shall maintain complete delivery history.

\paragraph{DUI-060 Exception Reporting}

Drivers shall report delivery exceptions immediately.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Fuel Management Interface}

\paragraph{DUI-061 Fuel Monitoring}

The application shall display current vehicle fuel information where
available.

\paragraph{DUI-062 Fuel Consumption}

The application shall calculate fuel consumption for each completed
trip.

\paragraph{DUI-063 Fuel Refill}

Drivers shall record fuel refill transactions.

\paragraph{DUI-064 Fuel Receipt}

Drivers shall upload photographs of fuel receipts where required.

\paragraph{DUI-065 Fuel Cost}

The application shall record fuel expenditure.

\paragraph{DUI-066 Fuel History}

The application shall maintain historical fuel records.

\paragraph{DUI-067 Fuel Alerts}

The application shall notify drivers when fuel levels fall below
configured thresholds.

\paragraph{DUI-068 Fuel Analytics}

Drivers shall view fuel usage statistics.

\paragraph{DUI-069 Fuel Approval}

Fuel reimbursement requests shall support approval workflows.

\paragraph{DUI-070 Fuel Reports}

The application shall generate fuel consumption reports.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Vehicle Maintenance Interface}

\paragraph{DUI-071 Maintenance Reporting}

Drivers shall report vehicle maintenance issues.

\paragraph{DUI-072 Fault Categories}

The application shall provide standardized maintenance categories.

\paragraph{DUI-073 Fault Description}

Drivers shall enter detailed maintenance descriptions.

\paragraph{DUI-074 Maintenance Images}

Drivers shall upload supporting maintenance photographs.

\paragraph{DUI-075 Urgency Level}

Maintenance requests shall support priority levels.

\paragraph{DUI-076 Maintenance History}

The application shall maintain vehicle maintenance history.

\paragraph{DUI-077 Maintenance Status}

Drivers shall monitor maintenance progress.

\paragraph{DUI-078 Workshop Assignment}

The application shall display assigned maintenance workshops where
applicable.

\paragraph{DUI-079 Vehicle Availability}

Vehicle availability shall be updated after maintenance reporting.

\paragraph{DUI-080 Maintenance Notifications}

Drivers shall receive maintenance status notifications.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Communication Interface}

\paragraph{DUI-081 Dispatch Communication}

Drivers shall securely communicate with dispatch personnel.

\paragraph{DUI-082 Collector Communication}

Drivers shall communicate with assigned collectors.

\paragraph{DUI-083 Supervisor Communication}

Drivers shall contact transport supervisors.

\paragraph{DUI-084 Internal Messaging}

The application shall support secure internal messaging.

\paragraph{DUI-085 Broadcast Messages}

Administrators shall distribute operational announcements.

\paragraph{DUI-086 Notifications}

Drivers shall receive operational notifications.

\paragraph{DUI-087 Attachment Support}

Messages shall support document and image attachments.

\paragraph{DUI-088 Emergency Communication}

Drivers shall immediately notify dispatch of emergency situations.

\paragraph{DUI-089 Message History}

The application shall maintain communication history.

\paragraph{DUI-090 Read Status}

The application shall distinguish between read and unread messages.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Offline Operation}

\paragraph{DUI-091 Offline Mode}

The application shall support offline operation.

\paragraph{DUI-092 Offline Trip Access}

Previously synchronized trips shall remain available while offline.

\paragraph{DUI-093 Offline Navigation}

Previously downloaded navigation routes shall remain available.

\paragraph{DUI-094 Offline Delivery Recording}

Drivers shall record deliveries while offline.

\paragraph{DUI-095 Offline Image Storage}

Delivery photographs shall be stored securely until synchronization.

\paragraph{DUI-096 Offline Queue}

Offline transactions shall be queued for synchronization.

\paragraph{DUI-097 Automatic Synchronization}

The application shall synchronize offline records automatically after
network connectivity is restored.

\paragraph{DUI-098 Synchronization Status}

Drivers shall monitor synchronization progress.

\paragraph{DUI-099 Conflict Resolution}

Synchronization conflicts shall be detected and resolved according to
configured business rules.

\paragraph{DUI-100 Offline Audit}

Offline activities shall be audited after successful synchronization.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Settings Interface}

\paragraph{DUI-101 Theme}

Drivers shall switch between Light Mode and Dark Mode.

\paragraph{DUI-102 Language}

Drivers shall configure preferred application language.

\paragraph{DUI-103 Notification Preferences}

Drivers shall manage notification preferences.

\paragraph{DUI-104 GPS Permission}

Drivers shall manage GPS permissions.

\paragraph{DUI-105 Camera Permission}

Drivers shall manage camera permissions.

\paragraph{DUI-106 Storage Permission}

Drivers shall manage storage permissions.

\paragraph{DUI-107 Synchronization Preferences}

Drivers shall configure synchronization settings.

\paragraph{DUI-108 Security Settings}

Drivers shall configure application security settings.

\paragraph{DUI-109 Application Information}

The application shall display version and licensing information.

\paragraph{DUI-110 Restore Defaults}

Drivers shall restore default application settings.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Validation Rules}

\begin{itemize}

\item Drivers shall authenticate before accessing transportation
functions.

\item Vehicle inspections shall be completed before trip commencement.

\item Electronic waste loads shall be verified before transport.

\item Delivery confirmation shall require GPS location and timestamp.

\item Digital signatures shall be captured where required.

\item Vehicle maintenance reports shall contain mandatory information.

\item Offline transactions shall synchronize successfully before final
processing.

\item Unauthorized users shall not access driver functions.

\item Transportation records shall remain tamper-resistant after
submission.

\item All transportation activities shall be recorded by the Audit Trail
and Activity Logging Module.

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Acceptance Criteria}

\paragraph{DAC-001}

Drivers can successfully receive and complete assigned transport jobs.

\paragraph{DAC-002}

Vehicle inspections are completed before each trip.

\paragraph{DAC-003}

Electronic waste loads are verified before transportation.

\paragraph{DAC-004}

Drivers navigate successfully using integrated GPS.

\paragraph{DAC-005}

Deliveries are confirmed using photographs, GPS coordinates,
timestamps, and digital signatures.

\paragraph{DAC-006}

Vehicle maintenance issues are reported successfully.

\paragraph{DAC-007}

Offline transportation activities synchronize automatically after
network connectivity is restored.

\paragraph{DAC-008}

Operational communications function securely.

\paragraph{DAC-009}

Transportation activities are completely auditable.

\paragraph{DAC-010}

The Driver Mobile Application provides a secure, reliable, and
enterprise-grade interface for transportation and logistics operations
within the EcoTrace platform.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Technician Mobile Application}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Purpose}

The Technician Mobile Application shall provide authorized EcoTrace
technicians with a secure and comprehensive interface for inspecting,
diagnosing, repairing, refurbishing, testing, certifying, and
documenting electronic equipment received through the EcoTrace platform.

The application shall support repair workflows, spare parts management,
quality assurance, refurbishment assessment, diagnostic reporting,
maintenance history, repair certification, inventory integration,
communication with supervisors, and offline operation. The application
shall be developed using Flutter and optimized for Android devices used
in repair workshops and refurbishment centres.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Primary Users}

\begin{itemize}

\item Repair Technicians

\item Refurbishment Technicians

\item Electronics Engineers

\item Workshop Supervisors

\item Quality Assurance Inspectors

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Main Navigation}

The Technician Mobile Application shall provide the following navigation
menu:

\begin{itemize}

\item Dashboard

\item Assigned Jobs

\item Diagnostics

\item Repairs

\item Spare Parts

\item Quality Inspection

\item Notifications

\item Messages

\item Profile

\item Settings

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Technician Dashboard Components}

The dashboard shall display:

\begin{itemize}

\item Technician Profile

\item Assigned Repair Jobs

\item Pending Diagnostics

\item Active Repairs

\item Completed Repairs

\item Spare Parts Summary

\item Quality Inspection Queue

\item Performance Statistics

\item Notifications

\item Workshop Announcements

\item Synchronization Status

\item Quick Actions

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Technician User Interface Requirements}

\paragraph{TUI-001 Dashboard}

The application shall display a personalized technician dashboard after
successful authentication.

\paragraph{TUI-002 Assigned Jobs}

The dashboard shall display assigned repair and refurbishment jobs.

\paragraph{TUI-003 Diagnostic Queue}

The dashboard shall display pending diagnostic tasks.

\paragraph{TUI-004 Repair Queue}

The dashboard shall display active repair tasks.

\paragraph{TUI-005 Completed Jobs}

The dashboard shall summarize completed repairs.

\paragraph{TUI-006 Performance Summary}

The dashboard shall display technician performance indicators.

\paragraph{TUI-007 Notifications}

Unread operational notifications shall be displayed prominently.

\paragraph{TUI-008 Workshop Status}

The dashboard shall display workshop operational status.

\paragraph{TUI-009 Synchronization Status}

The dashboard shall display cloud synchronization status.

\paragraph{TUI-010 Quick Actions}

The dashboard shall provide shortcuts to frequently performed repair
activities.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Diagnostic Interface}

\paragraph{TUI-011 Device Registration}

Technicians shall register electronic devices for inspection.

\paragraph{TUI-012 Device Search}

The application shall search registered devices.

\paragraph{TUI-013 Device Details}

The application shall display complete device information.

\paragraph{TUI-014 QR Code Scanning}

Technicians shall scan QR codes attached to electronic devices.

\paragraph{TUI-015 Barcode Scanning}

The application shall support barcode identification.

\paragraph{TUI-016 Diagnostic Checklist}

The application shall provide standardized diagnostic procedures.

\paragraph{TUI-017 Fault Identification}

Technicians shall record detected faults.

\paragraph{TUI-018 AI Diagnostic Assistance}

The application shall support AI-assisted fault diagnosis where
available.

\paragraph{TUI-019 Diagnostic Images}

Technicians shall capture diagnostic photographs.

\paragraph{TUI-020 Diagnostic Report}

The application shall generate a diagnostic report after inspection.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Repair Management Interface}

\paragraph{TUI-021 Repair Assignment}

The application shall display all repair jobs assigned to the technician.

\paragraph{TUI-022 Repair Details}

The application shall display complete repair job information.

\paragraph{TUI-023 Repair Procedures}

The application shall display standardized repair procedures for
supported electronic devices.

\paragraph{TUI-024 Repair Status}

Technicians shall update repair status throughout the repair lifecycle.

\paragraph{TUI-025 Repair Start}

Technicians shall record the commencement of repair activities.

\paragraph{TUI-026 Repair Completion}

Technicians shall record successful completion of repair activities.

\paragraph{TUI-027 Repair Duration}

The application shall calculate repair duration automatically.

\paragraph{TUI-028 Repair Notes}

Technicians shall record repair observations and recommendations.

\paragraph{TUI-029 Repair Images}

Technicians shall capture photographs before, during, and after repair.

\paragraph{TUI-030 Repair History}

The application shall maintain complete repair history for each device.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Spare Parts Management Interface}

\paragraph{TUI-031 Spare Parts Catalogue}

The application shall display the available spare parts inventory.

\paragraph{TUI-032 Spare Part Search}

Technicians shall search available spare parts.

\paragraph{TUI-033 Spare Part Reservation}

Technicians shall reserve spare parts required for repairs.

\paragraph{TUI-034 Spare Part Usage}

The application shall record spare parts consumed during repairs.

\paragraph{TUI-035 Inventory Availability}

The application shall display current stock availability.

\paragraph{TUI-036 Low Stock Alert}

The application shall notify technicians when spare parts are running
low.

\paragraph{TUI-037 Spare Part Barcode}

Technicians shall scan spare part barcodes before use.

\paragraph{TUI-038 Spare Part QR Code}

The application shall support QR code identification of spare parts.

\paragraph{TUI-039 Replacement Recommendation}

The application shall recommend compatible replacement parts where
available.

\paragraph{TUI-040 Inventory Update}

Spare part inventory shall automatically update after consumption.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Quality Assurance Interface}

\paragraph{TUI-041 Quality Inspection}

Completed repairs shall undergo quality inspection.

\paragraph{TUI-042 Inspection Checklist}

The application shall display standardized quality inspection
checklists.

\paragraph{TUI-043 Functional Testing}

Technicians shall record functional testing results.

\paragraph{TUI-044 Safety Inspection}

The application shall support electrical safety inspections.

\paragraph{TUI-045 Performance Testing}

Technicians shall record performance testing results.

\paragraph{TUI-046 Inspection Images}

Quality inspection photographs shall be captured where required.

\paragraph{TUI-047 Inspection Approval}

Quality inspections shall require approval before device release.

\paragraph{TUI-048 Inspection Failure}

Failed inspections shall automatically return the device to the repair
queue.

\paragraph{TUI-049 Inspection History}

The application shall maintain inspection history.

\paragraph{TUI-050 Quality Report}

The application shall generate a quality assurance report.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Refurbishment Interface}

\paragraph{TUI-051 Refurbishment Assessment}

Technicians shall assess whether electronic devices are suitable for
refurbishment.

\paragraph{TUI-052 Refurbishment Classification}

Devices shall be classified according to refurbishment condition.

\paragraph{TUI-053 Cosmetic Assessment}

Technicians shall assess cosmetic condition.

\paragraph{TUI-054 Functional Assessment}

Technicians shall assess functional condition.

\paragraph{TUI-055 Upgrade Recommendation}

The application shall recommend hardware upgrades where appropriate.

\paragraph{TUI-056 Refurbishment Status}

The application shall display refurbishment progress.

\paragraph{TUI-057 Refurbishment Cost}

The application shall estimate refurbishment costs.

\paragraph{TUI-058 Refurbishment Completion}

Technicians shall confirm completion of refurbishment activities.

\paragraph{TUI-059 Refurbishment Images}

The application shall maintain before-and-after refurbishment
photographs.

\paragraph{TUI-060 Refurbishment Report}

The application shall generate a refurbishment report.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Repair Certification Interface}

\paragraph{TUI-061 Repair Certification}

The application shall support generation of repair certification records
for successfully repaired electronic devices.

\paragraph{TUI-062 Certification Number}

Each repair certificate shall contain a unique certification number.

\paragraph{TUI-063 Technician Verification}

The application shall record the identity of the responsible technician.

\paragraph{TUI-064 Supervisor Approval}

Repair certificates shall require supervisor approval where applicable.

\paragraph{TUI-065 Repair Warranty}

The application shall support recording repair warranty information.

\paragraph{TUI-066 Certification Date}

The application shall automatically record the certification date.

\paragraph{TUI-067 Device Condition}

The repair certificate shall record the final condition of the device.

\paragraph{TUI-068 Certificate Export}

Repair certificates shall be exportable in PDF format.

\paragraph{TUI-069 Certificate Sharing}

Authorized users shall securely share repair certificates.

\paragraph{TUI-070 Certification Archive}

The application shall maintain a permanent archive of repair
certificates.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Communication Interface}

\paragraph{TUI-071 Supervisor Communication}

Technicians shall communicate securely with workshop supervisors.

\paragraph{TUI-072 Inventory Communication}

Technicians shall communicate with inventory personnel regarding spare
parts availability.

\paragraph{TUI-073 Recycler Communication}

Technicians shall communicate with recycling personnel regarding
non-repairable devices.

\paragraph{TUI-074 Internal Messaging}

The application shall provide secure internal messaging.

\paragraph{TUI-075 Broadcast Messages}

Administrators shall distribute operational announcements.

\paragraph{TUI-076 Notifications}

Technicians shall receive operational notifications.

\paragraph{TUI-077 File Attachments}

Messages shall support document and image attachments.

\paragraph{TUI-078 Read Status}

The application shall distinguish between read and unread messages.

\paragraph{TUI-079 Message History}

The application shall maintain complete communication history.

\paragraph{TUI-080 Emergency Notifications}

Emergency operational notifications shall receive high priority.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Offline Operation}

\paragraph{TUI-081 Offline Mode}

The application shall support offline workshop operations.

\paragraph{TUI-082 Offline Diagnostics}

Diagnostic activities shall continue without Internet connectivity.

\paragraph{TUI-083 Offline Repairs}

Repair records shall be created while offline.

\paragraph{TUI-084 Offline Images}

Repair photographs shall be stored locally until synchronization.

\paragraph{TUI-085 Offline Inventory}

Previously synchronized spare parts information shall remain available.

\paragraph{TUI-086 Offline Queue}

Offline activities shall be placed into a synchronization queue.

\paragraph{TUI-087 Automatic Synchronization}

Offline records shall synchronize automatically after connectivity is
restored.

\paragraph{TUI-088 Synchronization Status}

Technicians shall monitor synchronization progress.

\paragraph{TUI-089 Conflict Resolution}

Synchronization conflicts shall be detected and resolved according to
configured business rules.

\paragraph{TUI-090 Offline Audit}

Offline activities shall be audited after successful synchronization.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Settings Interface}

\paragraph{TUI-091 Theme}

Technicians shall switch between Light Mode and Dark Mode.

\paragraph{TUI-092 Language}

Technicians shall configure their preferred application language.

\paragraph{TUI-093 Notification Preferences}

Technicians shall configure notification preferences.

\paragraph{TUI-094 Camera Permission}

Technicians shall manage camera permissions.

\paragraph{TUI-095 Storage Permission}

Technicians shall manage storage permissions.

\paragraph{TUI-096 Synchronization Preferences}

Technicians shall configure synchronization settings.

\paragraph{TUI-097 Security Settings}

Technicians shall configure application security settings.

\paragraph{TUI-098 Profile Management}

Technicians shall update profile information.

\paragraph{TUI-099 Application Information}

The application shall display version, build number, and licensing
information.

\paragraph{TUI-100 Restore Defaults}

Technicians shall restore application settings to default values.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Validation Rules}

\begin{itemize}

\item Only authenticated technicians shall access technician functions.

\item Every repair shall be linked to a registered electronic device.

\item Spare parts shall be recorded before repair completion.

\item Quality inspection shall be completed before certification.

\item Repair certificates shall only be issued for approved repairs.

\item Refurbishment reports shall include mandatory assessment data.

\item Offline records shall synchronize successfully before permanent
storage.

\item Unauthorized users shall not access technician functions.

\item Workshop activities shall comply with organizational quality
procedures.

\item All technician activities shall be recorded by the Audit Trail and
Activity Logging Module.

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Acceptance Criteria}

\paragraph{TAC-001}

Technicians can successfully diagnose electronic devices.

\paragraph{TAC-002}

Repair activities are recorded throughout the repair lifecycle.

\paragraph{TAC-003}

Spare parts inventory is accurately updated.

\paragraph{TAC-004}

Quality inspections are completed before device release.

\paragraph{TAC-005}

Repair certificates are generated successfully.

\paragraph{TAC-006}

Refurbishment activities are fully documented.

\paragraph{TAC-007}

Offline repair activities synchronize successfully after network
connectivity is restored.

\paragraph{TAC-008}

Workshop communication functions securely.

\paragraph{TAC-009}

All technician activities are completely auditable.

\paragraph{TAC-010}

The Technician Mobile Application provides a secure, reliable, and
enterprise-grade interface for electronic device diagnosis, repair,
refurbishment, quality assurance, and certification within the
EcoTrace platform.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Recycler Mobile Application}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Purpose}

The Recycler Mobile Application shall provide authorized recycling
personnel with a secure, efficient, and comprehensive interface for
receiving, inspecting, sorting, dismantling, processing, recovering,
and documenting electronic waste materials delivered through the
EcoTrace platform.

The application shall support material recovery operations, hazardous
waste handling, recycling production management, environmental
compliance reporting, inventory tracking, quality monitoring,
communication with supervisors, and offline operation.

The application shall be developed using Flutter and optimized for
Android devices used within recycling facilities and material recovery
centres.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Primary Users}

\begin{itemize}

\item Recycling Operators

\item Recycling Supervisors

\item Material Recovery Officers

\item Environmental Compliance Officers

\item Recycling Plant Managers

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Main Navigation}

The Recycler Mobile Application shall provide the following navigation
menu:

\begin{itemize}

\item Dashboard

\item Incoming Materials

\item Material Sorting

\item Recycling Jobs

\item Inventory

\item Compliance

\item Reports

\item Notifications

\item Messages

\item Profile

\item Settings

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Recycler Dashboard Components}

The dashboard shall display:

\begin{itemize}

\item Recycler Profile

\item Incoming Electronic Waste

\item Pending Processing Jobs

\item Material Recovery Summary

\item Daily Production

\item Hazardous Waste Alerts

\item Environmental Compliance Status

\item Inventory Summary

\item Equipment Status

\item Performance Indicators

\item Notifications

\item Quick Actions

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Recycler User Interface Requirements}

\paragraph{RUI-001 Dashboard}

The application shall display a personalized recycler dashboard after
successful authentication.

\paragraph{RUI-002 Incoming Materials}

The dashboard shall display incoming electronic waste awaiting
processing.

\paragraph{RUI-003 Recycling Jobs}

The dashboard shall summarize active recycling activities.

\paragraph{RUI-004 Material Recovery}

The dashboard shall display recovered material statistics.

\paragraph{RUI-005 Production Summary}

The dashboard shall display daily recycling production.

\paragraph{RUI-006 Compliance Status}

The dashboard shall display environmental compliance indicators.

\paragraph{RUI-007 Hazard Alerts}

The dashboard shall display hazardous material alerts.

\paragraph{RUI-008 Notifications}

Unread operational notifications shall be prominently displayed.

\paragraph{RUI-009 Synchronization Status}

The dashboard shall display cloud synchronization status.

\paragraph{RUI-010 Quick Actions}

The dashboard shall provide shortcuts to frequently used recycling
operations.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Incoming Material Interface}

\paragraph{RUI-011 Material Reception}

The application shall record incoming electronic waste deliveries.

\paragraph{RUI-012 Delivery Verification}

Recycling personnel shall verify received electronic waste.

\paragraph{RUI-013 QR Code Verification}

The application shall support QR code verification.

\paragraph{RUI-014 Barcode Verification}

The application shall support barcode verification.

\paragraph{RUI-015 Delivery Inspection}

The application shall record initial inspection findings.

\paragraph{RUI-016 Material Categorization}

Incoming materials shall be categorized according to approved
electronic waste classifications.

\paragraph{RUI-017 Hazard Identification}

Hazardous materials shall be clearly identified.

\paragraph{RUI-018 Weight Recording}

The application shall record measured material weight.

\paragraph{RUI-019 Storage Assignment}

Incoming materials shall be assigned to storage locations.

\paragraph{RUI-020 Material Acceptance}

Authorized recyclers shall confirm material acceptance.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Material Sorting Interface}

\paragraph{RUI-021 Sorting Queue}

The application shall display electronic waste awaiting sorting.

\paragraph{RUI-022 Sorting Categories}

The application shall classify electronic waste into approved recycling
categories.

\paragraph{RUI-023 Automatic Classification}

The application shall support AI-assisted material classification where
available.

\paragraph{RUI-024 Manual Classification}

Authorized recyclers shall manually classify materials when necessary.

\paragraph{RUI-025 Material Condition}

The recycler shall record the physical condition of incoming materials.

\paragraph{RUI-026 Hazard Separation}

Hazardous materials shall be separated from non-hazardous materials.

\paragraph{RUI-027 Storage Allocation}

Sorted materials shall be assigned to designated storage areas.

\paragraph{RUI-028 Sorting Verification}

Sorting activities shall require verification before processing.

\paragraph{RUI-029 Sorting Images}

The application shall support photographic documentation of sorted
materials.

\paragraph{RUI-030 Sorting History}

The application shall maintain complete material sorting history.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Dismantling Interface}

\paragraph{RUI-031 Dismantling Job}

The application shall assign dismantling jobs to authorized personnel.

\paragraph{RUI-032 Dismantling Instructions}

The application shall display standardized dismantling procedures.

\paragraph{RUI-033 Component Identification}

Recovered components shall be individually identified.

\paragraph{RUI-034 Component Categorization}

Recovered components shall be categorized according to material type.

\paragraph{RUI-035 Hazardous Component Identification}

Hazardous components shall be clearly identified.

\paragraph{RUI-036 Component Weighing}

Recovered materials shall be weighed after dismantling.

\paragraph{RUI-037 Component Images}

Photographs shall be captured during dismantling where required.

\paragraph{RUI-038 Dismantling Progress}

The application shall display dismantling progress.

\paragraph{RUI-039 Dismantling Completion}

Authorized recyclers shall confirm dismantling completion.

\paragraph{RUI-040 Dismantling History}

The application shall maintain complete dismantling history.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Material Recovery Interface}

\paragraph{RUI-041 Material Recovery}

The application shall record recovered recyclable materials.

\paragraph{RUI-042 Material Types}

Recovered materials shall include metals, plastics, glass, circuit
boards, batteries, cables, and other approved material categories.

\paragraph{RUI-043 Recovery Quantity}

Recovered material quantities shall be recorded.

\paragraph{RUI-044 Recovery Weight}

Recovered material weights shall be measured and stored.

\paragraph{RUI-045 Recovery Purity}

The application shall record material purity levels where applicable.

\paragraph{RUI-046 Recovery Yield}

The application shall calculate material recovery yield.

\paragraph{RUI-047 Recovery Value}

The application shall estimate the economic value of recovered
materials.

\paragraph{RUI-048 Recovery Inventory}

Recovered materials shall automatically update inventory records.

\paragraph{RUI-049 Recovery Report}

The application shall generate material recovery reports.

\paragraph{RUI-050 Recovery History}

The application shall maintain complete recovery history.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Hazardous Waste Interface}

\paragraph{RUI-051 Hazardous Waste Identification}

The application shall identify hazardous electronic waste materials.

\paragraph{RUI-052 Hazard Categories}

Hazardous waste shall be categorized according to applicable
environmental regulations.

\paragraph{RUI-053 Hazard Labels}

Hazardous materials shall receive standardized warning labels.

\paragraph{RUI-054 Secure Storage}

Hazardous materials shall be assigned secure storage locations.

\paragraph{RUI-055 Hazard Documentation}

The application shall maintain hazardous waste documentation.

\paragraph{RUI-056 Environmental Compliance}

Hazardous waste processing shall comply with environmental regulations.

\paragraph{RUI-057 Hazard Transport}

The application shall record hazardous material transportation details.

\paragraph{RUI-058 Disposal Authorization}

Hazardous waste disposal shall require authorization.

\paragraph{RUI-059 Hazard Audit}

Hazardous waste activities shall be audited.

\paragraph{RUI-060 Hazard Reports}

The application shall generate hazardous waste reports.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Inventory Management Interface}

\paragraph{RUI-061 Inventory Dashboard}

The application shall display the current inventory of recovered
materials.

\paragraph{RUI-062 Material Inventory}

Recovered metals, plastics, glass, batteries, circuit boards, cables,
and other recyclable materials shall be maintained in inventory.

\paragraph{RUI-063 Inventory Search}

Authorized recyclers shall search inventory records.

\paragraph{RUI-064 Inventory Categories}

Inventory shall be organized according to standardized material
categories.

\paragraph{RUI-065 Inventory Quantities}

The application shall display current inventory quantities.

\paragraph{RUI-066 Inventory Weight}

The application shall maintain material weight records.

\paragraph{RUI-067 Inventory Valuation}

The application shall estimate the monetary value of stored materials.

\paragraph{RUI-068 Inventory Movement}

The application shall record inventory movements between storage
locations.

\paragraph{RUI-069 Inventory Adjustment}

Authorized personnel shall adjust inventory after verification.

\paragraph{RUI-070 Inventory Reports}

The application shall generate inventory reports.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Environmental Compliance Interface}

\paragraph{RUI-071 Compliance Dashboard}

The application shall display environmental compliance information.

\paragraph{RUI-072 Regulatory Compliance}

Recycling activities shall comply with applicable environmental
regulations.

\paragraph{RUI-073 Permit Verification}

The application shall display recycling permit information.

\paragraph{RUI-074 Compliance Checklist}

The application shall provide standardized compliance checklists.

\paragraph{RUI-075 Environmental Inspection}

Environmental inspections shall be recorded.

\paragraph{RUI-076 Compliance Violations}

The application shall record environmental compliance violations.

\paragraph{RUI-077 Corrective Actions}

Corrective actions shall be assigned for identified violations.

\paragraph{RUI-078 Compliance Monitoring}

The application shall continuously monitor compliance status.

\paragraph{RUI-079 Compliance Certificates}

Authorized users shall access compliance certificates.

\paragraph{RUI-080 Compliance Reports}

The application shall generate environmental compliance reports.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Production Reporting Interface}

\paragraph{RUI-081 Production Dashboard}

The application shall display daily recycling production statistics.

\paragraph{RUI-082 Daily Production}

Daily production quantities shall be recorded.

\paragraph{RUI-083 Weekly Production}

Weekly production summaries shall be generated.

\paragraph{RUI-084 Monthly Production}

Monthly production summaries shall be generated.

\paragraph{RUI-085 Recovery Efficiency}

The application shall calculate recovery efficiency.

\paragraph{RUI-086 Processing Time}

The application shall calculate material processing time.

\paragraph{RUI-087 Equipment Utilization}

The application shall display equipment utilization statistics.

\paragraph{RUI-088 Production Targets}

The application shall compare actual production against targets.

\paragraph{RUI-089 Production Analytics}

The application shall display graphical production analytics.

\paragraph{RUI-090 Production Reports}

The application shall generate production reports in PDF format.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Communication Interface}

\paragraph{RUI-091 Supervisor Communication}

Recyclers shall securely communicate with supervisors.

\paragraph{RUI-092 Technician Communication}

Recyclers shall communicate with repair technicians.

\paragraph{RUI-093 Inventory Communication}

Recyclers shall communicate with inventory personnel.

\paragraph{RUI-094 Internal Messaging}

The application shall support secure internal messaging.

\paragraph{RUI-095 Notifications}

Operational notifications shall be delivered in real time.

\paragraph{RUI-096 Broadcast Announcements}

Administrators shall distribute facility-wide announcements.

\paragraph{RUI-097 File Attachments}

Messages shall support document and image attachments.

\paragraph{RUI-098 Message History}

The application shall maintain communication history.

\paragraph{RUI-099 Emergency Alerts}

Emergency alerts shall receive the highest delivery priority.

\paragraph{RUI-100 Read Status}

The application shall distinguish between read and unread messages.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Offline Operation}

\paragraph{RUI-101 Offline Mode}

The application shall support offline recycling operations.

\paragraph{RUI-102 Offline Inventory}

Previously synchronized inventory information shall remain available
offline.

\paragraph{RUI-103 Offline Production Recording}

Production records shall be captured without Internet connectivity.

\paragraph{RUI-104 Offline Image Storage}

Photographs shall be securely stored until synchronization.

\paragraph{RUI-105 Offline Queue}

Offline activities shall be queued for synchronization.

\paragraph{RUI-106 Automatic Synchronization}

Offline records shall synchronize automatically after connectivity is
restored.

\paragraph{RUI-107 Synchronization Status}

The application shall display synchronization progress.

\paragraph{RUI-108 Conflict Resolution}

Synchronization conflicts shall be detected and resolved according to
configured business rules.

\paragraph{RUI-109 Offline Audit}

Offline activities shall be audited after synchronization.

\paragraph{RUI-110 Data Integrity}

The application shall verify data integrity before synchronization.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Validation Rules}

\begin{itemize}

\item Only authorized recycling personnel shall access recycler
functions.

\item Every incoming material shall be verified before processing.

\item Hazardous materials shall be processed according to environmental
regulations.

\item Material recovery records shall contain mandatory measurements.

\item Inventory quantities shall remain synchronized with production
activities.

\item Environmental compliance reports shall be generated from verified
records.

\item Offline records shall synchronize successfully before permanent
storage.

\item Unauthorized users shall not access recycling operations.

\item Environmental incidents shall be reported immediately.

\item All recycling activities shall be recorded by the Audit Trail and
Activity Logging Module.

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Acceptance Criteria}

\paragraph{RAC-001}

Incoming electronic waste is successfully received and verified.

\paragraph{RAC-002}

Materials are correctly sorted and dismantled.

\paragraph{RAC-003}

Recovered materials are accurately recorded in inventory.

\paragraph{RAC-004}

Hazardous waste is managed in accordance with environmental
requirements.

\paragraph{RAC-005}

Production reports are generated successfully.

\paragraph{RAC-006}

Environmental compliance reports are accurate.

\paragraph{RAC-007}

Offline recycling activities synchronize successfully after network
connectivity is restored.

\paragraph{RAC-008}

Internal communication operates securely.

\paragraph{RAC-009}

All recycling operations are completely auditable.

\paragraph{RAC-010}

The Recycler Mobile Application provides a secure, reliable, and
enterprise-grade interface for electronic waste recycling, material
recovery, inventory management, environmental compliance, and
production reporting within the EcoTrace platform.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Organization Web Portal}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Purpose}

The Organization Web Portal shall provide registered organizations with
a secure, scalable, and comprehensive web-based interface for managing
electronic waste activities across one or more organizational locations.
The portal shall support enterprise asset management, bulk electronic
waste registration, pickup scheduling, environmental compliance,
organizational reporting, user administration, analytics, marketplace
operations, and communication with EcoTrace stakeholders.

The portal shall be accessible through modern web browsers and shall
support responsive layouts for desktop and tablet devices.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Primary Users}

\begin{itemize}

\item Organization Administrators

\item Sustainability Officers

\item Environmental Compliance Officers

\item Asset Managers

\item Procurement Officers

\item Facility Managers

\item Department Managers

\item Executive Management

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Main Navigation}

The Organization Web Portal shall provide the following navigation menu:

\begin{itemize}

\item Dashboard

\item Asset Management

\item Pickup Requests

\item AI Asset Identification

\item Marketplace

\item Reports

\item Analytics

\item User Management

\item Organization Settings

\item Documents

\item Notifications

\item Profile

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Organization Dashboard Components}

The dashboard shall include:

\begin{itemize}

\item Organization Summary

\item Active Pickup Requests

\item Electronic Asset Inventory

\item Environmental Impact Dashboard

\item Carbon Emission Reduction Statistics

\item Recycling Performance Indicators

\item Compliance Status

\item Marketplace Orders

\item Financial Summary

\item Notifications

\item Quick Actions

\item Recent Activities

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Organization Web Interface Requirements}

\paragraph{OWI-001 Dashboard}

The portal shall display a personalized organizational dashboard after
successful authentication.

\paragraph{OWI-002 Organization Profile}

The dashboard shall display organization profile information.

\paragraph{OWI-003 Asset Summary}

The dashboard shall summarize registered electronic assets.

\paragraph{OWI-004 Environmental Summary}

The dashboard shall display environmental sustainability indicators.

\paragraph{OWI-005 Compliance Summary}

The dashboard shall display regulatory compliance status.

\paragraph{OWI-006 Marketplace Summary}

The dashboard shall summarize marketplace transactions.

\paragraph{OWI-007 Notifications}

Unread organizational notifications shall be prominently displayed.

\paragraph{OWI-008 Analytics}

The dashboard shall display graphical analytics and performance charts.

\paragraph{OWI-009 Reports}

The dashboard shall provide quick access to organizational reports.

\paragraph{OWI-010 Recent Activities}

The dashboard shall display recent organizational activities.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Asset Management Interface}

\paragraph{OWI-011 Asset Registration}

Organizations shall register electronic assets individually or in bulk.

\paragraph{OWI-012 Bulk Import}

The portal shall support bulk asset import using approved spreadsheet
templates.

\paragraph{OWI-013 Asset Search}

Users shall search organizational assets using multiple criteria.

\paragraph{OWI-014 Asset Details}

The portal shall display complete asset information.

\paragraph{OWI-015 Asset Categories}

Assets shall be organized according to standardized categories.

\paragraph{OWI-016 Asset Status}

The portal shall display the lifecycle status of every registered asset.

\paragraph{OWI-017 QR Code Generation}

The system shall generate unique QR codes for registered assets.

\paragraph{OWI-018 Barcode Generation}

The system shall support barcode generation and printing.

\paragraph{OWI-019 Asset History}

The portal shall maintain complete lifecycle history for every asset.

\paragraph{OWI-020 Asset Disposal Request}

Organizations shall initiate electronic waste disposal requests directly
from asset records.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Pickup Management Interface}

\paragraph{OWI-021 Pickup Dashboard}

The portal shall provide a centralized dashboard for managing electronic
waste pickup requests.

\paragraph{OWI-022 New Pickup Request}

Authorized users shall create new pickup requests.

\paragraph{OWI-023 Bulk Pickup Request}

The portal shall support bulk pickup requests for multiple electronic
assets.

\paragraph{OWI-024 Pickup Scheduling}

Organizations shall schedule pickup dates and preferred collection
time windows.

\paragraph{OWI-025 Pickup Location}

Users shall select one or more organizational pickup locations.

\paragraph{OWI-026 Pickup Priority}

Authorized users shall assign pickup priority levels.

\paragraph{OWI-027 Pickup Tracking}

The portal shall display real-time pickup progress.

\paragraph{OWI-028 Assigned Collector}

Users shall view assigned collector information.

\paragraph{OWI-029 Assigned Driver}

Users shall view assigned driver information.

\paragraph{OWI-030 Pickup History}

The portal shall maintain complete organizational pickup history.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Organization User Management Interface}

\paragraph{OWI-031 User Management}

Organization administrators shall manage organizational users.

\paragraph{OWI-032 User Registration}

Authorized administrators shall register new organization users.

\paragraph{OWI-033 User Search}

Administrators shall search organization users.

\paragraph{OWI-034 User Profile}

The portal shall display complete user profiles.

\paragraph{OWI-035 User Status}

Administrators shall activate or deactivate organization users.

\paragraph{OWI-036 Role Assignment}

Administrators shall assign organizational roles.

\paragraph{OWI-037 Permission Assignment}

Administrators shall configure user permissions.

\paragraph{OWI-038 Password Reset}

Administrators shall initiate password reset procedures.

\paragraph{OWI-039 Multi-Factor Authentication}

The portal shall support multi-factor authentication for organizational
users.

\paragraph{OWI-040 User Activity}

The portal shall display user login and activity history.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Document Management Interface}

\paragraph{OWI-041 Document Repository}

The portal shall provide a centralized document repository.

\paragraph{OWI-042 Document Upload}

Authorized users shall upload organizational documents.

\paragraph{OWI-043 Document Categories}

Documents shall be organized using standardized categories.

\paragraph{OWI-044 Document Search}

Users shall search organizational documents.

\paragraph{OWI-045 Document Versioning}

The portal shall maintain document version history.

\paragraph{OWI-046 Secure Download}

Protected documents shall require authorization before download.

\paragraph{OWI-047 Document Approval}

Specified documents shall support approval workflows.

\paragraph{OWI-048 Digital Certificates}

The portal shall display issued recycling and compliance certificates.

\paragraph{OWI-049 Document Archive}

Historical documents shall remain accessible according to retention
policies.

\paragraph{OWI-050 Document Audit}

All document activities shall be recorded by the Audit Trail and
Activity Logging Module.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Compliance Management Interface}

\paragraph{OWI-051 Compliance Dashboard}

The portal shall display organizational compliance information.

\paragraph{OWI-052 Environmental Compliance}

Organizations shall monitor environmental compliance status.

\paragraph{OWI-053 Regulatory Reports}

The portal shall generate regulatory compliance reports.

\paragraph{OWI-054 Collection Certificates}

Organizations shall access electronic waste collection certificates.

\paragraph{OWI-055 Recycling Certificates}

Organizations shall access recycling certificates.

\paragraph{OWI-056 Carbon Reduction Reports}

The portal shall generate carbon emission reduction reports.

\paragraph{OWI-057 Sustainability Reports}

Organizations shall generate sustainability reports.

\paragraph{OWI-058 Compliance Alerts}

Users shall receive compliance deadline notifications.

\paragraph{OWI-059 Corrective Actions}

The portal shall monitor compliance corrective actions.

\paragraph{OWI-060 Compliance History}

The portal shall maintain complete compliance history.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Sustainability and Environmental Analytics Interface}

\paragraph{OWI-061 Sustainability Dashboard}

The portal shall provide a comprehensive sustainability dashboard for
organizational environmental performance monitoring.

\paragraph{OWI-062 Carbon Footprint}

The portal shall calculate and display the organization's carbon
footprint reduction.

\paragraph{OWI-063 Carbon Savings}

The portal shall calculate carbon emissions avoided through responsible
electronic waste recycling.

\paragraph{OWI-064 Recycling Performance}

The portal shall display recycling performance indicators.

\paragraph{OWI-065 Circular Economy Metrics}

The portal shall display circular economy performance metrics.

\paragraph{OWI-066 Material Recovery Statistics}

Recovered material statistics shall be displayed graphically.

\paragraph{OWI-067 Environmental Goals}

Organizations shall define environmental sustainability goals.

\paragraph{OWI-068 Goal Monitoring}

The portal shall monitor progress toward sustainability goals.

\paragraph{OWI-069 Environmental Benchmarking}

Organizations shall compare sustainability performance across reporting
periods.

\paragraph{OWI-070 Sustainability Reports}

The portal shall generate sustainability reports in PDF format.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Analytics and Business Intelligence Interface}

\paragraph{OWI-071 Analytics Dashboard}

The portal shall provide interactive business intelligence dashboards.

\paragraph{OWI-072 Interactive Charts}

Analytics dashboards shall display interactive charts and graphs.

\paragraph{OWI-073 Trend Analysis}

The portal shall display historical electronic waste trends.

\paragraph{OWI-074 Collection Analytics}

Collection statistics shall be analyzed by location and period.

\paragraph{OWI-075 Asset Analytics}

The portal shall analyze organizational electronic asset utilization.

\paragraph{OWI-076 AI Analytics}

The portal shall summarize AI identification accuracy and usage.

\paragraph{OWI-077 Performance Indicators}

The portal shall display organizational KPIs.

\paragraph{OWI-078 Export Analytics}

Users shall export analytical reports.

\paragraph{OWI-079 Custom Reports}

Authorized users shall generate custom analytical reports.

\paragraph{OWI-080 Data Visualization}

The portal shall provide graphical visualization of organizational
performance.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Marketplace Management Interface}

\paragraph{OWI-081 Marketplace Dashboard}

The portal shall provide a marketplace management dashboard.

\paragraph{OWI-082 Marketplace Orders}

Organizations shall monitor marketplace purchases.

\paragraph{OWI-083 Product Catalogue}

The portal shall display refurbished electronic products.

\paragraph{OWI-084 Product Search}

Users shall search marketplace products.

\paragraph{OWI-085 Product Filters}

Products shall support advanced filtering.

\paragraph{OWI-086 Shopping Cart}

The portal shall provide shopping cart functionality.

\paragraph{OWI-087 Secure Checkout}

Marketplace purchases shall support secure payment processing.

\paragraph{OWI-088 Order Tracking}

Organizations shall monitor order progress.

\paragraph{OWI-089 Purchase History}

The portal shall maintain purchase history.

\paragraph{OWI-090 Marketplace Notifications}

Users shall receive marketplace notifications.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Organization Settings Interface}

\paragraph{OWI-091 Organization Profile}

Authorized administrators shall manage organization profile
information.

\paragraph{OWI-092 Branch Management}

The portal shall support management of multiple organizational
branches.

\paragraph{OWI-093 Department Management}

Organizations shall manage departments.

\paragraph{OWI-094 Notification Preferences}

Administrators shall configure organizational notification settings.

\paragraph{OWI-095 Security Settings}

The portal shall provide organizational security configuration.

\paragraph{OWI-096 Privacy Settings}

Organizations shall configure privacy preferences.

\paragraph{OWI-097 Branding}

Organizations shall customize approved branding elements where
permitted.

\paragraph{OWI-098 Regional Settings}

Users shall configure regional settings.

\paragraph{OWI-099 Backup Preferences}

Organizations shall configure data backup preferences where supported.

\paragraph{OWI-100 System Preferences}

The portal shall provide configurable organizational system settings.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Notification and Communication Interface}

\paragraph{OWI-101 Notification Centre}

The portal shall provide a centralized notification centre.

\paragraph{OWI-102 Internal Messaging}

Users shall exchange secure internal messages.

\paragraph{OWI-103 Broadcast Announcements}

Organization administrators shall distribute announcements.

\paragraph{OWI-104 Email Notifications}

The portal shall send email notifications for important events.

\paragraph{OWI-105 SMS Notifications}

The system shall support SMS notifications where configured.

\paragraph{OWI-106 Push Notifications}

Browser push notifications shall be supported.

\paragraph{OWI-107 Read Status}

The portal shall distinguish between read and unread notifications.

\paragraph{OWI-108 Notification Archive}

Historical notifications shall remain accessible.

\paragraph{OWI-109 Attachment Support}

Messages shall support document attachments.

\paragraph{OWI-110 Communication History}

The portal shall maintain complete communication history.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Validation Rules}

\begin{itemize}

\item Only authenticated organizational users shall access the
Organization Web Portal.

\item Organization administrators shall manage user accounts and
permissions.

\item Electronic assets shall be registered before disposal requests are
submitted.

\item Compliance reports shall be generated only from verified records.

\item Marketplace purchases shall require successful payment
authorization.

\item Uploaded organizational documents shall satisfy configured file
validation rules.

\item QR codes generated by the system shall remain unique.

\item Multi-factor authentication shall be enforced where enabled.

\item Organizational settings shall comply with security policies.

\item All portal activities shall be recorded by the Audit Trail and
Activity Logging Module.

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Acceptance Criteria}

\paragraph{OAC-001}

Organizations can successfully manage electronic assets.

\paragraph{OAC-002}

Organizations can schedule and monitor bulk electronic waste pickups.

\paragraph{OAC-003}

Compliance and sustainability reports are generated accurately.

\paragraph{OAC-004}

Organizational users and roles are managed securely.

\paragraph{OAC-005}

Marketplace transactions are completed successfully.

\paragraph{OAC-006}

Business intelligence dashboards display accurate organizational
analytics.

\paragraph{OAC-007}

Electronic documents are securely managed.

\paragraph{OAC-008}

Organizational communications operate securely.

\paragraph{OAC-009}

All organizational activities are completely auditable.

\paragraph{OAC-010}

The Organization Web Portal provides a secure, scalable, and
enterprise-grade interface for managing organizational participation
within the EcoTrace Intelligent Electronic Waste Recovery and Circular
Economy Management System.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Administrator Web Portal}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Purpose}

The Administrator Web Portal shall provide authorized EcoTrace
administrators with a centralized enterprise management platform for
monitoring, configuring, supervising, securing, and maintaining all
components of the EcoTrace Intelligent Electronic Waste Recovery and
Circular Economy Management System.

The portal shall enable administrators to manage users,
organizations, electronic assets, collection operations,
transportation, repair centres, recycling facilities, AI services,
notifications, reports, analytics, environmental compliance,
marketplace operations, security policies, and system configuration.

The Administrator Web Portal shall serve as the primary operational
control centre of the EcoTrace platform and shall be accessible through
modern desktop web browsers.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Primary Users}

\begin{itemize}

\item System Administrators

\item Operations Managers

\item Environmental Administrators

\item Platform Administrators

\item Customer Support Administrators

\item Fleet Administrators

\item Security Administrators

\item Compliance Officers

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Main Navigation}

The Administrator Web Portal shall provide the following navigation
menu:

\begin{itemize}

\item Dashboard

\item User Management

\item Organization Management

\item Asset Management

\item Collection Operations

\item Fleet Management

\item Repair Management

\item Recycling Management

\item Marketplace

\item AI Services

\item GIS Mapping

\item Reports

\item Analytics

\item Notifications

\item Security

\item Audit Logs

\item Settings

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Administrator Dashboard Components}

The dashboard shall display:

\begin{itemize}

\item Platform Summary

\item Active Users

\item Registered Organizations

\item Collection Statistics

\item Fleet Status

\item Repair Statistics

\item Recycling Statistics

\item AI Service Status

\item Environmental Compliance

\item Revenue Summary

\item Marketplace Statistics

\item Carbon Reduction Metrics

\item System Health

\item Security Alerts

\item Notifications

\item Quick Actions

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Administrator Web Interface Requirements}

\paragraph{AWI-001 Dashboard}

The portal shall display a comprehensive administrator dashboard after
successful authentication.

\paragraph{AWI-002 Platform Overview}

The dashboard shall display real-time platform statistics.

\paragraph{AWI-003 Active Users}

The dashboard shall display currently active users.

\paragraph{AWI-004 Registered Organizations}

The dashboard shall display registered organizations.

\paragraph{AWI-005 Collection Summary}

The dashboard shall summarize electronic waste collection activities.

\paragraph{AWI-006 Fleet Summary}

The dashboard shall display fleet operational status.

\paragraph{AWI-007 Recycling Summary}

The dashboard shall summarize recycling activities.

\paragraph{AWI-008 AI Summary}

The dashboard shall display AI service statistics.

\paragraph{AWI-009 Security Status}

The dashboard shall display platform security status.

\paragraph{AWI-010 Notifications}

Unread administrative notifications shall be prominently displayed.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{User Management Interface}

\paragraph{AWI-011 User Dashboard}

The portal shall provide a centralized user management dashboard.

\paragraph{AWI-012 User Registration}

Administrators shall register new platform users.

\paragraph{AWI-013 User Search}

Administrators shall search platform users.

\paragraph{AWI-014 User Profile}

The portal shall display complete user profiles.

\paragraph{AWI-015 User Approval}

Administrators shall approve new user registrations.

\paragraph{AWI-016 User Suspension}

Administrators shall suspend user accounts.

\paragraph{AWI-017 User Reactivation}

Administrators shall reactivate suspended accounts.

\paragraph{AWI-018 Password Reset}

Administrators shall initiate password reset procedures.

\paragraph{AWI-019 Role Assignment}

Administrators shall assign platform roles.

\paragraph{AWI-020 Permission Management}

Administrators shall configure role-based permissions.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Repair Centre Administration Interface}

\paragraph{AWI-061 Repair Centre Dashboard}

The portal shall provide a centralized dashboard for monitoring all
registered repair centres.

\paragraph{AWI-062 Repair Centre Registration}

Administrators shall register repair centres.

\paragraph{AWI-063 Repair Centre Approval}

Administrators shall approve repair centre registration requests.

\paragraph{AWI-064 Repair Job Monitoring}

The portal shall monitor repair jobs across all repair centres.

\paragraph{AWI-065 Technician Assignment}

Administrators shall assign technicians to repair tasks.

\paragraph{AWI-066 Spare Parts Monitoring}

The portal shall monitor spare parts inventory across repair centres.

\paragraph{AWI-067 Repair Performance}

The portal shall display repair performance indicators.

\paragraph{AWI-068 Quality Assurance}

Administrators shall monitor quality assurance activities.

\paragraph{AWI-069 Repair Certification}

The portal shall monitor issued repair certificates.

\paragraph{AWI-070 Repair Reports}

The portal shall generate repair centre performance reports.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Recycling Facility Administration Interface}

\paragraph{AWI-071 Recycling Facility Dashboard}

The portal shall provide a centralized dashboard for all recycling
facilities.

\paragraph{AWI-072 Recycling Facility Registration}

Administrators shall register recycling facilities.

\paragraph{AWI-073 Facility Approval}

Administrators shall approve recycling facility registrations.

\paragraph{AWI-074 Material Processing}

The portal shall monitor material processing activities.

\paragraph{AWI-075 Material Recovery}

Administrators shall monitor recovered materials.

\paragraph{AWI-076 Hazardous Waste Management}

The portal shall supervise hazardous electronic waste processing.

\paragraph{AWI-077 Production Monitoring}

The portal shall monitor recycling production.

\paragraph{AWI-078 Environmental Compliance}

The portal shall monitor environmental compliance across facilities.

\paragraph{AWI-079 Recycling Performance}

Administrators shall evaluate recycling facility performance.

\paragraph{AWI-080 Recycling Reports}

The portal shall generate recycling performance reports.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Artificial Intelligence Administration Interface}

\paragraph{AWI-081 AI Dashboard}

The portal shall provide a dashboard for monitoring AI services.

\paragraph{AWI-082 AI Model Management}

Administrators shall manage deployed AI models.

\paragraph{AWI-083 Model Versioning}

The system shall maintain AI model version history.

\paragraph{AWI-084 Model Deployment}

Authorized administrators shall deploy approved AI models.

\paragraph{AWI-085 AI Performance}

The portal shall monitor AI prediction performance.

\paragraph{AWI-086 Confidence Analysis}

Administrators shall review AI confidence statistics.

\paragraph{AWI-087 Dataset Management}

The portal shall manage AI training datasets.

\paragraph{AWI-088 Model Retraining}

Authorized administrators shall initiate AI model retraining.

\paragraph{AWI-089 AI Error Monitoring}

The system shall monitor AI prediction failures.

\paragraph{AWI-090 AI Reports}

The portal shall generate AI performance reports.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{GIS and Mapping Administration Interface}

\paragraph{AWI-091 GIS Dashboard}

The portal shall provide a GIS management dashboard.

\paragraph{AWI-092 Interactive Map}

The portal shall display an interactive map of operational activities.

\paragraph{AWI-093 Collection Zones}

Administrators shall manage collection zones.

\paragraph{AWI-094 Recycling Locations}

The portal shall display recycling facility locations.

\paragraph{AWI-095 Route Visualization}

The portal shall visualize collection and transportation routes.

\paragraph{AWI-096 Heat Maps}

The system shall generate electronic waste heat maps.

\paragraph{AWI-097 Geofencing}

The portal shall support geofencing for operational monitoring.

\paragraph{AWI-098 GPS Monitoring}

Administrators shall monitor GPS-enabled field operations.

\paragraph{AWI-099 Spatial Analytics}

The portal shall provide spatial analytics dashboards.

\paragraph{AWI-100 GIS Reports}

The portal shall generate GIS analytical reports.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{IoT Device Administration Interface}

\paragraph{AWI-101 IoT Dashboard}

The portal shall display connected IoT devices.

\paragraph{AWI-102 Device Registration}

Administrators shall register IoT devices.

\paragraph{AWI-103 Device Status}

The portal shall display IoT device operational status.

\paragraph{AWI-104 Device Monitoring}

Administrators shall monitor IoT sensor readings.

\paragraph{AWI-105 Device Configuration}

Authorized administrators shall configure IoT devices.

\paragraph{AWI-106 Device Alerts}

The system shall notify administrators of IoT device failures.

\paragraph{AWI-107 Firmware Management}

The portal shall manage IoT firmware updates.

\paragraph{AWI-108 Device Maintenance}

Administrators shall schedule IoT device maintenance.

\paragraph{AWI-109 Device History}

The portal shall maintain IoT device operational history.

\paragraph{AWI-110 IoT Reports}

The portal shall generate IoT monitoring reports.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Inventory Administration Interface}

\paragraph{AWI-111 Inventory Dashboard}

The portal shall display centralized inventory information.

\paragraph{AWI-112 Inventory Search}

Administrators shall search inventory records.

\paragraph{AWI-113 Inventory Categories}

Inventory shall be organized according to standardized categories.

\paragraph{AWI-114 Inventory Monitoring}

The portal shall monitor inventory levels across facilities.

\paragraph{AWI-115 Inventory Transfers}

Administrators shall authorize inventory transfers.

\paragraph{AWI-116 Low Stock Alerts}

The system shall notify administrators of low inventory levels.

\paragraph{AWI-117 Inventory Valuation}

The portal shall estimate inventory value.

\paragraph{AWI-118 Inventory Audit}

Inventory movements shall be recorded for auditing.

\paragraph{AWI-119 Inventory Reports}

The portal shall generate inventory reports.

\paragraph{AWI-120 Inventory Analytics}

The portal shall provide inventory analytics dashboards.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Financial Administration Interface}

\paragraph{AWI-121 Financial Dashboard}

The portal shall provide a centralized financial management dashboard.

\paragraph{AWI-122 Revenue Monitoring}

Administrators shall monitor platform revenue generated from marketplace
transactions, service fees, and recycling operations.

\paragraph{AWI-123 Expense Monitoring}

The portal shall monitor operational expenditures.

\paragraph{AWI-124 Payment Transactions}

Administrators shall review completed payment transactions.

\paragraph{AWI-125 Refund Management}

Authorized administrators shall process approved refunds.

\paragraph{AWI-126 Invoice Management}

The portal shall generate and manage invoices.

\paragraph{AWI-127 Financial Reports}

The system shall generate financial reports.

\paragraph{AWI-128 Revenue Analytics}

The portal shall display revenue trends.

\paragraph{AWI-129 Financial Forecasting}

The portal shall support financial forecasting dashboards.

\paragraph{AWI-130 Financial Audit}

Financial transactions shall be recorded for auditing purposes.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Marketplace Administration Interface}

\paragraph{AWI-131 Marketplace Dashboard}

The portal shall provide centralized marketplace administration.

\paragraph{AWI-132 Product Management}

Administrators shall manage marketplace products.

\paragraph{AWI-133 Product Approval}

Marketplace products shall require administrative approval before
publication.

\paragraph{AWI-134 Category Management}

Administrators shall manage marketplace categories.

\paragraph{AWI-135 Order Monitoring}

The portal shall monitor customer orders.

\paragraph{AWI-136 Seller Management}

Administrators shall manage marketplace sellers.

\paragraph{AWI-137 Pricing Management}

Administrators shall configure pricing policies.

\paragraph{AWI-138 Discount Management}

The portal shall support promotional campaigns and discounts.

\paragraph{AWI-139 Marketplace Analytics}

Marketplace performance shall be monitored using analytics dashboards.

\paragraph{AWI-140 Marketplace Reports}

The portal shall generate marketplace reports.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Security Administration Interface}

\paragraph{AWI-141 Security Dashboard}

The portal shall provide a centralized security dashboard.

\paragraph{AWI-142 Access Control}

Administrators shall manage role-based access control policies.

\paragraph{AWI-143 Multi-Factor Authentication}

The portal shall enforce multi-factor authentication where configured.

\paragraph{AWI-144 Session Management}

Administrators shall monitor active user sessions.

\paragraph{AWI-145 Account Lockout}

The system shall automatically lock accounts after repeated failed
authentication attempts according to configured security policies.

\paragraph{AWI-146 Password Policy}

Administrators shall configure password complexity policies.

\paragraph{AWI-147 Device Management}

Administrators shall manage trusted devices.

\paragraph{AWI-148 Threat Monitoring}

The portal shall monitor security threats.

\paragraph{AWI-149 Incident Management}

Administrators shall manage security incidents.

\paragraph{AWI-150 Security Reports}

The portal shall generate security reports.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Audit Trail Administration Interface}

\paragraph{AWI-151 Audit Dashboard}

The portal shall provide centralized audit trail management.

\paragraph{AWI-152 Activity Logs}

Administrators shall review system activity logs.

\paragraph{AWI-153 User Logs}

The portal shall maintain user activity records.

\paragraph{AWI-154 Administrative Logs}

Administrative operations shall be logged.

\paragraph{AWI-155 Search Logs}

Audit logs shall support advanced searching.

\paragraph{AWI-156 Log Filtering}

Logs shall support filtering by user, date, organization, and activity.

\paragraph{AWI-157 Log Export}

Authorized administrators shall export audit logs.

\paragraph{AWI-158 Log Retention}

Audit logs shall comply with configured retention policies.

\paragraph{AWI-159 Log Integrity}

Audit records shall be tamper-resistant.

\paragraph{AWI-160 Audit Reports}

The portal shall generate audit reports.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Backup and Disaster Recovery Interface}

\paragraph{AWI-161 Backup Dashboard}

The portal shall display backup status.

\paragraph{AWI-162 Backup Scheduling}

Administrators shall configure automated backup schedules.

\paragraph{AWI-163 Backup Execution}

Authorized administrators shall initiate manual backups.

\paragraph{AWI-164 Backup Verification}

The system shall verify backup integrity.

\paragraph{AWI-165 Backup History}

The portal shall maintain backup history.

\paragraph{AWI-166 Disaster Recovery}

Administrators shall initiate disaster recovery procedures.

\paragraph{AWI-167 Restore Operations}

Authorized administrators shall restore approved backups.

\paragraph{AWI-168 Recovery Validation}

Recovery operations shall be validated after completion.

\paragraph{AWI-169 Recovery Reports}

The portal shall generate recovery reports.

\paragraph{AWI-170 Backup Notifications}

Administrators shall receive backup and recovery notifications.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{System Configuration Interface}

\paragraph{AWI-171 Platform Configuration}

Administrators shall configure global platform settings.

\paragraph{AWI-172 Module Configuration}

Administrators shall enable or disable supported modules.

\paragraph{AWI-173 Notification Configuration}

The portal shall configure notification services.

\paragraph{AWI-174 API Configuration}

Administrators shall configure external API integrations.

\paragraph{AWI-175 AI Configuration}

Administrators shall configure AI service parameters.

\paragraph{AWI-176 GIS Configuration}

Administrators shall configure GIS services.

\paragraph{AWI-177 Payment Configuration}

Administrators shall configure payment gateway settings.

\paragraph{AWI-178 Email Configuration}

Administrators shall configure email services.

\paragraph{AWI-179 SMS Configuration}

Administrators shall configure SMS gateway services.

\paragraph{AWI-180 System Maintenance Mode}

Administrators shall place the platform into maintenance mode when
required.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Validation Rules}

\begin{itemize}

\item Only authorized platform administrators shall access
administrative functions.

\item Administrative operations shall require appropriate permissions.

\item Critical administrative actions shall be recorded by the Audit
Trail and Activity Logging Module.

\item Platform configuration changes shall require validation before
being applied.

\item Security policies shall comply with organizational governance
requirements.

\item Financial reports shall be generated only from verified
transaction records.

\item Backup operations shall be validated before completion.

\item AI model deployments shall require administrative approval.

\item External system integrations shall use secure authenticated
connections.

\item Administrative activities shall comply with organizational
security and compliance policies.

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Acceptance Criteria}

\paragraph{AAC-001}

Administrators can successfully manage all platform users and
organizations.

\paragraph{AAC-002}

Operational activities are monitored in real time.

\paragraph{AAC-003}

Platform security policies are enforced correctly.

\paragraph{AAC-004}

Financial, operational, and environmental reports are generated
accurately.

\paragraph{AAC-005}

Marketplace operations are administered successfully.

\paragraph{AAC-006}

AI, GIS, IoT, and external services are managed securely.

\paragraph{AAC-007}

Backup and disaster recovery operations function successfully.

\paragraph{AAC-008}

Audit logs accurately record all administrative activities.

\paragraph{AAC-009}

Platform configuration changes are securely controlled.

\paragraph{AAC-010}

The Administrator Web Portal provides a secure, scalable, enterprise-
grade operational control centre for the EcoTrace Intelligent
Electronic Waste Recovery and Circular Economy Management System.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Super Administrator Portal}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Purpose}

The Super Administrator Portal shall provide the highest level of
administrative control over the EcoTrace Intelligent Electronic Waste
Recovery and Circular Economy Management System.

The portal shall enable platform owners to manage global system
configuration, tenant organizations, platform licensing, artificial
intelligence services, cloud infrastructure, cybersecurity policies,
system monitoring, deployments, disaster recovery, platform analytics,
and enterprise governance.

The Super Administrator Portal shall only be accessible to authorized
Super Administrators possessing the highest system privileges.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Primary Users}

\begin{itemize}

\item Platform Owner

\item Chief System Administrator

\item Enterprise Platform Administrator

\item Chief Information Officer (CIO)

\item Enterprise Security Administrator

\item Platform Governance Team

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Main Navigation}

The Super Administrator Portal shall provide the following navigation
menu:

\begin{itemize}

\item Global Dashboard

\item Tenant Management

\item Platform Administration

\item Security Center

\item AI Governance

\item Cloud Infrastructure

\item Monitoring

\item Audit Center

\item Disaster Recovery

\item Licensing

\item DevOps

\item Reports

\item Settings

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Global Dashboard Components}

The dashboard shall display:

\begin{itemize}

\item Platform Status

\item Active Organizations

\item Active Users

\item Cloud Infrastructure Status

\item AI Services Status

\item Security Alerts

\item Global Analytics

\item Storage Utilization

\item API Usage

\item Revenue Summary

\item System Health

\item Disaster Recovery Status

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Super Administrator Interface Requirements}

\paragraph{SAI-001 Global Dashboard}

The portal shall display a centralized enterprise dashboard.

\paragraph{SAI-002 Platform Health}

The dashboard shall display overall platform health.

\paragraph{SAI-003 Active Organizations}

The dashboard shall display active tenant organizations.

\paragraph{SAI-004 Active Users}

The dashboard shall display active platform users.

\paragraph{SAI-005 Infrastructure Status}

The dashboard shall display infrastructure health.

\paragraph{SAI-006 Security Status}

The dashboard shall display enterprise security status.

\paragraph{SAI-007 AI Status}

The dashboard shall display AI service health.

\paragraph{SAI-008 Global Notifications}

Unread enterprise notifications shall be prominently displayed.

\paragraph{SAI-009 Global Analytics}

The dashboard shall display enterprise analytics.

\paragraph{SAI-010 Quick Administration}

The dashboard shall provide shortcuts to global administrative
functions.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Tenant Management Interface}

\paragraph{SAI-011 Tenant Registration}

Super Administrators shall register tenant organizations.

\paragraph{SAI-012 Tenant Approval}

The portal shall approve tenant registration requests.

\paragraph{SAI-013 Tenant Suspension}

Super Administrators shall suspend tenant organizations.

\paragraph{SAI-014 Tenant Reactivation}

Suspended organizations shall be reactivated.

\paragraph{SAI-015 Tenant Configuration}

Tenant-specific platform settings shall be configurable.

\paragraph{SAI-016 Tenant Storage}

The portal shall monitor tenant storage utilization.

\paragraph{SAI-017 Tenant Billing}

The portal shall manage tenant billing information.

\paragraph{SAI-018 Tenant Usage}

The portal shall monitor tenant platform usage.

\paragraph{SAI-019 Tenant Analytics}

The portal shall display tenant performance analytics.

\paragraph{SAI-020 Tenant Audit}

Tenant administrative activities shall be audited.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Platform Administration Interface}

\paragraph{SAI-021 Platform Dashboard}

The portal shall provide a centralized platform administration dashboard.

\paragraph{SAI-022 Platform Configuration}

Super Administrators shall configure global platform settings.

\paragraph{SAI-023 Module Management}

The portal shall enable or disable platform modules.

\paragraph{SAI-024 Feature Management}

Super Administrators shall manage platform feature availability.

\paragraph{SAI-025 System Parameters}

The portal shall configure global system parameters.

\paragraph{SAI-026 Regional Configuration}

The platform shall support country and regional configuration.

\paragraph{SAI-027 Time Zone Configuration}

The portal shall configure global time zone settings.

\paragraph{SAI-028 Localization}

The platform shall manage supported languages and localization.

\paragraph{SAI-029 Platform Availability}

Super Administrators shall place the platform into maintenance mode.

\paragraph{SAI-030 Platform Status}

The portal shall continuously monitor overall platform operational
status.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Global User Governance Interface}

\paragraph{SAI-031 Global User Directory}

The portal shall maintain a centralized directory of all platform users.

\paragraph{SAI-032 Global User Search}

Super Administrators shall search users across all organizations.

\paragraph{SAI-033 Cross-Tenant User Monitoring}

The portal shall monitor user activities across all tenants.

\paragraph{SAI-034 Global Role Management}

Super Administrators shall define platform-wide roles.

\paragraph{SAI-035 Permission Templates}

The portal shall support reusable permission templates.

\paragraph{SAI-036 Privileged Account Monitoring}

The portal shall monitor privileged user accounts.

\paragraph{SAI-037 Account Lockout}

The system shall enforce account lockout policies.

\paragraph{SAI-038 Account Recovery}

Super Administrators shall recover privileged accounts.

\paragraph{SAI-039 Global Authentication}

The portal shall configure enterprise authentication services.

\paragraph{SAI-040 User Governance Reports}

The portal shall generate enterprise user governance reports.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Platform Licensing Interface}

\paragraph{SAI-041 License Dashboard}

The portal shall display platform licensing information.

\paragraph{SAI-042 License Management}

Super Administrators shall manage platform licenses.

\paragraph{SAI-043 Subscription Plans}

The platform shall support multiple subscription plans.

\paragraph{SAI-044 Tenant Subscription}

Tenant subscriptions shall be managed centrally.

\paragraph{SAI-045 License Renewal}

The portal shall monitor upcoming license renewals.

\paragraph{SAI-046 License Expiration}

The system shall notify administrators before license expiration.

\paragraph{SAI-047 Usage Limits}

The platform shall enforce subscription usage limits.

\paragraph{SAI-048 Billing Summary}

The portal shall display enterprise billing summaries.

\paragraph{SAI-049 Invoice Management}

Super Administrators shall manage enterprise invoices.

\paragraph{SAI-050 Licensing Reports}

The portal shall generate licensing reports.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Artificial Intelligence Governance Interface}

\paragraph{SAI-051 AI Governance Dashboard}

The portal shall provide enterprise AI governance dashboards.

\paragraph{SAI-052 AI Model Registry}

The platform shall maintain a registry of approved AI models.

\paragraph{SAI-053 Model Approval}

Only approved AI models shall be deployed into production.

\paragraph{SAI-054 Model Version Control}

The platform shall maintain AI model version history.

\paragraph{SAI-055 AI Performance Monitoring}

The portal shall monitor AI performance metrics.

\paragraph{SAI-056 AI Drift Detection}

The system shall detect significant degradation in AI model
performance.

\paragraph{SAI-057 Dataset Governance}

Training datasets shall be managed according to organizational
governance policies.

\paragraph{SAI-058 AI Deployment}

Super Administrators shall deploy AI models to production.

\paragraph{SAI-059 AI Rollback}

The platform shall support rollback to previous AI model versions.

\paragraph{SAI-060 AI Governance Reports}

The portal shall generate enterprise AI governance reports.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Cloud Infrastructure Interface}

\paragraph{SAI-061 Infrastructure Dashboard}

The portal shall display cloud infrastructure status.

\paragraph{SAI-062 Compute Resources}

The portal shall monitor compute resource utilization.

\paragraph{SAI-063 Storage Resources}

The portal shall monitor storage utilization.

\paragraph{SAI-064 Database Services}

The portal shall monitor database performance.

\paragraph{SAI-065 Network Services}

The portal shall monitor network availability.

\paragraph{SAI-066 Cloud Functions}

The portal shall monitor cloud function execution.

\paragraph{SAI-067 Service Availability}

The system shall continuously monitor platform service availability.

\paragraph{SAI-068 Performance Metrics}

Infrastructure performance metrics shall be displayed in real time.

\paragraph{SAI-069 Infrastructure Alerts}

Infrastructure failures shall generate immediate alerts.

\paragraph{SAI-070 Infrastructure Reports}

The portal shall generate cloud infrastructure reports.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Enterprise Security Governance Interface}

\paragraph{SAI-071 Security Dashboard}

The portal shall provide a centralized enterprise security dashboard.

\paragraph{SAI-072 Threat Detection}

The system shall detect suspicious security activities.

\paragraph{SAI-073 Intrusion Monitoring}

The portal shall monitor unauthorized access attempts.

\paragraph{SAI-074 Security Policies}

Super Administrators shall configure enterprise security policies.

\paragraph{SAI-075 Encryption Management}

The portal shall manage encryption policies.

\paragraph{SAI-076 API Security}

The portal shall manage API authentication and authorization policies.

\paragraph{SAI-077 Vulnerability Monitoring}

The platform shall monitor known vulnerabilities.

\paragraph{SAI-078 Security Alerts}

Critical security events shall trigger immediate alerts.

\paragraph{SAI-079 Incident Response}

The portal shall support enterprise security incident response.

\paragraph{SAI-080 Security Compliance}

The portal shall generate enterprise security compliance reports.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Audit Governance Interface}

\paragraph{SAI-081 Enterprise Audit Dashboard}

The portal shall provide a centralized enterprise audit dashboard.

\paragraph{SAI-082 Global Audit Logs}

The portal shall maintain immutable audit logs for all platform
activities.

\paragraph{SAI-083 Cross-Tenant Audit}

Super Administrators shall review audit logs across all tenant
organizations.

\paragraph{SAI-084 Administrative Audit}

All administrative actions shall be permanently recorded.

\paragraph{SAI-085 Security Audit}

Security-related activities shall be separately categorized for audit
purposes.

\paragraph{SAI-086 Configuration Audit}

System configuration changes shall be recorded with timestamps, user
identity, and previous values where applicable.

\paragraph{SAI-087 Audit Search}

The portal shall support advanced audit searching and filtering.

\paragraph{SAI-088 Audit Export}

Authorized users shall export audit records.

\paragraph{SAI-089 Audit Retention}

Audit records shall be retained according to configured retention
policies.

\paragraph{SAI-090 Audit Integrity}

Audit records shall be protected against unauthorized modification.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Disaster Recovery Governance Interface}

\paragraph{SAI-091 Disaster Recovery Dashboard}

The portal shall display disaster recovery readiness status.

\paragraph{SAI-092 Backup Monitoring}

The portal shall monitor backup operations across the platform.

\paragraph{SAI-093 Backup Scheduling}

Super Administrators shall configure enterprise backup schedules.

\paragraph{SAI-094 Backup Verification}

The system shall verify backup integrity after every completed backup.

\paragraph{SAI-095 Restore Operations}

Authorized Super Administrators shall initiate system restoration.

\paragraph{SAI-096 Recovery Point Objective}

The portal shall monitor configured Recovery Point Objectives (RPO).

\paragraph{SAI-097 Recovery Time Objective}

The portal shall monitor configured Recovery Time Objectives (RTO).

\paragraph{SAI-098 Disaster Recovery Testing}

The portal shall support scheduled disaster recovery testing.

\paragraph{SAI-099 Recovery Reporting}

The portal shall generate disaster recovery reports.

\paragraph{SAI-100 Recovery Notifications}

Critical backup and recovery events shall generate administrator
notifications.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{DevOps and Deployment Management Interface}

\paragraph{SAI-101 Deployment Dashboard}

The portal shall provide centralized deployment management.

\paragraph{SAI-102 Environment Management}

The portal shall manage Development, Testing, Staging, and Production
environments.

\paragraph{SAI-103 Release Management}

Super Administrators shall schedule software releases.

\paragraph{SAI-104 Version Management}

The portal shall maintain application version history.

\paragraph{SAI-105 Deployment Approval}

Production deployments shall require administrative approval.

\paragraph{SAI-106 Rollback Management}

The platform shall support rollback to previous stable releases.

\paragraph{SAI-107 Deployment Monitoring}

The portal shall monitor deployment progress.

\paragraph{SAI-108 Deployment Notifications}

Deployment events shall generate notifications.

\paragraph{SAI-109 Deployment History}

The platform shall maintain deployment history.

\paragraph{SAI-110 DevOps Reports}

The portal shall generate deployment reports.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Enterprise Monitoring Interface}

\paragraph{SAI-111 Enterprise Monitoring Dashboard}

The portal shall provide enterprise-wide operational monitoring.

\paragraph{SAI-112 System Availability}

The portal shall continuously monitor system availability.

\paragraph{SAI-113 Service Health}

The portal shall monitor health status of all platform services.

\paragraph{SAI-114 API Monitoring}

The portal shall monitor API performance.

\paragraph{SAI-115 Database Monitoring}

Database performance shall be continuously monitored.

\paragraph{SAI-116 Storage Monitoring}

Storage utilization shall be continuously monitored.

\paragraph{SAI-117 Resource Monitoring}

CPU, memory, and network utilization shall be monitored.

\paragraph{SAI-118 Performance Alerts}

Threshold violations shall generate automatic alerts.

\paragraph{SAI-119 Capacity Planning}

The portal shall support infrastructure capacity planning.

\paragraph{SAI-120 Monitoring Reports}

The portal shall generate enterprise monitoring reports.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Global Reporting and Analytics Interface}

\paragraph{SAI-121 Executive Dashboard}

The portal shall provide executive-level dashboards.

\paragraph{SAI-122 Platform Analytics}

The portal shall display enterprise platform analytics.

\paragraph{SAI-123 Environmental Analytics}

The portal shall display environmental impact analytics.

\paragraph{SAI-124 Operational Analytics}

Operational performance shall be analyzed across all modules.

\paragraph{SAI-125 Financial Analytics}

Financial performance dashboards shall be available.

\paragraph{SAI-126 AI Analytics}

Enterprise AI performance analytics shall be displayed.

\paragraph{SAI-127 Sustainability Analytics}

The portal shall provide sustainability performance dashboards.

\paragraph{SAI-128 Cross-Tenant Analytics}

The platform shall compare performance across tenant organizations.

\paragraph{SAI-129 Executive Reports}

Executive reports shall be exportable in PDF and spreadsheet formats.

\paragraph{SAI-130 Enterprise KPIs}

The portal shall display enterprise Key Performance Indicators.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Validation Rules}

\begin{itemize}

\item Only authenticated Super Administrators shall access Super
Administrator functions.

\item Platform-wide configuration changes shall require appropriate
authorization.

\item Tenant management operations shall be fully audited.

\item AI model deployments shall require formal approval before
production release.

\item Production deployments shall support rollback procedures.

\item Backup integrity shall be verified before restoration.

\item Global reports shall use verified enterprise data.

\item Security incidents shall be logged immediately.

\item Enterprise monitoring shall operate continuously.

\item All Super Administrator activities shall be permanently recorded
by the Audit Trail and Activity Logging Module.

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Acceptance Criteria}

\paragraph{SAC-001}

Super Administrators can successfully manage the entire EcoTrace
platform.

\paragraph{SAC-002}

Tenant organizations are administered securely.

\paragraph{SAC-003}

Enterprise security governance is enforced successfully.

\paragraph{SAC-004}

Platform deployments and rollbacks execute correctly.

\paragraph{SAC-005}

AI governance functions operate successfully.

\paragraph{SAC-006}

Cloud infrastructure is continuously monitored.

\paragraph{SAC-007}

Disaster recovery procedures are operational.

\paragraph{SAC-008}

Enterprise analytics accurately represent platform activities.

\paragraph{SAC-009}

Global audit logs maintain integrity and traceability.

\paragraph{SAC-010}

The Super Administrator Portal provides a secure, scalable,
enterprise-grade governance platform for managing every aspect of the
EcoTrace Intelligent Electronic Waste Recovery and Circular Economy
Management System.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Windows Desktop Application}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Purpose}

The Windows Desktop Application shall provide authorized EcoTrace users
with a high-performance desktop interface optimized for enterprise
operations requiring intensive data entry, document management,
inventory administration, reporting, repair operations, warehouse
management, and administrative activities.

The application shall provide enhanced productivity through keyboard
shortcuts, multi-window workflows, high-speed data processing,
integration with desktop peripherals, and advanced reporting
capabilities.

The desktop application shall be developed using Flutter Desktop for
Microsoft Windows.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Primary Users}

\begin{itemize}

\item Administrative Officers

\item Warehouse Officers

\item Inventory Officers

\item Repair Workshop Staff

\item Recycling Facility Staff

\item Financial Officers

\item Compliance Officers

\item System Administrators

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Main Navigation}

The Windows Desktop Application shall provide the following navigation
menu:

\begin{itemize}

\item Dashboard

\item Assets

\item Inventory

\item Collections

\item Repairs

\item Recycling

\item Marketplace

\item Reports

\item Documents

\item Notifications

\item Administration

\item Settings

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Desktop Dashboard Components}

The dashboard shall include:

\begin{itemize}

\item User Profile

\item Organization Summary

\item Operational Statistics

\item Inventory Status

\item Active Work Orders

\item Repair Queue

\item Collection Summary

\item Recycling Summary

\item Notifications

\item Performance Charts

\item Recent Activities

\item Quick Actions

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Windows Desktop Interface Requirements}

\paragraph{WDI-001 Desktop Dashboard}

The application shall display a personalized desktop dashboard after
successful authentication.

\paragraph{WDI-002 Workspace}

The application shall provide an enterprise multi-panel workspace.

\paragraph{WDI-003 Window Management}

Users shall resize, maximize, minimize, and restore application windows.

\paragraph{WDI-004 Multi-Window Support}

The application shall support multiple simultaneously open windows.

\paragraph{WDI-005 Navigation Panel}

The application shall provide a collapsible navigation sidebar.

\paragraph{WDI-006 Toolbar}

The application shall provide a customizable toolbar.

\paragraph{WDI-007 Status Bar}

The application shall display synchronization and system status.

\paragraph{WDI-008 Keyboard Shortcuts}

Frequently used operations shall support keyboard shortcuts.

\paragraph{WDI-009 Right-Click Menu}

Desktop components shall support context menus.

\paragraph{WDI-010 Drag-and-Drop}

The application shall support drag-and-drop where appropriate.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Desktop Productivity Interface}

\paragraph{WDI-011 Batch Processing}

The application shall support batch processing of records.

\paragraph{WDI-012 Bulk Editing}

Authorized users shall edit multiple records simultaneously.

\paragraph{WDI-013 Advanced Search}

Desktop users shall perform advanced searches.

\paragraph{WDI-014 Advanced Filtering}

Records shall support advanced filtering.

\paragraph{WDI-015 Sorting}

Data tables shall support multi-column sorting.

\paragraph{WDI-016 Pagination}

Large datasets shall support pagination.

\paragraph{WDI-017 Export}

Users shall export records to PDF, Excel, and CSV.

\paragraph{WDI-018 Printing}

Desktop users shall print reports and documents.

\paragraph{WDI-019 Report Preview}

Reports shall support print preview.

\paragraph{WDI-020 Clipboard Support}

The application shall support copy and paste operations.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Inventory and Warehouse Interface}

\paragraph{WDI-021 Inventory Dashboard}

The application shall provide a centralized inventory management
dashboard.

\paragraph{WDI-022 Inventory Search}

Users shall search inventory records using advanced search criteria.

\paragraph{WDI-023 Inventory Filtering}

Inventory records shall support advanced filtering.

\paragraph{WDI-024 Inventory Adjustment}

Authorized users shall adjust inventory quantities.

\paragraph{WDI-025 Inventory Transfer}

The application shall support inventory transfers between facilities.

\paragraph{WDI-026 Inventory Verification}

Inventory verification activities shall be recorded.

\paragraph{WDI-027 Inventory Reconciliation}

The application shall support inventory reconciliation procedures.

\paragraph{WDI-028 Warehouse Locations}

Inventory shall be organized according to warehouse storage locations.

\paragraph{WDI-029 Stock Alerts}

The application shall notify users of low inventory levels.

\paragraph{WDI-030 Inventory Reports}

Inventory reports shall be generated automatically.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Desktop Data Entry Interface}

\paragraph{WDI-031 High-Speed Data Entry}

The application shall support high-speed keyboard-based data entry.

\paragraph{WDI-032 Keyboard Navigation}

Users shall navigate all interface components using the keyboard.

\paragraph{WDI-033 Keyboard Shortcuts}

Frequently used operations shall support configurable keyboard
shortcuts.

\paragraph{WDI-034 Auto-Completion}

Frequently entered values shall support auto-completion.

\paragraph{WDI-035 Data Validation}

The application shall validate data before submission.

\paragraph{WDI-036 Mandatory Fields}

Mandatory fields shall be clearly identified.

\paragraph{WDI-037 Auto Save}

Long-running forms shall support automatic draft saving.

\paragraph{WDI-038 Bulk Data Import}

The application shall import data from approved spreadsheet formats.

\paragraph{WDI-039 Bulk Data Export}

Data shall be exportable to Excel, CSV, and PDF.

\paragraph{WDI-040 Error Highlighting}

Validation errors shall be clearly highlighted.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Peripheral Device Integration}

\paragraph{WDI-041 QR Code Scanner}

The application shall support USB and wireless QR code scanners.

\paragraph{WDI-042 Barcode Scanner}

The application shall support USB and wireless barcode scanners.

\paragraph{WDI-043 Label Printer}

The application shall support label printer integration.

\paragraph{WDI-044 Document Printer}

Users shall print reports and certificates.

\paragraph{WDI-045 Camera Integration}

Desktop cameras shall be supported where available.

\paragraph{WDI-046 External Storage}

The application shall support approved external storage devices.

\paragraph{WDI-047 Digital Signature Device}

The application shall support compatible digital signature devices.

\paragraph{WDI-048 Multiple Monitor Support}

The desktop application shall support multiple display monitors.

\paragraph{WDI-049 Network Printer}

Users shall print to authorized network printers.

\paragraph{WDI-050 Peripheral Status}

The application shall display connected peripheral device status.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Document Management Interface}

\paragraph{WDI-051 Document Repository}

The application shall provide centralized document management.

\paragraph{WDI-052 File Upload}

Users shall upload supporting documents.

\paragraph{WDI-053 File Download}

Authorized users shall securely download documents.

\paragraph{WDI-054 File Preview}

Supported documents shall be previewed before download.

\paragraph{WDI-055 Version Control}

The application shall maintain document version history.

\paragraph{WDI-056 Document Approval}

Documents shall support approval workflows.

\paragraph{WDI-057 Digital Certificates}

The application shall generate digital certificates.

\paragraph{WDI-058 Report Archive}

Historical reports shall remain accessible.

\paragraph{WDI-059 Document Search}

Users shall search documents using multiple criteria.

\paragraph{WDI-060 Secure Storage}

Documents shall be securely stored according to organizational
retention policies.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Offline Operation}

\paragraph{WDI-061 Offline Mode}

The application shall support offline desktop operations.

\paragraph{WDI-062 Offline Data Entry}

Users shall continue entering records while offline.

\paragraph{WDI-063 Offline Queue}

Offline operations shall be stored in a synchronization queue.

\paragraph{WDI-064 Automatic Synchronization}

Offline records shall synchronize automatically after connectivity is
restored.

\paragraph{WDI-065 Synchronization Status}

The application shall display synchronization progress.

\paragraph{WDI-066 Conflict Resolution}

Synchronization conflicts shall be resolved according to business rules.

\paragraph{WDI-067 Local Cache}

Frequently accessed information shall be cached locally.

\paragraph{WDI-068 Backup Queue}

Offline backup copies shall be maintained until synchronization
completes.

\paragraph{WDI-069 Offline Audit}

Offline activities shall be audited after synchronization.

\paragraph{WDI-070 Data Integrity}

The application shall verify data integrity before synchronization.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Validation Rules}

\begin{itemize}

\item Only authenticated desktop users shall access desktop functions.

\item Bulk operations shall validate all records before processing.

\item Imported files shall conform to approved formats.

\item Peripheral devices shall be verified before use.

\item Reports shall only contain authorized information.

\item Offline records shall synchronize successfully before permanent
storage.

\item Printed reports shall include document identification numbers.

\item Desktop activities shall comply with organizational security
policies.

\item Unauthorized users shall not access desktop administration
functions.

\item All desktop operations shall be recorded by the Audit Trail and
Activity Logging Module.

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Acceptance Criteria}

\paragraph{DAC-001}

Desktop users can efficiently perform high-volume operational tasks.

\paragraph{DAC-002}

Peripheral devices integrate successfully with the application.

\paragraph{DAC-003}

Bulk data import and export operate correctly.

\paragraph{DAC-004}

Inventory operations execute accurately.

\paragraph{DAC-005}

Reports and certificates are generated and printed successfully.

\paragraph{DAC-006}

Offline desktop activities synchronize successfully.

\paragraph{DAC-007}

Enterprise document management operates securely.

\paragraph{DAC-008}

Desktop productivity features improve operational efficiency.

\paragraph{DAC-009}

Desktop activities are completely auditable.

\paragraph{DAC-010}

The Windows Desktop Application provides a secure, scalable,
high-performance enterprise interface for administrative, warehouse,
repair, inventory, and reporting operations within the EcoTrace
platform.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Accessibility Requirements}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Overview}

The EcoTrace platform shall be designed to provide an accessible,
inclusive, and user-friendly experience for all users, including persons
with disabilities. Accessibility requirements shall apply consistently
across Android mobile applications, Web applications, and Windows
Desktop applications.

The user interface shall follow internationally recognized accessibility
principles, including the Web Content Accessibility Guidelines (WCAG)
2.1 Level AA where applicable.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Accessibility Principles}

The EcoTrace platform shall be designed according to the following
principles:

\begin{itemize}

\item Perceivable

\item Operable

\item Understandable

\item Robust

\item Inclusive

\item Consistent

\item Responsive

\item Accessible by Design

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Accessibility Interface Requirements}

\paragraph{AIR-001 Keyboard Accessibility}

All system functionality shall be accessible using only a keyboard.

\paragraph{AIR-002 Keyboard Navigation}

Users shall navigate all menus, forms, and controls using keyboard
navigation.

\paragraph{AIR-003 Focus Indicator}

Interactive interface elements shall display visible keyboard focus.

\paragraph{AIR-004 Screen Reader Support}

The platform shall support modern screen readers.

\paragraph{AIR-005 Alternative Text}

Meaningful images and icons shall provide descriptive alternative text.

\paragraph{AIR-006 Form Labels}

All form controls shall include descriptive labels.

\paragraph{AIR-007 Error Identification}

Validation errors shall be clearly identified and explained.

\paragraph{AIR-008 Error Suggestions}

Error messages shall include recommendations for correction.

\paragraph{AIR-009 Colour Independence}

Important information shall not rely solely on colour.

\paragraph{AIR-010 Colour Contrast}

Text and interface components shall maintain sufficient colour contrast.

\paragraph{AIR-011 Text Scaling}

Users shall enlarge interface text without loss of functionality.

\paragraph{AIR-012 Responsive Layout}

Accessibility shall be maintained across different screen sizes.

\paragraph{AIR-013 High Contrast Mode}

The platform shall support high contrast display modes.

\paragraph{AIR-014 Dark Mode}

The platform shall support Dark Mode.

\paragraph{AIR-015 Light Mode}

The platform shall support Light Mode.

\paragraph{AIR-016 Readable Typography}

The interface shall use clear and readable fonts.

\paragraph{AIR-017 Consistent Navigation}

Navigation components shall remain consistent throughout the platform.

\paragraph{AIR-018 Accessible Buttons}

Buttons shall provide sufficient size for touch interaction.

\paragraph{AIR-019 Accessible Forms}

Forms shall provide accessible validation and navigation.

\paragraph{AIR-020 Accessible Tables}

Data tables shall support accessible navigation.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Multilingual Accessibility}

\paragraph{AIR-021 Language Selection}

Users shall select their preferred language.

\paragraph{AIR-022 Localization}

The platform shall support localization of interface text.

\paragraph{AIR-023 Date Formats}

Dates shall follow regional formatting standards.

\paragraph{AIR-024 Number Formats}

Numbers shall follow regional formatting standards.

\paragraph{AIR-025 Currency Formats}

Currency values shall support regional configuration.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Accessibility Validation Rules}

\begin{itemize}

\item All major workflows shall remain accessible using only the keyboard.

\item Screen readers shall correctly identify interface components.

\item Colour shall never be the only indicator of status.

\item Accessibility shall be preserved after interface updates.

\item Accessibility testing shall be performed before every production
release.

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Accessibility Acceptance Criteria}

\paragraph{AAC-001}

Users can complete all major workflows using keyboard navigation.

\paragraph{AAC-002}

Screen readers correctly interpret user interface components.

\paragraph{AAC-003}

Interface text remains readable after scaling.

\paragraph{AAC-004}

Colour contrast satisfies accessibility requirements.

\paragraph{AAC-005}

The EcoTrace platform provides an inclusive and accessible user
experience across Android, Web, and Windows Desktop applications.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Hardware Interface Requirements}

\subsection{Overview}

The Hardware Interface Requirements specify the physical devices,
equipment, sensors, and hardware components that interact with the
EcoTrace Intelligent Electronic Waste Recovery and Circular Economy
Management System.

The EcoTrace platform shall operate across Android mobile devices,
Windows desktop computers, cloud servers, barcode scanners, QR code
scanners, GPS receivers, digital cameras, printers, and future Internet
of Things (IoT) devices. These hardware interfaces enable data capture,
asset identification, geolocation, reporting, communication, and
operational monitoring.

All supported hardware devices shall communicate securely with the
platform and comply with the minimum technical specifications defined in
this chapter.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Android Mobile Devices}

Android smartphones and tablets shall serve as the primary mobile
platform for household users, business users, collectors, drivers,
technicians, recyclers, and field officers.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Supported Devices}

The application shall support:

\begin{itemize}

\item Android smartphones

\item Android tablets

\item Rugged industrial Android devices

\item Enterprise handheld terminals

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Hardware Requirements}

\paragraph{HIR-001 Operating System}

The mobile application shall support Android 10 (API Level 29) or
higher.

\paragraph{HIR-002 Processor}

Devices should contain a 64-bit ARM processor.

\paragraph{HIR-003 Memory}

Devices should contain at least 4 GB RAM.

\paragraph{HIR-004 Storage}

Devices should provide at least 2 GB available storage for application
data.

\paragraph{HIR-005 Camera}

Devices shall include an integrated camera for image capture, QR code
scanning, and documentation.

\paragraph{HIR-006 GPS}

Devices shall include GPS hardware supporting real-time location
services.

\paragraph{HIR-007 Internet Connectivity}

Devices shall support Wi-Fi and/or mobile data connectivity.

\paragraph{HIR-008 Bluetooth}

Devices shall support Bluetooth communication with approved peripherals.

\paragraph{HIR-009 Biometrics}

Devices may support fingerprint or facial authentication where
available.

\paragraph{HIR-010 Battery}

Devices should provide sufficient battery capacity for extended field
operations.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Windows Computers}

Windows desktop and laptop computers shall support administrative,
warehouse, repair workshop, financial, reporting, inventory, and system
administration operations through the EcoTrace Windows Desktop
Application.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Supported Devices}

The desktop application shall support:

\begin{itemize}

\item Desktop computers

\item Laptop computers

\item All-in-One computers

\item Industrial workstation computers

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Hardware Requirements}

\paragraph{HIR-011 Operating System}

The desktop application shall support Microsoft Windows 10 (64-bit) and
Windows 11 (64-bit).

\paragraph{HIR-012 Processor}

The computer shall contain a dual-core processor operating at a minimum
clock speed of 2.0 GHz. Quad-core processors are recommended for
enterprise deployments.

\paragraph{HIR-013 Memory}

The computer shall contain at least 8 GB RAM. Enterprise deployments
should provide 16 GB RAM or higher.

\paragraph{HIR-014 Storage}

The computer shall provide at least 10 GB of available storage for
application files, reports, and cached data. Solid-State Drives (SSD)
are recommended.

\paragraph{HIR-015 Display Resolution}

The application shall support a minimum display resolution of
1920 × 1080 pixels.

\paragraph{HIR-016 Keyboard and Mouse}

The system shall support standard USB and wireless keyboards and mice.

\paragraph{HIR-017 Network Connectivity}

The computer shall support Ethernet and Wi-Fi network connectivity.

\paragraph{HIR-018 USB Interfaces}

The application shall support USB-connected peripheral devices including
barcode scanners, QR code scanners, printers, and external storage
devices.

\paragraph{HIR-019 Audio Devices}

The application shall support speakers and microphones for multimedia
notifications and communication features where applicable.

\paragraph{HIR-020 Power Protection}

Enterprise deployments should utilize Uninterruptible Power Supply
(UPS) devices to minimize operational disruption during power failures.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Digital Cameras}

Digital cameras shall capture images of electronic waste, repair
activities, recycling operations, collection evidence, inventory
records, and supporting documentation.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Hardware Requirements}

\paragraph{HIR-021 Camera Resolution}

The camera shall support a minimum resolution of 8 megapixels.

\paragraph{HIR-022 Image Format}

The system shall support JPEG, PNG, and WebP image formats.

\paragraph{HIR-023 Auto Focus}

The camera shall support automatic focus functionality.

\paragraph{HIR-024 Flash Support}

The camera shall support flash operation in low-light environments.

\paragraph{HIR-025 Image Compression}

Captured images shall be automatically compressed before upload.

\paragraph{HIR-026 Image Metadata}

The system shall record timestamps and image metadata where supported.

\paragraph{HIR-027 GPS Metadata}

Captured images shall include GPS coordinates when location services
are enabled.

\paragraph{HIR-028 Multiple Image Capture}

The application shall support capturing multiple photographs per
operation.

\paragraph{HIR-029 Camera Permissions}

Users shall grant camera permissions before image capture.

\paragraph{HIR-030 Camera Validation}

The application shall verify image quality before upload.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Global Positioning System (GPS)}

GPS hardware shall support navigation, pickup verification, route
optimization, geofencing, asset tracking, and operational monitoring.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Hardware Requirements}

\paragraph{HIR-031 GPS Receiver}

Mobile devices shall include integrated GPS receivers.

\paragraph{HIR-032 Location Accuracy}

GPS accuracy should be within 10 meters under normal operating
conditions.

\paragraph{HIR-033 Continuous Tracking}

The application shall support continuous location tracking for
authorized users.

\paragraph{HIR-034 Route Recording}

The application shall record transportation routes.

\paragraph{HIR-035 Geofencing}

GPS hardware shall support geofencing functionality.

\paragraph{HIR-036 Location History}

The application shall maintain GPS location history where authorized.

\paragraph{HIR-037 Offline GPS}

Previously downloaded maps shall support offline navigation.

\paragraph{HIR-038 Location Permissions}

Users shall explicitly authorize location access.

\paragraph{HIR-039 Secure Transmission}

GPS information shall be securely transmitted to cloud services.

\paragraph{HIR-040 GPS Validation}

The application shall validate received GPS coordinates before storage.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{QR Code Scanners}

QR code scanning hardware shall support electronic asset
identification, inventory verification, collection tracking, repair
operations, recycling workflows, and document verification throughout
the EcoTrace platform.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Hardware Requirements}

\paragraph{HIR-041 QR Code Support}

The system shall support scanning of standard QR Code symbols compliant
with ISO/IEC 18004.

\paragraph{HIR-042 Integrated Camera Scanning}

Android mobile device cameras shall function as QR code scanners.

\paragraph{HIR-043 External QR Scanners}

The platform shall support USB and Bluetooth QR code scanners.

\paragraph{HIR-044 Scan Accuracy}

QR code scanners shall accurately decode supported QR codes under
normal operating conditions.

\paragraph{HIR-045 Scan Speed}

QR codes shall be decoded within two seconds under normal lighting
conditions.

\paragraph{HIR-046 Damaged Code Recognition}

The system shall attempt to decode partially damaged QR codes where
technically feasible.

\paragraph{HIR-047 Duplicate Detection}

The platform shall detect duplicate QR code registrations.

\paragraph{HIR-048 Secure Verification}

Scanned QR codes shall be validated against the EcoTrace database.

\paragraph{HIR-049 Scan Logging}

All QR code scanning activities shall be recorded for auditing.

\paragraph{HIR-050 Error Notification}

The application shall notify users when QR codes cannot be decoded.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Barcode Scanners}

Barcode scanners shall support inventory management, warehouse
operations, repair centres, recycling facilities, and logistics
operations.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Hardware Requirements}

\paragraph{HIR-051 Barcode Standards}

The platform shall support common one-dimensional and
two-dimensional barcode standards.

\paragraph{HIR-052 USB Barcode Scanners}

The platform shall support USB-connected barcode scanners.

\paragraph{HIR-053 Bluetooth Barcode Scanners}

The platform shall support Bluetooth barcode scanners.

\paragraph{HIR-054 Wireless Operation}

Wireless barcode scanners shall operate within supported communication
ranges.

\paragraph{HIR-055 Scan Validation}

Scanned barcode values shall be validated before processing.

\paragraph{HIR-056 Inventory Lookup}

Barcode scans shall automatically retrieve corresponding inventory
records.

\paragraph{HIR-057 Batch Scanning}

The application shall support continuous barcode scanning for batch
operations.

\paragraph{HIR-058 Scan History}

The system shall maintain barcode scan history.

\paragraph{HIR-059 Error Detection}

Invalid barcode values shall generate validation errors.

\paragraph{HIR-060 Barcode Audit}

Barcode scanning activities shall be recorded by the Audit Trail and
Activity Logging Module.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Printers}

Printing hardware shall support labels, certificates, invoices,
receipts, reports, inventory documents, and operational forms.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Hardware Requirements}

\paragraph{HIR-061 Report Printing}

The platform shall support printing reports on standard office printers.

\paragraph{HIR-062 Label Printing}

The platform shall support compatible label printers.

\paragraph{HIR-063 Receipt Printing}

The platform shall support thermal receipt printers where required.

\paragraph{HIR-064 PDF Printing}

Generated PDF documents shall be printable.

\paragraph{HIR-065 Network Printers}

The desktop application shall support authorized network printers.

\paragraph{HIR-066 Printer Detection}

The application shall detect available printers automatically.

\paragraph{HIR-067 Print Preview}

Users shall preview documents before printing.

\paragraph{HIR-068 Print Queue}

The application shall monitor print queue status.

\paragraph{HIR-069 Print Confirmation}

Users shall receive confirmation after successful printing.

\paragraph{HIR-070 Printer Error Handling}

The application shall notify users of printer-related errors.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{IoT Sensors (Future Expansion)}

Future versions of EcoTrace may integrate Internet of Things (IoT)
devices to improve operational efficiency, environmental monitoring,
asset tracking, and smart waste management.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Hardware Requirements}

\paragraph{HIR-071 Sensor Registration}

The platform shall support registration of approved IoT devices.

\paragraph{HIR-072 Sensor Monitoring}

The system shall continuously monitor connected IoT sensors.

\paragraph{HIR-073 Environmental Sensors}

The platform shall support temperature, humidity, and environmental
monitoring sensors.

\paragraph{HIR-074 Smart Bin Sensors}

Future smart electronic waste collection bins shall communicate with
the platform.

\paragraph{HIR-075 Weight Sensors}

The platform shall support electronic weighing sensors.

\paragraph{HIR-076 Fill-Level Sensors}

Smart containers shall report fill-level information where deployed.

\paragraph{HIR-077 Connectivity}

IoT devices shall communicate using approved secure communication
protocols.

\paragraph{HIR-078 Remote Configuration}

Authorized administrators shall remotely configure supported IoT
devices.

\paragraph{HIR-079 Firmware Updates}

Supported IoT devices shall receive secure firmware updates.

\paragraph{HIR-080 Device Security}

IoT devices shall authenticate securely before exchanging information
with the EcoTrace platform.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection*{Hardware Validation Rules}

\begin{itemize}

\item All supported hardware devices shall be compatible with approved
platform specifications.

\item Hardware devices shall communicate securely using authenticated
connections.

\item Captured images, GPS coordinates, and scanned codes shall be
validated before storage.

\item Peripheral devices shall be detected before operational use.

\item Printer operations shall verify successful document generation.

\item IoT devices shall authenticate before transmitting sensor data.

\item Hardware failures shall generate user notifications and audit
records.

\item Hardware communication errors shall be logged.

\item Device firmware shall comply with approved versions where
applicable.

\item All hardware interactions shall be recorded by the Audit Trail
and Activity Logging Module.

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection*{Hardware Acceptance Criteria}

\paragraph{HAC-001}

Android devices successfully operate the EcoTrace mobile application.

\paragraph{HAC-002}

Windows computers successfully operate the EcoTrace desktop
application.

\paragraph{HAC-003}

Digital cameras capture images with acceptable quality.

\paragraph{HAC-004}

GPS hardware provides accurate operational locations.

\paragraph{HAC-005}

QR code and barcode scanners accurately identify electronic assets.

\paragraph{HAC-006}

Reports, labels, and certificates print successfully.

\paragraph{HAC-007}

Supported peripheral devices integrate correctly with the platform.

\paragraph{HAC-008}

Future IoT devices communicate securely with the platform.

\paragraph{HAC-009}

Hardware failures are detected and reported appropriately.

\paragraph{HAC-010}

The EcoTrace platform operates reliably across all approved hardware
devices and peripherals.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Software Interface Requirements}

\subsection{Overview}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Software Interface Requirements}

\subsection{Overview}

The Software Interface Requirements define the software platforms,
frameworks, databases, cloud services, application programming
interfaces (APIs), middleware, artificial intelligence services, and
third-party software components required by the EcoTrace Intelligent
Electronic Waste Recovery and Circular Economy Management System.

EcoTrace adopts a cloud-first architecture based primarily on Flutter
and Google Firebase. These software interfaces provide authentication,
data storage, cloud computing, messaging, mapping, AI inference,
payment processing, communication, and reporting capabilities.

All software interfaces shall communicate using secure protocols and
standardized APIs while maintaining interoperability, scalability,
availability, maintainability, and enterprise-grade security.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Flutter Framework}

Flutter shall serve as the primary cross-platform application
development framework for Android mobile applications, Windows Desktop
applications, and Web applications.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Software Interface Requirements}

\paragraph{SIR-001 Cross-Platform Development}

The platform shall be developed using the Flutter framework.

\paragraph{SIR-002 Android Support}

Flutter shall support Android mobile devices.

\paragraph{SIR-003 Windows Support}

Flutter shall support Microsoft Windows Desktop.

\paragraph{SIR-004 Web Support}

Flutter shall support modern web browsers.

\paragraph{SIR-005 Responsive Interface}

Flutter shall provide responsive user interfaces across supported
platforms.

\paragraph{SIR-006 Material Design}

The user interface shall implement Google's Material Design principles.

\paragraph{SIR-007 Performance}

Flutter applications shall maintain responsive user interaction.

\paragraph{SIR-008 Plugin Support}

Flutter shall integrate approved third-party plugins.

\paragraph{SIR-009 Offline Storage}

Flutter shall support secure local storage for offline operation.

\paragraph{SIR-010 Platform Updates}

Applications shall remain compatible with supported Flutter releases.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Firebase Authentication}

Firebase Authentication shall provide centralized user identity
management and authentication services.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Software Interface Requirements}

\paragraph{SIR-011 User Registration}

The system shall support secure user registration.

\paragraph{SIR-012 User Authentication}

Users shall authenticate using Firebase Authentication.

\paragraph{SIR-013 Email Verification}

Email verification shall be supported.

\paragraph{SIR-014 Password Reset}

Users shall securely reset forgotten passwords.

\paragraph{SIR-015 Multi-Factor Authentication}

The platform shall support multi-factor authentication where enabled.

\paragraph{SIR-016 Session Management}

Authenticated sessions shall be securely managed.

\paragraph{SIR-017 Token Validation}

Authentication tokens shall be validated before resource access.

\paragraph{SIR-018 Account Lockout}

Repeated authentication failures shall trigger account protection
mechanisms.

\paragraph{SIR-019 Secure Logout}

Users shall securely terminate authenticated sessions.

\paragraph{SIR-020 Authentication Audit}

Authentication activities shall be recorded by the Audit Trail and
Activity Logging Module.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Cloud Firestore}

Cloud Firestore shall serve as the primary NoSQL cloud database for the
EcoTrace platform. It shall securely store structured application data,
support real-time synchronization, and provide scalable access for all
authorized users and services.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Software Interface Requirements}

\paragraph{SIR-021 Database Storage}

Cloud Firestore shall store structured application data.

\paragraph{SIR-022 Real-Time Synchronization}

The database shall support real-time data synchronization.

\paragraph{SIR-023 Offline Persistence}

Firestore shall support offline data persistence on supported devices.

\paragraph{SIR-024 Access Control}

Database access shall be controlled using Firebase Security Rules.

\paragraph{SIR-025 Data Validation}

Incoming data shall be validated before storage.

\paragraph{SIR-026 Transaction Support}

Firestore shall support atomic database transactions.

\paragraph{SIR-027 Scalability}

The database shall automatically scale according to application demand.

\paragraph{SIR-028 Backup Support}

Database backups shall be performed according to configured backup
policies.

\paragraph{SIR-029 Audit Logging}

Database modification activities shall be recorded by the Audit Trail
and Activity Logging Module.

\paragraph{SIR-030 High Availability}

Firestore shall provide highly available cloud database services.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Firebase Storage}

Firebase Storage shall securely store electronic waste images,
documents, reports, certificates, user profile images, AI datasets, and
other digital files generated by the EcoTrace platform.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Software Interface Requirements}

\paragraph{SIR-031 Secure File Storage}

The platform shall securely store uploaded files in Firebase Storage.

\paragraph{SIR-032 Image Upload}

Users shall upload electronic waste photographs.

\paragraph{SIR-033 Document Upload}

Users shall upload reports, certificates, invoices, and supporting
documents.

\paragraph{SIR-034 File Validation}

Uploaded files shall be validated before storage.

\paragraph{SIR-035 Access Control}

File access shall comply with Firebase Storage Security Rules.

\paragraph{SIR-036 File Versioning}

The platform shall maintain file versions where applicable.

\paragraph{SIR-037 Download Support}

Authorized users shall securely download stored files.

\paragraph{SIR-038 Automatic Compression}

Large images shall be compressed before storage where appropriate.

\paragraph{SIR-039 Malware Protection}

Uploaded files should be scanned for malicious content before use where
supported by the deployment environment.

\paragraph{SIR-040 Storage Monitoring}

Administrators shall monitor storage utilization.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Cloud Functions}

Cloud Functions shall execute server-side business logic, automation,
notifications, scheduled tasks, AI workflows, and system integration
services.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Software Interface Requirements}

\paragraph{SIR-041 Serverless Execution}

Cloud Functions shall execute backend business logic.

\paragraph{SIR-042 Event Triggers}

Functions shall execute in response to configured events.

\paragraph{SIR-043 Scheduled Tasks}

The platform shall support scheduled background jobs.

\paragraph{SIR-044 Notification Processing}

Cloud Functions shall process notification events.

\paragraph{SIR-045 AI Processing}

Cloud Functions shall invoke AI inference services where applicable.

\paragraph{SIR-046 Data Validation}

Cloud Functions shall validate business rules before database updates.

\paragraph{SIR-047 External API Integration}

Cloud Functions shall securely communicate with approved external APIs.

\paragraph{SIR-048 Logging}

Function execution logs shall be maintained.

\paragraph{SIR-049 Error Handling}

Cloud Functions shall implement structured exception handling.

\paragraph{SIR-050 Scalability}

Cloud Functions shall automatically scale based on workload.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Firebase Cloud Messaging}

Firebase Cloud Messaging (FCM) shall deliver push notifications to
Android devices, Web browsers, and Windows desktop applications.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Software Interface Requirements}

\paragraph{SIR-051 Push Notifications}

The platform shall deliver secure push notifications.

\paragraph{SIR-052 Device Registration}

Supported client devices shall register for push notifications.

\paragraph{SIR-053 Topic Messaging}

The platform shall support topic-based notification delivery.

\paragraph{SIR-054 Individual Messaging}

Notifications shall be delivered to individual users.

\paragraph{SIR-055 Group Messaging}

Notifications shall be delivered to authorized user groups.

\paragraph{SIR-056 Notification Priority}

The system shall support configurable notification priority levels.

\paragraph{SIR-057 Delivery Confirmation}

The platform shall monitor notification delivery status where supported.

\paragraph{SIR-058 Notification History}

Notification history shall be maintained.

\paragraph{SIR-059 Secure Messaging}

Notification payloads shall be securely transmitted.

\paragraph{SIR-060 Notification Logging}

Push notification events shall be recorded by the Audit Trail and
Activity Logging Module.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Google Maps Platform}

Google Maps Platform shall provide mapping, geolocation, route
optimization, navigation, geocoding, and spatial visualization services
for the EcoTrace platform.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Software Interface Requirements}

\paragraph{SIR-061 Interactive Maps}

The platform shall display interactive digital maps.

\paragraph{SIR-062 GPS Integration}

Google Maps shall integrate with device GPS hardware.

\paragraph{SIR-063 Geocoding}

The platform shall convert addresses into geographic coordinates.

\paragraph{SIR-064 Reverse Geocoding}

The platform shall convert geographic coordinates into readable
addresses.

\paragraph{SIR-065 Route Navigation}

The platform shall calculate navigation routes between locations.

\paragraph{SIR-066 Route Optimization}

The platform shall recommend optimized collection and delivery routes.

\paragraph{SIR-067 Distance Calculation}

The platform shall calculate travel distance between locations.

\paragraph{SIR-068 Estimated Travel Time}

Estimated travel times shall be calculated automatically.

\paragraph{SIR-069 Geofencing}

Google Maps services shall support geofencing operations.

\paragraph{SIR-070 Map Visualization}

Operational activities shall be displayed on interactive maps.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Artificial Intelligence Inference Service}

Artificial Intelligence services shall provide electronic waste
identification, classification, object detection, image analysis, and
decision support capabilities.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Software Interface Requirements}

\paragraph{SIR-071 AI Model Loading}

Approved AI models shall be loaded securely.

\paragraph{SIR-072 Image Classification}

AI services shall classify electronic waste images.

\paragraph{SIR-073 Object Detection}

AI services shall detect electronic devices and components.

\paragraph{SIR-074 Confidence Score}

Prediction confidence values shall accompany AI results.

\paragraph{SIR-075 Model Version}

The platform shall maintain AI model version information.

\paragraph{SIR-076 AI Logging}

Prediction activities shall be logged.

\paragraph{SIR-077 AI Monitoring}

Administrators shall monitor AI service health.

\paragraph{SIR-078 AI Error Handling}

Prediction failures shall be handled gracefully.

\paragraph{SIR-079 AI Scalability}

AI inference services shall support scalable processing.

\paragraph{SIR-080 AI Security}

AI services shall securely process uploaded images.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Payment Gateway}

The EcoTrace platform shall integrate with secure payment gateways to
support marketplace purchases, service payments, subscriptions, and
financial transactions.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Software Interface Requirements}

\paragraph{SIR-081 Payment Processing}

The platform shall process secure electronic payments.

\paragraph{SIR-082 Transaction Verification}

Completed payment transactions shall be verified.

\paragraph{SIR-083 Refund Support}

Approved refunds shall be processed securely.

\paragraph{SIR-084 Payment Receipts}

Digital payment receipts shall be generated automatically.

\paragraph{SIR-085 Transaction History}

Payment history shall be maintained.

\paragraph{SIR-086 Secure Encryption}

Payment information shall be encrypted during transmission.

\paragraph{SIR-087 Payment Notifications}

Users shall receive payment confirmation notifications.

\paragraph{SIR-088 Failed Transactions}

Failed payment transactions shall generate appropriate error messages.

\paragraph{SIR-089 Financial Audit}

Payment activities shall be recorded for auditing.

\paragraph{SIR-090 Payment Availability}

Payment services shall provide high availability.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Email Service}

The Email Service shall support user verification, password recovery,
system notifications, reports, and administrative communication.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Software Interface Requirements}

\paragraph{SIR-091 Email Verification}

The platform shall send verification emails.

\paragraph{SIR-092 Password Recovery}

Password reset emails shall be delivered securely.

\paragraph{SIR-093 Notification Emails}

The platform shall distribute operational notifications by email.

\paragraph{SIR-094 Report Delivery}

Generated reports shall be delivered by email.

\paragraph{SIR-095 Attachment Support}

Emails shall support document attachments.

\paragraph{SIR-096 Delivery Monitoring}

Email delivery status shall be monitored.

\paragraph{SIR-097 Retry Mechanism}

Failed email delivery attempts shall be retried.

\paragraph{SIR-098 Email Templates}

The platform shall maintain reusable email templates.

\paragraph{SIR-099 Email Logging}

Email activities shall be logged.

\paragraph{SIR-100 Secure Email Transmission}

Emails shall be transmitted using secure communication protocols.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{SMS Gateway}

SMS Gateway services shall provide text message notifications for
authentication, alerts, reminders, and operational communication.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Software Interface Requirements}

\paragraph{SIR-101 SMS Notifications}

The platform shall send SMS notifications.

\paragraph{SIR-102 One-Time Passwords}

SMS services shall support one-time password delivery.

\paragraph{SIR-103 Pickup Reminders}

Users shall receive pickup reminder messages.

\paragraph{SIR-104 Emergency Alerts}

Critical operational alerts shall be delivered by SMS.

\paragraph{SIR-105 Delivery Confirmation}

SMS delivery status shall be monitored.

\paragraph{SIR-106 Message Retry}

Failed SMS delivery shall support automatic retry.

\paragraph{SIR-107 SMS Templates}

Reusable SMS templates shall be maintained.

\paragraph{SIR-108 SMS Logging}

SMS communication activities shall be recorded.

\paragraph{SIR-109 Secure Messaging}

SMS messages shall comply with organizational security policies.

\paragraph{SIR-110 Gateway Availability}

The SMS Gateway shall provide high service availability.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection*{Software Validation Rules}

\begin{itemize}

\item All software interfaces shall use authenticated and encrypted
communication.

\item External APIs shall validate requests before processing.

\item AI services shall process only supported image formats.

\item Payment transactions shall be verified before completion.

\item Email and SMS notifications shall be logged.

\item Database updates shall comply with defined business rules.

\item Cloud Functions shall validate all incoming requests.

\item Software components shall support graceful error handling.

\item All software integrations shall comply with organizational
security policies.

\item All software interface activities shall be recorded by the Audit
Trail and Activity Logging Module.

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection*{Software Acceptance Criteria}

\paragraph{SAC-001}

Flutter applications operate successfully across Android, Windows, and
Web platforms.

\paragraph{SAC-002}

Firebase Authentication securely authenticates users.

\paragraph{SAC-003}

Cloud Firestore stores and synchronizes application data correctly.

\paragraph{SAC-004}

Firebase Storage securely stores uploaded files.

\paragraph{SAC-005}

Cloud Functions execute business logic successfully.

\paragraph{SAC-006}

Firebase Cloud Messaging delivers notifications reliably.

\paragraph{SAC-007}

Google Maps Platform provides accurate mapping and navigation services.

\paragraph{SAC-008}

Artificial Intelligence services generate reliable predictions.

\paragraph{SAC-009}

Payment, Email, and SMS services operate securely and reliably.

\paragraph{SAC-010}

The EcoTrace platform integrates all software services into a secure,
scalable, enterprise-grade software ecosystem.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Communication Interface Requirements}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Overview}

The Communication Interface Requirements define the communication
protocols, networking technologies, messaging mechanisms, data exchange
formats, and transmission standards used by the EcoTrace Intelligent
Electronic Waste Recovery and Circular Economy Management System.

These interfaces enable secure communication between mobile
applications, web applications, desktop applications, cloud services,
artificial intelligence services, external APIs, IoT devices, payment
gateways, and third-party systems.

All communication interfaces shall ensure confidentiality, integrity,
availability, authentication, interoperability, and high performance.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{HTTPS Communication}

Hypertext Transfer Protocol Secure (HTTPS) shall be the primary
communication protocol between all client applications and cloud
services.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Communication Interface Requirements}

\paragraph{CIR-001 Secure Communication}

All client-server communication shall use HTTPS.

\paragraph{CIR-002 TLS Encryption}

HTTPS communication shall use Transport Layer Security (TLS).

\paragraph{CIR-003 Certificate Validation}

Client applications shall validate server certificates before
communication.

\paragraph{CIR-004 Confidentiality}

Sensitive information shall be encrypted during transmission.

\paragraph{CIR-005 Integrity}

Communication shall protect transmitted information against
unauthorized modification.

\paragraph{CIR-006 Authentication}

Authenticated requests shall include valid security tokens.

\paragraph{CIR-007 Session Protection}

Communication sessions shall remain protected against hijacking.

\paragraph{CIR-008 Timeout Management}

Inactive communication sessions shall expire automatically.

\paragraph{CIR-009 Error Handling}

Communication failures shall generate meaningful error messages.

\paragraph{CIR-010 Logging}

HTTPS communication events shall be recorded where appropriate.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{REST API Communication}

RESTful APIs shall enable communication between EcoTrace client
applications, backend services, cloud functions, AI services, and
approved third-party systems.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Communication Interface Requirements}

\paragraph{CIR-011 REST Architecture}

All application APIs shall follow REST architectural principles.

\paragraph{CIR-012 HTTP Methods}

The platform shall support GET, POST, PUT, PATCH, and DELETE methods as
appropriate.

\paragraph{CIR-013 Authentication}

REST APIs shall require authenticated access where applicable.

\paragraph{CIR-014 Authorization}

API requests shall comply with role-based access control policies.

\paragraph{CIR-015 Request Validation}

Incoming API requests shall be validated before processing.

\paragraph{CIR-016 Response Validation}

API responses shall follow standardized response structures.

\paragraph{CIR-017 Error Responses}

REST APIs shall return standardized HTTP status codes.

\paragraph{CIR-018 Rate Limiting}

The platform shall support API rate limiting.

\paragraph{CIR-019 API Versioning}

REST APIs shall support version management.

\paragraph{CIR-020 API Documentation}

All public APIs shall be documented using approved API documentation
standards.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{JSON Data Exchange}

JavaScript Object Notation (JSON) shall be the primary format used for
data exchange throughout the EcoTrace platform.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Communication Interface Requirements}

\paragraph{CIR-021 JSON Format}

Application data shall be exchanged using JSON.

\paragraph{CIR-022 UTF-8 Encoding}

JSON documents shall use UTF-8 character encoding.

\paragraph{CIR-023 Schema Validation}

JSON payloads shall be validated before processing.

\paragraph{CIR-024 Required Fields}

Mandatory JSON fields shall be validated.

\paragraph{CIR-025 Data Types}

JSON values shall comply with defined data types.

\paragraph{CIR-026 Null Handling}

The platform shall properly handle null values.

\paragraph{CIR-027 Nested Objects}

Nested JSON structures shall be supported.

\paragraph{CIR-028 Array Support}

JSON arrays shall be supported.

\paragraph{CIR-029 Serialization}

Objects shall be serialized consistently.

\paragraph{CIR-030 Deserialization}

Incoming JSON payloads shall be safely deserialized.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{WebSocket Communication}

WebSocket communication shall provide real-time bidirectional
communication between EcoTrace client applications and backend services
for live operational monitoring, notifications, fleet tracking, and
dashboard updates.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Communication Interface Requirements}

\paragraph{CIR-031 Real-Time Communication}

The platform shall support real-time bidirectional communication using
WebSockets.

\paragraph{CIR-032 Persistent Connection}

The platform shall maintain persistent WebSocket connections while
authorized sessions remain active.

\paragraph{CIR-033 Connection Authentication}

WebSocket connections shall require authenticated users.

\paragraph{CIR-034 Secure WebSockets}

The platform shall use Secure WebSockets (WSS).

\paragraph{CIR-035 Automatic Reconnection}

Client applications shall automatically reconnect after temporary
connection loss.

\paragraph{CIR-036 Live Dashboard Updates}

Operational dashboards shall receive live updates.

\paragraph{CIR-037 Fleet Tracking}

Vehicle locations shall be updated in real time.

\paragraph{CIR-038 Notification Delivery}

Real-time notifications shall be delivered through WebSocket
connections where appropriate.

\paragraph{CIR-039 Connection Monitoring}

The platform shall monitor WebSocket connection health.

\paragraph{CIR-040 Connection Logging}

WebSocket connection activities shall be logged.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Push Notification Communication}

Push notification services shall deliver operational updates, reminders,
alerts, approvals, and emergency notifications to authorized users.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Communication Interface Requirements}

\paragraph{CIR-041 Notification Delivery}

Push notifications shall be delivered to registered client devices.

\paragraph{CIR-042 Device Registration}

Devices shall register securely before receiving notifications.

\paragraph{CIR-043 User Targeting}

Notifications shall support delivery to individual users.

\paragraph{CIR-044 Group Targeting}

Notifications shall support delivery to user groups.

\paragraph{CIR-045 Broadcast Notifications}

Authorized administrators shall broadcast notifications to all users.

\paragraph{CIR-046 Notification Priority}

Notifications shall support configurable priority levels.

\paragraph{CIR-047 Delivery Confirmation}

Notification delivery status shall be monitored where supported.

\paragraph{CIR-048 Notification History}

The platform shall maintain notification history.

\paragraph{CIR-049 Retry Mechanism}

Failed notification delivery shall support automatic retry.

\paragraph{CIR-050 Notification Audit}

Notification activities shall be recorded by the Audit Trail and
Activity Logging Module.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Secure File Upload Communication}

Secure file upload services shall support photographs, reports,
certificates, invoices, AI datasets, and supporting documentation.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Communication Interface Requirements}

\paragraph{CIR-051 Secure Upload}

Uploaded files shall use encrypted communication channels.

\paragraph{CIR-052 File Validation}

Uploaded files shall be validated before storage.

\paragraph{CIR-053 Supported File Formats}

The platform shall accept only approved file formats.

\paragraph{CIR-054 File Size Validation}

Maximum upload sizes shall be enforced.

\paragraph{CIR-055 Virus Scanning}

Uploaded files should be scanned for malicious content where supported
by the deployment environment.

\paragraph{CIR-056 Upload Progress}

The application shall display upload progress indicators.

\paragraph{CIR-057 Upload Recovery}

Interrupted uploads shall support resumption where technically feasible.

\paragraph{CIR-058 File Integrity}

Uploaded files shall be verified after transfer.

\paragraph{CIR-059 Secure Storage}

Uploaded files shall be securely transferred to cloud storage.

\paragraph{CIR-060 Upload Logging}

File upload activities shall be recorded.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Transport Layer Security (TLS)}

Transport Layer Security (TLS) shall provide encrypted communication
between all EcoTrace components and external systems.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Communication Interface Requirements}

\paragraph{CIR-061 TLS Support}

All external communications shall use Transport Layer Security.

\paragraph{CIR-062 Certificate Validation}

Digital certificates shall be validated before communication.

\paragraph{CIR-063 Encryption Algorithms}

The platform shall use industry-standard encryption algorithms.

\paragraph{CIR-064 Secure Key Exchange}

Cryptographic keys shall be exchanged securely.

\paragraph{CIR-065 Certificate Renewal}

TLS certificates shall be renewed before expiration.

\paragraph{CIR-066 Forward Secrecy}

Communication should support Perfect Forward Secrecy where supported.

\paragraph{CIR-067 Protocol Validation}

Only approved TLS protocol versions shall be permitted.

\paragraph{CIR-068 Secure Handshake}

TLS handshake procedures shall verify endpoint authenticity.

\paragraph{CIR-069 Encryption Monitoring}

Communication encryption status shall be monitored continuously.

\paragraph{CIR-070 TLS Audit}

TLS-related security events shall be logged.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection*{Communication Validation Rules}

\begin{itemize}

\item All communication channels shall use authenticated and encrypted
connections.

\item API requests shall validate authentication tokens before
processing.

\item JSON payloads shall conform to approved schemas.

\item WebSocket sessions shall terminate automatically after logout.

\item Uploaded files shall satisfy configured validation rules before
storage.

\item Notification delivery failures shall be logged.

\item TLS certificates shall remain valid throughout communication.

\item Communication failures shall generate standardized error
responses.

\item Unauthorized communication attempts shall be rejected.

\item All communication activities shall be recorded by the Audit Trail
and Activity Logging Module.

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection*{Communication Acceptance Criteria}

\paragraph{CAC-001}

HTTPS communication securely protects all client-server interactions.

\paragraph{CAC-002}

REST APIs successfully exchange validated application data.

\paragraph{CAC-003}

JSON payloads are correctly serialized and deserialized.

\paragraph{CAC-004}

WebSocket communication provides reliable real-time updates.

\paragraph{CAC-005}

Push notifications are delivered successfully.

\paragraph{CAC-006}

Secure file uploads complete without compromising data integrity.

\paragraph{CAC-007}

TLS encryption protects all communication channels.

\paragraph{CAC-008}

Communication failures are detected and handled appropriately.

\paragraph{CAC-009}

Unauthorized communication attempts are prevented.

\paragraph{CAC-010}

The EcoTrace platform provides secure, reliable, scalable, and
enterprise-grade communication across all integrated system components.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{External System Interfaces}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Overview}

The External System Interface Requirements define how the EcoTrace
Intelligent Electronic Waste Recovery and Circular Economy Management
System exchanges information with external organizations, government
agencies, certified recycling partners, logistics providers, cloud
platforms, financial service providers, and future third-party systems.

External interfaces shall provide secure, authenticated, interoperable,
and standards-compliant communication using approved application
programming interfaces (APIs), secure communication protocols, and data
exchange standards.

All external integrations shall comply with organizational security,
privacy, environmental regulations, and data governance requirements.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Government Environmental Agencies}

EcoTrace shall support secure integration with government environmental
protection agencies responsible for monitoring electronic waste
management, environmental compliance, and regulatory reporting.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{External Interface Requirements}

\paragraph{EIR-001 Regulatory Reporting}

The platform shall generate regulatory reports for authorized
government agencies.

\paragraph{EIR-002 Compliance Data}

Environmental compliance information shall be securely exchanged.

\paragraph{EIR-003 Authorized Access}

Only authorized government personnel shall access regulatory
information.

\paragraph{EIR-004 Secure APIs}

Government interfaces shall communicate through secure APIs.

\paragraph{EIR-005 Audit Logging}

Government data exchanges shall be recorded for auditing.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Licensed Recycling Partners}

The platform shall exchange operational information with licensed
electronic waste recycling partners.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{External Interface Requirements}

\paragraph{EIR-006 Recycler Registration}

Licensed recycling organizations shall be registered before integration.

\paragraph{EIR-007 Material Transfer}

The platform shall securely exchange electronic waste transfer records.

\paragraph{EIR-008 Recycling Confirmation}

Recycling completion confirmations shall be received electronically.

\paragraph{EIR-009 Certificate Exchange}

Digital recycling certificates shall be exchanged securely.

\paragraph{EIR-010 Performance Reporting}

The platform shall receive recycling performance information.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Waste Collection Partners}

Authorized waste collection companies shall integrate with EcoTrace to
manage collection requests and transportation activities.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{External Interface Requirements}

\paragraph{EIR-011 Pickup Integration}

Collection requests shall be exchanged electronically.

\paragraph{EIR-012 Route Information}

Authorized collection partners shall receive assigned routes.

\paragraph{EIR-013 Collection Status}

Collection status updates shall be transmitted in real time.

\paragraph{EIR-014 GPS Tracking}

Collection vehicle locations shall be shared securely where authorized.

\paragraph{EIR-015 Collection Reports}

Collection performance reports shall be exchanged electronically.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Educational Institutions}

Educational institutions participating in electronic waste awareness,
research, or collection programs may integrate with the platform.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{External Interface Requirements}

\paragraph{EIR-016 Institution Registration}

Educational institutions shall register before participation.

\paragraph{EIR-017 Collection Campaigns}

Institutions shall participate in approved collection campaigns.

\paragraph{EIR-018 Research Data}

Authorized research data shall be exchanged securely.

\paragraph{EIR-019 Awareness Reports}

The platform shall generate educational campaign reports.

\paragraph{EIR-020 Student Participation}

Educational participation statistics shall be maintained.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Non-Governmental Organizations (NGOs)}

Authorized NGOs may participate in awareness campaigns,
community outreach, sustainability programs, and environmental
initiatives.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{External Interface Requirements}

\paragraph{EIR-021 NGO Registration}

NGOs shall register before accessing partnership services.

\paragraph{EIR-022 Partnership Projects}

The platform shall support collaborative environmental projects.

\paragraph{EIR-023 Awareness Campaigns}

NGOs shall participate in approved awareness campaigns.

\paragraph{EIR-024 Project Reporting}

Project progress reports shall be exchanged electronically.

\paragraph{EIR-025 Sustainability Metrics}

NGOs shall access approved sustainability statistics.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Carbon Credit Platforms}

Future versions of EcoTrace may integrate with carbon credit
marketplaces to support verified environmental sustainability
initiatives.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{External Interface Requirements}

\paragraph{EIR-026 Carbon Reporting}

Verified environmental impact data shall support carbon reporting.

\paragraph{EIR-027 Carbon Calculations}

Carbon reduction calculations shall be exchanged securely.

\paragraph{EIR-028 Verification}

Carbon information shall undergo verification before submission.

\paragraph{EIR-029 Secure Integration}

Carbon platforms shall communicate using secure APIs.

\paragraph{EIR-030 Carbon Audit}

Carbon reporting activities shall be recorded for auditing.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Logistics Providers}

Authorized logistics providers may integrate with EcoTrace to support
transportation, warehouse management, and shipment tracking.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{External Interface Requirements}

\paragraph{EIR-031 Shipment Registration}

Transport shipments shall be registered electronically.

\paragraph{EIR-032 Shipment Tracking}

Shipment status shall be monitored in real time.

\paragraph{EIR-033 Delivery Confirmation}

Completed deliveries shall be confirmed electronically.

\paragraph{EIR-034 Logistics Reports}

Logistics providers shall exchange operational reports.

\paragraph{EIR-035 Route Optimization}

Approved logistics providers shall receive optimized transportation
routes.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection*{External Interface Validation Rules}

\begin{itemize}

\item All external systems shall authenticate before exchanging data.

\item External APIs shall use encrypted communication channels.

\item Data exchanged with external organizations shall comply with
organizational privacy and security policies.

\item Failed integrations shall generate standardized error messages.

\item External data shall be validated before processing.

\item Unauthorized external systems shall be denied access.

\item External communication shall comply with approved API standards.

\item Regulatory reports shall use verified operational data.

\item Carbon reporting shall use validated environmental metrics.

\item All external interface activities shall be recorded by the Audit
Trail and Activity Logging Module.

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection*{External Interface Acceptance Criteria}

\paragraph{EAC-001}

Government regulatory reporting operates successfully.

\paragraph{EAC-002}

Licensed recycling partners exchange information securely.

\paragraph{EAC-003}

Collection partners receive and update operational information.

\paragraph{EAC-004}

Educational institutions and NGOs participate securely.

\paragraph{EAC-005}

Carbon reporting integrations operate correctly where enabled.

\paragraph{EAC-006}

Logistics providers exchange transportation information successfully.

\paragraph{EAC-007}

All external systems authenticate securely.

\paragraph{EAC-008}

External communication uses encrypted protocols.

\paragraph{EAC-009}

External data exchanges are fully auditable.

\paragraph{EAC-010}

The EcoTrace platform securely integrates with approved external
organizations, government agencies, and enterprise partners.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%







%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Interface Security Requirements}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Overview}

The Interface Security Requirements define the security controls,
authentication mechanisms, authorization policies, encryption methods,
audit capabilities, and monitoring procedures that protect all
interfaces within the EcoTrace Intelligent Electronic Waste Recovery
and Circular Economy Management System.

Security controls shall apply consistently across Android mobile
applications, Web applications, Windows desktop applications, cloud
services, databases, APIs, communication channels, IoT devices, and
external systems.

The platform shall implement the principles of Confidentiality,
Integrity, Availability, Authentication, Authorization, Accountability,
and Non-Repudiation.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Authentication Security}

\subsubsection*{Security Requirements}

\paragraph{ISR-001 User Authentication}

All users shall authenticate before accessing protected resources.

\paragraph{ISR-002 Multi-Factor Authentication}

The platform shall support Multi-Factor Authentication (MFA) for
privileged accounts.

\paragraph{ISR-003 Password Policy}

Passwords shall satisfy configured complexity requirements.

\paragraph{ISR-004 Password Encryption}

Passwords shall never be stored in plaintext.

\paragraph{ISR-005 Session Timeout}

Inactive user sessions shall expire automatically.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Authorization Security}

\subsubsection*{Security Requirements}

\paragraph{ISR-006 Role-Based Access Control}

Access permissions shall follow Role-Based Access Control (RBAC).

\paragraph{ISR-007 Least Privilege}

Users shall receive only the permissions required to perform assigned
responsibilities.

\paragraph{ISR-008 Resource Authorization}

Every protected resource shall verify authorization before access.

\paragraph{ISR-009 Administrative Privileges}

Administrative privileges shall be granted only to authorized personnel.

\paragraph{ISR-010 Privilege Revocation}

Privileges shall be revoked immediately after authorization changes.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Communication Security}

\subsubsection*{Security Requirements}

\paragraph{ISR-011 HTTPS}

All communications shall use HTTPS.

\paragraph{ISR-012 TLS Encryption}

Communication channels shall use Transport Layer Security (TLS).

\paragraph{ISR-013 Secure APIs}

External APIs shall require authenticated access.

\paragraph{ISR-014 Secure Tokens}

Authentication tokens shall be securely transmitted and validated.

\paragraph{ISR-015 Certificate Validation}

Digital certificates shall be validated before communication.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Data Security}

\subsubsection*{Security Requirements}

\paragraph{ISR-016 Encryption at Rest}

Sensitive data shall be encrypted while stored.

\paragraph{ISR-017 Encryption in Transit}

Sensitive information shall remain encrypted during transmission.

\paragraph{ISR-018 Secure Storage}

Uploaded files shall be securely stored.

\paragraph{ISR-019 Backup Security}

Backup files shall be encrypted.

\paragraph{ISR-020 Data Integrity}

Stored information shall be protected against unauthorized
modification.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Audit and Monitoring Security}

\subsubsection*{Security Requirements}

\paragraph{ISR-021 Audit Logging}

Security events shall be recorded.

\paragraph{ISR-022 Login Monitoring}

User login activities shall be monitored.

\paragraph{ISR-023 Failed Authentication}

Repeated failed authentication attempts shall generate alerts.

\paragraph{ISR-024 Security Alerts}

Critical security events shall notify administrators.

\paragraph{ISR-025 Incident Investigation}

Security logs shall support forensic investigations.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Application Security}

\subsubsection*{Security Requirements}

\paragraph{ISR-026 Input Validation}

All user input shall be validated.

\paragraph{ISR-027 SQL Injection Protection}

The platform shall prevent injection attacks.

\paragraph{ISR-028 Cross-Site Scripting Protection}

The platform shall protect against XSS attacks.

\paragraph{ISR-029 Cross-Site Request Forgery Protection}

The platform shall protect against CSRF attacks where applicable.

\paragraph{ISR-030 Secure Error Messages}

System error messages shall not disclose sensitive information.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection*{Security Validation Rules}

\begin{itemize}

\item Authentication shall be required before accessing protected
resources.

\item Authorization shall be verified before every protected operation.

\item Sensitive information shall always remain encrypted.

\item Security events shall be logged automatically.

\item Administrative activities shall require elevated privileges.

\item Failed authentication attempts shall trigger monitoring.

\item API requests shall validate authentication tokens.

\item Uploaded files shall satisfy security validation.

\item External integrations shall use encrypted communication.

\item Security policies shall comply with organizational governance
requirements.

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection*{Security Acceptance Criteria}

\paragraph{IAC-001}

All authenticated users successfully access only authorized resources.

\paragraph{IAC-002}

Sensitive information remains encrypted during storage and transmission.

\paragraph{IAC-003}

Unauthorized access attempts are prevented.

\paragraph{IAC-004}

Security events are logged successfully.

\paragraph{IAC-005}

The EcoTrace platform provides enterprise-grade security across all
interfaces.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Interface Error Handling}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Overview}

The Interface Error Handling Requirements define the mechanisms used by
the EcoTrace Intelligent Electronic Waste Recovery and Circular Economy
Management System to detect, report, manage, and recover from interface
errors occurring across user interfaces, hardware interfaces, software
interfaces, communication interfaces, and external system integrations.

The objectives of error handling are to maintain system availability,
protect data integrity, provide meaningful feedback to users, support
system recovery, and facilitate troubleshooting by administrators.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{User Interface Error Handling}

\subsubsection*{Error Handling Requirements}

\paragraph{IER-001 Input Validation}

Invalid user input shall generate descriptive validation messages.

\paragraph{IER-002 Mandatory Fields}

Required fields shall be clearly identified before form submission.

\paragraph{IER-003 Error Highlighting}

Fields containing invalid values shall be visually highlighted.

\paragraph{IER-004 User Guidance}

Error messages shall provide recommendations for correcting the problem.

\paragraph{IER-005 Session Expiration}

Expired user sessions shall redirect users to the authentication page.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Hardware Interface Error Handling}

\subsubsection*{Error Handling Requirements}

\paragraph{IER-006 Device Detection}

Disconnected hardware devices shall be detected automatically.

\paragraph{IER-007 Camera Errors}

Camera failures shall generate descriptive notifications.

\paragraph{IER-008 GPS Errors}

Unavailable GPS services shall notify affected users.

\paragraph{IER-009 Scanner Errors}

QR code and barcode scanning failures shall generate retry options.

\paragraph{IER-010 Printer Errors}

Printer failures shall generate printable error reports where
appropriate.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Software Interface Error Handling}

\subsubsection*{Error Handling Requirements}

\paragraph{IER-011 Database Errors}

Database operation failures shall be logged and handled gracefully.

\paragraph{IER-012 Cloud Service Errors}

Cloud service failures shall trigger automatic retry where appropriate.

\paragraph{IER-013 AI Service Errors}

AI prediction failures shall notify users without exposing internal
implementation details.

\paragraph{IER-014 Storage Errors}

File upload and download failures shall provide recovery options.

\paragraph{IER-015 Notification Errors}

Notification delivery failures shall be logged.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Communication Error Handling}

\subsubsection*{Error Handling Requirements}

\paragraph{IER-016 Network Failure}

Communication interruptions shall generate connection status
notifications.

\paragraph{IER-017 API Failure}

API communication failures shall return standardized error responses.

\paragraph{IER-018 Timeout Handling}

Communication timeouts shall support configurable retry mechanisms.

\paragraph{IER-019 Offline Mode}

Supported client applications shall continue operating in offline mode
where applicable.

\paragraph{IER-020 Synchronization Recovery}

Offline synchronization failures shall be recoverable after network
restoration.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{External System Error Handling}

\subsubsection*{Error Handling Requirements}

\paragraph{IER-021 Third-Party Service Failure}

External integration failures shall not interrupt unrelated platform
functions.

\paragraph{IER-022 Payment Errors}

Payment failures shall notify users and prevent duplicate transactions.

\paragraph{IER-023 Email Delivery Failure}

Email delivery failures shall support automatic retry.

\paragraph{IER-024 SMS Delivery Failure}

SMS delivery failures shall be logged and retried where appropriate.

\paragraph{IER-025 External API Errors}

External API failures shall be recorded for administrative review.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection*{Error Handling Validation Rules}

\begin{itemize}

\item Error messages shall never expose confidential system
information.

\item Recoverable errors shall provide users with appropriate recovery
options.

\item Critical failures shall generate administrator alerts.

\item Failed transactions shall maintain data consistency.

\item Error logs shall include timestamps and diagnostic information.

\item Retry mechanisms shall prevent duplicate operations.

\item Communication failures shall not corrupt stored data.

\item Offline operations shall synchronize after connectivity is
restored.

\item External service failures shall be isolated where possible.

\item All interface errors shall be recorded by the Audit Trail and
Activity Logging Module.

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection*{Error Handling Acceptance Criteria}

\paragraph{IEC-001}

Users receive meaningful and actionable error messages.

\paragraph{IEC-002}

Recoverable failures are handled without system crashes.

\paragraph{IEC-003}

Critical failures generate administrator notifications.

\paragraph{IEC-004}

System data remains consistent after interface failures.

\paragraph{IEC-005}

The EcoTrace platform provides reliable and fault-tolerant interface
error handling across all supported components.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Interface Validation Rules}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Overview}

The Interface Validation Rules define the verification procedures,
business rules, consistency checks, integrity constraints, and quality
assurance mechanisms that shall be applied to all interfaces within the
EcoTrace Intelligent Electronic Waste Recovery and Circular Economy
Management System.

These validation rules ensure that information exchanged between users,
hardware devices, software services, communication channels, and
external systems remains accurate, complete, secure, consistent, and
reliable throughout the system lifecycle.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{General Validation Rules}

\paragraph{IVR-001 Authentication Validation}

All protected interfaces shall verify user authentication before
processing requests.

\paragraph{IVR-002 Authorization Validation}

Every protected operation shall verify user authorization according to
Role-Based Access Control (RBAC).

\paragraph{IVR-003 Required Fields}

Mandatory information shall be validated before submission.

\paragraph{IVR-004 Data Type Validation}

All input values shall conform to the expected data type.

\paragraph{IVR-005 Input Length}

Input values shall satisfy defined minimum and maximum length
constraints.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Data Validation Rules}

\paragraph{IVR-006 Unique Identifiers}

Primary identifiers shall remain unique throughout the system.

\paragraph{IVR-007 Duplicate Prevention}

Duplicate records shall not be created unless explicitly permitted.

\paragraph{IVR-008 Date Validation}

Dates shall represent valid calendar values.

\paragraph{IVR-009 Numerical Validation}

Numeric values shall satisfy defined business constraints.

\paragraph{IVR-010 File Validation}

Uploaded files shall comply with approved file formats and size limits.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Communication Validation Rules}

\paragraph{IVR-011 Secure Communication}

All interface communication shall use encrypted channels.

\paragraph{IVR-012 API Validation}

API requests shall satisfy authentication and schema validation.

\paragraph{IVR-013 JSON Validation}

JSON payloads shall conform to approved schemas.

\paragraph{IVR-014 Timeout Validation}

Communication timeouts shall trigger recovery procedures.

\paragraph{IVR-015 Response Validation}

Responses received from external systems shall be validated before use.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Database Validation Rules}

\paragraph{IVR-016 Referential Integrity}

Database relationships shall maintain referential integrity.

\paragraph{IVR-017 Transaction Validation}

Database transactions shall satisfy ACID properties where applicable.

\paragraph{IVR-018 Concurrency Validation}

Simultaneous updates shall prevent data inconsistency.

\paragraph{IVR-019 Backup Validation}

Backup files shall be verified before restoration.

\paragraph{IVR-020 Audit Validation}

Critical database changes shall be recorded by the Audit Trail and
Activity Logging Module.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Security Validation Rules}

\paragraph{IVR-021 Password Validation}

Passwords shall comply with organizational password policies.

\paragraph{IVR-022 Token Validation}

Authentication tokens shall be validated before resource access.

\paragraph{IVR-023 Session Validation}

User sessions shall remain valid throughout authenticated operations.

\paragraph{IVR-024 Encryption Validation}

Sensitive information shall remain encrypted during storage and
transmission.

\paragraph{IVR-025 Access Validation}

Unauthorized access attempts shall be rejected immediately.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Operational Validation Rules}

\paragraph{IVR-026 Asset Registration}

Electronic assets shall be registered before participating in
operational workflows.

\paragraph{IVR-027 Collection Validation}

Collection requests shall satisfy operational business rules before
approval.

\paragraph{IVR-028 Recycling Validation}

Recycling records shall be verified before certificate generation.

\paragraph{IVR-029 Payment Validation}

Payments shall be verified before transaction completion.

\paragraph{IVR-030 Report Validation}

Generated reports shall contain verified operational information.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection*{Validation Acceptance Criteria}

\paragraph{VAC-001}

All required input fields are successfully validated.

\paragraph{VAC-002}

Invalid information is rejected before processing.

\paragraph{VAC-003}

Database integrity is maintained.

\paragraph{VAC-004}

Secure communication validation operates correctly.

\paragraph{VAC-005}

Business rules are consistently enforced across all platform interfaces.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Chapter Summary}

This chapter presented the External Interface Requirements for the
EcoTrace Intelligent Electronic Waste Recovery and Circular Economy
Management System.

The chapter defined the functional and technical interfaces required for
communication between users, hardware devices, software services,
communication networks, and external organizations.

The User Interface Requirements described the interfaces provided for
households, businesses, collectors, drivers, technicians, recyclers,
organizations, administrators, super administrators, and Windows
desktop users while incorporating comprehensive accessibility
requirements.

The Hardware Interface Requirements specified the supported hardware
devices including Android smartphones, Windows computers, digital
cameras, GPS receivers, QR code scanners, barcode scanners, printers,
and future Internet of Things (IoT) sensors.

The Software Interface Requirements identified the software platforms,
frameworks, databases, cloud services, artificial intelligence
components, mapping services, communication services, payment systems,
and external software integrations required by the platform.

The Communication Interface Requirements defined the secure networking
protocols, REST APIs, JSON data exchange mechanisms, WebSocket
communication, push notification services, secure file transfer, and
Transport Layer Security (TLS) requirements.

The External System Interface Requirements described secure integration
with government environmental agencies, licensed recycling partners,
waste collection partners, educational institutions,
non-governmental organizations, carbon credit platforms, and logistics
providers.

Finally, the chapter established enterprise-grade requirements for
interface security, error handling, and validation to ensure secure,
reliable, interoperable, and scalable communication across all
components of the EcoTrace platform.

The interface requirements defined in this chapter provide the
foundation for implementing a secure, maintainable, and enterprise-grade
electronic waste recovery and circular economy management system.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
